---
title: "CORT covariates"
author: "Katherine Lauck"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE,fig.width = 3, fig.height = 2)
library(tidyverse)
require(ggeffects)
require(lme4)
require(viridis)
library(car)
library(gt)
library(ggpubr)
library(cowplot)
library(magick)
g <- read_rds("../data/growth.rds")
c <- read_rds("../data/cort_with_id.rds")

fun_peak <- function(x, adjust = 1) {
  d <- density(x, adjust = adjust)
  d$x[c(F, diff(diff(d$y) >= 0) < 0)]
}

peaks <- filter(c,
               Sex == "F",
               Age %in% c("SY","ASY","AHY")) %>%
  group_by(year,Species) %>%
  summarize(peaks = fun_peak(juliandate))

af <- filter(c,
               Sex == "F",
               Age %in% c("SY","ASY","AHY")) %>%
  arrange(desc(date.x)) %>%
  distinct(blood_num,.keep_all = TRUE) %>%
  group_by(year,ind_id) %>%
  group_map(~ {
    if(nrow(.x) > 1) {
      .x <- arrange(.x,juliandate) %>%
        mutate(mother_attempt_num = seq(from = 1, to = nrow(.x)))
    } else {
      peak <- filter(peaks,year == .y$year,Species == .x$Species)
      difference <- abs(.x$juliandate-peak)
      .x <- mutate(.x,mother_attempt_num = which.min(difference$peaks))
    }
  }) %>% list_rbind() %>%
  mutate(mother_attempt_num = factor(mother_attempt_num))
```
Objective: What factors affect CORT of adult female WEBL and TRES?

## Adult Females
### Distribution of the data
#### WEBL

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
   ggtitle("S1") +
   geom_density(fill = "grey"))


(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
    ggtitle("S2") +
   geom_density(fill = "grey"))

```

#### TRES

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("S1") +
   geom_density(fill = "grey"))


(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
    ggtitle("S2") +
   geom_density(fill = "grey"))

```

### Cort coviariate candidates for adult females

1. Brood size: larger broods require more care, which increases adult female baseline and stress response cort
2. Body condition of female: This could be either low condition -> high baseline cort or high baseline cort -> low condition
    a. Lower condition requires individuals to mobilize more emergency energy in order to reproduce, which requires increasing cort levels in blood
    b. An exogenous source of stress (predation pressure, competition, low food supply) increases baseline cort, which mobilizes more stored energy, lowering body condition.
3. Day of year: Later in the season, the weather is hotter and dryer, and food is less abundant, and females may have already had a first clutch, so they may have higher baseline cort later in the season.
4. For this female, is this attempt 1 or 2 of this year?: Second attempts are later in the season, when the weather is hotter and dryer and food is less abundant, and females have already expended a lot of energy laying eggs during the first attempt, so they may have higher baseline cort during the second attempt.

To investigate these covariates, I ran a full model:

cort ~ brood_size * habitat + condition * habitat + juliandate or nestingattemptfemale

For each of the covariates, I:

1. Plotted the distribution of the covariate
2. Plotted how the covariate changed over julian date (seasonal variation) and how it was associated with female attempt number
3. Plotted the observed correlation between the covariate and adult female cort
4. Plotted the model-predicted relationship between the covariate and adult female cort
5. Used maximum-likelihood model comparison to determine whether the inclusion of the covariate improves the model. 

Plots and models are per species and separated between s1 & s2 where appropriate.

### Summary of findings

First off, whether to use julian day or mother attempt number. I found very few differences in significance of covariates and no differences in model selection between models using julian day or mother attempt number (results compared throughout details of findings #1 and #2. I think julian day is more holistic and will soak up more unwanted variation, so I think that's what we should use.

```{r}
(t <- expand.grid(model = c("additive","interactive"),
                  seasonal = c("Julian day", "Mother attempt number"),
                 factor = c("Brood size","Condition","Julian day","Mother attempt number"),
                 sample = c("s1","s2"),
                 species = c("WEBL","TRES")) %>%
  tibble() %>%
  mutate(significant = c("Yes","No","Yes","No", # WEBL S1 bs
                         "No","No","No","Yes", # WEBL s1 c
                         "No",NA,NA,NA, #WEBL s1 jd
                         NA,NA,"No",NA, #WEBL s1 ma
                         "No","No","No","No", # WEBL S2 bs
                         "No","No","Yes","Yes", # WEBL s2 c
                         "No",NA,NA,NA, #WEBL s2 jd
                         NA,NA,"No",NA, #WEBL s2 ma
                         "No","No","No","No", #TRES S1 bs
                         "No","No","No","No", #TRES s1 c
                         "No",NA,NA,NA, #TRES s1 jd
                         NA,NA,"No",NA, #TRES s1 ma
                         "No","Yes","No","Yes", #TRES S2 bs
                         "No","No","No","No", # TRES s2 c
                         "No",NA,NA,NA, #TRES s2 jd
                         NA,NA,"No",NA #TRES s2 ma
  )) %>%
   pivot_wider(names_from = c(sample,factor),values_from = significant) %>%
   gt() %>%
   tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = list(
      cells_body(
        columns = `s1_Brood size`,
        rows = `s1_Brood size` == "Yes"),
      cells_body(
        columns = `s1_Condition`,
        rows = `s1_Condition` == "Yes"),
      cells_body(
        columns = `s1_Julian day`,
        rows = `s1_Julian day` == "Yes"),
      cells_body(
        columns = `s1_Mother attempt number`,
        rows = `s1_Julian day` == "Yes"),
      cells_body(
        columns = `s2_Brood size`,
        rows = `s2_Brood size` == "Yes"),
      cells_body(
        columns = `s2_Condition`,
        rows = `s2_Condition` == "Yes"),
      cells_body(
        columns = `s2_Julian day`,
        rows = `s2_Julian day` == "Yes"),
      cells_body(
        columns = `s2_Mother attempt number`,
        rows = `s2_Julian day` == "Yes")))  %>%
   tab_spanner_delim(
    delim="_"
  ))
```

This table summarizes my findings. A "Yes" indicates a model in which the specified factor (the columns) significantly improved the parsimony of the model. I used likelihood ratio tests for all comparisons to compare a model with and without the factor in its linear or interactive form. The first column, model, describes whether the covariate under consideration is additive or interacted with habitat. I did not interact habitat with julian day or mother attempt number, so those significance indicators are NA.  The second column, seasonal, describes whether the seasonal variation in cort was quantified using julian day of female capture or mother attempt number. The third column indicates the species under consideration. The column spanners indicate whether the measure was baseline or stressed cort, and the column names indicate the covariate under consideration. There don't seem to be many patterns, other than that neither julian day nor mother attempt number improved the models. Maybe baseline cort is more related to chronic stressors than stressed cort? And there doesn't seem to be a huge difference in pattern between julian day and mother attempt number. Because julian date is a better measure of seasonal variation for a lot of different things, and it appears to be capturing much the same information (except maybe for WEBL s2 condition?), I think I would prefer to use julian day moving forward. I was only able to directly determine the attempt number for a few females (not more than 4), and the rest were determined using the calculated peaks of the density distribution of mother capture date, so julian day and mother attempt number are very close to the same information anyways.

### Details of findings

#### 1. How does brood size relate to cort?

##### Distribution of brood size

```{r}
(p <- ggplot(aes(x = brood_size),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
   ggtitle("WEBL") +
   geom_density(fill = "grey"))

(p <- ggplot(aes(x = brood_size),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("TRES") +
   geom_density(fill = "grey"))

```

##### Seasonal variation in brood size

```{r}
ggplot(mapping = aes(x = juliandate,y = brood_size),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = juliandate,y = brood_size),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES")
```

##### Variation between mother attempt number in brood size

```{r}

ggplot(mapping = aes(x = mother_attempt_num,y = brood_size,group = mother_attempt_num),data = filter(af,
                                                               Species == "WEBL")) +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = mother_attempt_num,y = brood_size,group = mother_attempt_num),data = filter(af,
                                                               Species == "TRES")) +
  geom_violin() +
  geom_point() +
  ggtitle("TRES")
```

##### Correlation of brood size and cort

###### WEBL

```{r}
ggplot(mapping = aes(x = brood_size,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL",
                                                               condition < 1.5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = brood_size,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL",
                                                               condition < 1.5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

###### TRES

```{r}
ggplot(mapping = aes(x = brood_size,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = brood_size,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

##### Model-predicted relationship between brood size and cort

Reminder: full model is 
- cort ~ brood_size * habitat + condition * habitat + juliandate and 
- cort ~ brood_size * habitat + condition * habitat + mother attempt number

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s1_ma <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s1_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```

Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. It looks like results are fairly similar between juliandate and mother attempt number.

###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s1_noint <- lm(mean_s1_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s1_noint_ma <- lm(mean_s1_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar_ma <- lm(mean_s1_scaled ~ condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar_ma,m_s1_noint_ma,m_s1_ma) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model. Based on the table, it looks like including brood_size does improve the model, but including its interaction with habitat does not significantly improve the model. Overall results appear to be the same between julian day and mother attempt number.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=4}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s2_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s2_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)
```

Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. The results are pretty much the same between julian day and mother attempt number.

###### Plot of predicted relationship between stressed cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

(p <- ggpredict(m_s2_ma,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?



```{r}
m_s2_noint <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s2_noint_ma <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar_ma <- lm(mean_s2_scaled ~ condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar_ma,m_s2_noint_ma,m_s2_ma) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")
```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model. Based on the table, it looks like including brood_size, even as a linear term, does not improve the model. Results are similar between julian day and mother attempt number.

###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s1_ma <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s1_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```


Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. Responses are similar between julian day and mother attempt number.


###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s1_noint <- lm(mean_s1_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s1_noint_ma <- lm(mean_s1_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar_ma <- lm(mean_s1_scaled ~ condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar_ma,m_s1_noint_ma,m_s1_ma) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model. Based on the table, it looks like including brood_size does not improve the model. Responses are similar between julian day and mother attempt number.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s2_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s2_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```

Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. Results were similar for julian date and mother attempt number.

###### Plot of predicted relationship between stressed cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s2_noint <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s2_noint_ma <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar_ma <- lm(mean_s2_scaled ~ condition_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar_ma,m_s2_noint_ma,m_s2_ma) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model. Based on the table, it looks like including brood_size as an interaction between habitat and brood_size does improve the model. Results are similar between julian date and mother attempt number.

#### 1. How does body condition relate to cort?

##### Distribution of condition

```{r}
(p <- ggplot(aes(x = condition),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL",
                                       condition < 1.5)) +
   theme_classic() +
   ggtitle("WEBL") +
   geom_density(fill = "grey"))

(p <- ggplot(aes(x = condition),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("TRES") +
   geom_density(fill = "grey"))

```

##### Seasonal variation in condition

```{r}
ggplot(mapping = aes(x = juliandate,y = condition),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL",
                                                               condition < 1.5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = juliandate,y = condition),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES")

```

##### Variation between mother attempt number in condition

```{r}

ggplot(mapping = aes(x = mother_attempt_num,y = condition,group = mother_attempt_num),data = filter(af,
                                                               Species == "WEBL",
                                                               condition < 1.5)) +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = mother_attempt_num,y = condition,group = mother_attempt_num),data = filter(af,
                                                               Species == "TRES")) +
  geom_violin() +
  geom_point() +
  ggtitle("TRES")
```

##### Correlation of condition and cort

###### WEBL

```{r}
ggplot(mapping = aes(x = condition,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL",
                                                              condition < 1.5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = condition,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL",
                                                              condition < 1.5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

###### TRES

```{r}
ggplot(mapping = aes(x = condition,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = condition,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

##### Model-predicted relationship between condition and cort

Reminder: full model is 
- cort ~ brood_size * habitat + condition * habitat + juliandate and 
- cort ~ brood_size * habitat + condition * habitat + mother attempt number

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s1_ma <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s1_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```

Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. It looks like results are fairly similar between juliandate and mother attempt number.

###### Plot of predicted relationship between baseline cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT WEBL; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s1_noint <- lm(mean_s1_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s1_noint_ma <- lm(mean_s1_scaled ~ condition_scaled + brood_size * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar_ma <- lm(mean_s1_scaled ~ brood_size * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar_ma,m_s1_noint_ma,m_s1_ma) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model. Based on the table, it looks like condition only improves the model when it is interacted with habitat, and then only when mother_attempt_num is a predictor.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=4}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s2_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s2_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)
```

Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. The results are pretty much the same between julian day and mother attempt number.

###### Plot of predicted relationship between stressed cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

(p <- ggpredict(m_s2_ma,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Stressed CORT WEBL; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?



```{r}
m_s2_noint <- lm(mean_s2_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s2_noint_ma <- lm(mean_s2_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar_ma,m_s2_noint_ma,m_s2_ma) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")
```

This table compares three models: the full model, one with no interaction between habitat and condition, and one without condition in the model. Based on the table, it looks like including condition in the model only improves it when it is a linear term and then only when mother_attempt_number is included as a covariate.

###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s1_ma <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s1_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```


Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. Responses are similar between julian day and mother attempt number.


###### Plot of predicted relationship between baseline cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT TRES; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s1_noint <- lm(mean_s1_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s1_noint_ma <- lm(mean_s1_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s1_nocovar_ma <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar_ma,m_s1_noint_ma,m_s1_ma) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and condition, and one without condition in the model. Based on the table, it looks like including condition does not improve the model. Responses are similar between julian day and mother attempt number.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

m_s2_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate") %>% gtsave('t1.png',path = getwd())

t <- summary(m_s2_ma) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t2 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number") %>% gtsave('t2.png',path = getwd())

t1 <- ggdraw() + draw_image('t1.png')
t2 <- ggdraw() + draw_image('t2.png')
ggarrange(t1,t2,ncol = 2)

```

Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved. Results were similar for julian date and mother attempt number.

###### Plot of predicted relationship between stressed cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

(p2 <- ggpredict(m_s1_ma,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "condition") +
   ggtitle("Baseline CORT TRES; predictor mother attempt number") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}
m_s2_noint <- lm(mean_s2_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

# %>%
#   gtsave('t1.png',path = getwd())

m_s2_noint_ma <- lm(mean_s2_scaled ~ condition_scaled + brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
m_s2_nocovar_ma <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + juliandate,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar_ma,m_s2_noint_ma,m_s2_ma) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

# %>%
#   gtsave('t2.png',path = getwd())
# 
# t1 <- ggdraw() + draw_image('t1.png')
# t2 <- ggdraw() + draw_image('t2.png')
# ggarrange(t1,t2,nrow = 2)

```

This table compares three models: the full model, one with no interaction between habitat and condition, and one without condition in the model. Based on the table, it looks like including condition does not improve the model. Results are similar between julian date and mother attempt number.

#### 3. How does julian day relate to cort?

##### Distribution of julian day

```{r}
(p <- ggplot(aes(x = juliandate),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
   ggtitle("WEBL") +
   geom_density(fill = "grey"))

(p <- ggplot(aes(x = juliandate),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("TRES") +
   geom_density(fill = "grey"))

```

##### Correlation of julian day and cort

###### WEBL

```{r}
ggplot(mapping = aes(x = juliandate,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = juliandate,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

###### TRES

```{r}
ggplot(mapping = aes(x = juliandate,y = mean_s1),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = juliandate,y = mean_s2),data = filter(c,
                                                               Sex == "F",
                                                               Age %in% c("SY","ASY","AHY"),
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
```

##### Model-predicted relationship between juliandate and cort

Reminder: full model is cort ~ brood_size * habitat + condition * habitat + juliandate

###### WEBL

Baseline cort as response variable:

```{r}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s1")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and julian day:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s1,terms = c("juliandate","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Julian day") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no julian day","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without julian day and the full model. Based on the table, it looks like including julian day does not improve the model.

###### Stressed cort as response variable

```{r}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s2")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and julian day:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("juliandate","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Julian day") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no julian day","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without julian day and the full model. Based on the table, it looks like including julian day does not improve the model.

###### TRES

Baseline cort as response variable:

```{r}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s1")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and julian day:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s1,terms = c("juliandate","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Julian day") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no julian day","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without julian day and the full model. Based on the table, it looks like including julian day does not improve the model.

###### Stressed cort as response variable

```{r}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + juliandate,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s2")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and julian day:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("juliandate","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Julian day") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no julian day","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without julian day and the full model. Based on the table, it looks like including julian day does not improve the model.

#### 4. How does attempt number by mother relate to cort?

To explore this question, I calculated attempt ID by mother. To do so, I assigned each mother an individual ID, which in all cases was her band number. I grouped female captures by year and individual ID, and for cases where the same female was caught twice in a year, I assigned attempt IDs. Then, I calculated the peaks of julian day for female captures for each year, and assigned each female the attempt number corresponding to the closest peak.

##### Distribution of cort over attempt number

```{r}

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s1,group = mother_attempt_num),data = filter(af,
                                                               Species == "WEBL")) +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL s1")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2,group = mother_attempt_num),data = filter(af,
                                                               Species == "WEBL")) +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL s2")
ggplot(mapping = aes(x = mother_attempt_num,y = mean_s1,group = mother_attempt_num),data = filter(af,
                                                               Species == "TRES")) +
  geom_violin() +
  geom_point() +
  ggtitle("TRES s1")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2,group = mother_attempt_num),data = filter(af,
                                                               Species == "TRES")) +
  geom_violin() +
  geom_point() +
  ggtitle("TRES s2")

```

##### Model-predicted relationship between mother attempt number and cort

Reminder: full model is cort ~ brood_size * habitat + condition * habitat + mother_attempt_num

###### WEBL

Baseline cort as response variable:

```{r}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s1")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and julian day:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother attempt number") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of mother attempt number improve the model?

```{r}
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no attempt number","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without mother attempt number and the full model. Based on the table, it looks like including mother attempt number does not improve the model.

###### Stressed cort as response variable

```{r}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s2")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.5) %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother attempt number","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without mother attempt number and the full model. Based on the table, it looks like including mother attempt number does not improve the model.

###### TRES

Baseline cort as response variable:

```{r}
m_s1 <- lm(mean_s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s1) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s1")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s1) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother attempt number") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of julian day improve the model?

```{r}
m_s1_nocovar <- lm(mean_s1_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = af %>%
            filter(!is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no mother attempt number","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without mother attempt number and the full model. Based on the table, it looks like including mother attempt number does not improve the model.

###### Stressed cort as response variable

```{r}
m_s2 <- lm(mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )


t <- summary(m_s2) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Model output: response variable is s2")
```

This is the same model as for other covariates. Personally, I think this model is rather overfitted: N = `r resid(m_s2) %>% length()`, but I left it as is so we could just see what the shape of the data is like with all of these terms involved.

###### Plot of predicted relationship between baseline cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p <- ggpredict(m_s2,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother attempt number") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

###### Does the inclusion of mother attempt number improve the model?

```{r}
m_s2_nocovar <- lm(mean_s2_scaled ~ condition_scaled * habitat + brood_size_scaled * habitat,
          data = af %>%
            filter(!is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother attempt number","full model"),.before = Res.Df) %>%
  rename(`P-value` = `Pr(>F)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt()
```

This table compares two models: one without mother attempt number and the full model. Based on the table, it looks like including mother attempt number does not improve the model.
