---
title: "Cort explorations"
author: "Katie Lauck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
library(tidyverse)
require(ggeffects)
require(lme4)
require(viridis)
library(car)
library(gt)
g <- read_rds("../data/growth.rds")
```

## Some important correlations

```{r}
ggplot(mapping = aes(x = brood_size,y = gweight),data = filter(g,Species == "TRES",meanmaxtempI < 40)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```

---

```{r}
ggplot(mapping = aes(x = habitat,y = gweight),data = filter(g,Species == "WEBL")) +
  geom_boxplot() +
  ggtitle("WEBL")
```

---

```{r}
ggplot(mapping = aes(x = habitat,y = gweight),data = filter(g,Species == "TRES")) +
  geom_boxplot() +
  ggtitle("TRES")
```

---

```{r}
ggplot(mapping = aes(x = habitat,y = cort_s1),data = filter(g,Species == "WEBL")) +
  geom_boxplot() +
  ggtitle("WEBL")
```

---

```{r}
ggplot(mapping = aes(x = habitat,y = cort_s2),data = filter(g,Species == "WEBL")) +
  geom_boxplot() +
  ggtitle("WEBL")
```

---

```{r}
ggplot(mapping = aes(x = habitat,y = cort_s1),data = filter(g,Species == "TRES")) +
  geom_boxplot() +
  ggtitle("TRES")
```


---

```{r}
ggplot(mapping = aes(x = habitat,y = cort_s2),data = filter(g,Species == "TRES")) +
  geom_boxplot() +
  ggtitle("TRES")
```

---

```{r}
hist(filter(g,cort_s1 < 100000)$cort_s1)
```

---

```{r }
hist(filter(g,cort_s2 < 100000)$cort_s2)
```


---

```{r}
ggplot(mapping = aes(x = cort_s1,y = gweight),data = filter(g,Species == "WEBL",cort_s1 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```

---

```{r}
ggplot(mapping = aes(x = cort_s1,y = gweight),data = filter(g,Species == "TRES",cort_s1 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```


---

```{r}
ggplot(mapping = aes(x = meanmaxtempI,y = cort_s1),data = filter(g,Species == "WEBL",cort_s1 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```


---

```{r}
ggplot(mapping = aes(x = meanmaxtempI,y = cort_s1),data = filter(g,Species == "TRES",cort_s1 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```

---

```{r}
ggplot(mapping = aes(x = cort_s2,y = gweight),data = filter(g,Species == "WEBL",cort_s2 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```

---

```{r}
ggplot(mapping = aes(x = cort_s2,y = gweight),data = filter(g,Species == "TRES")) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```


---

```{r}
ggplot(mapping = aes(x = meanmaxtempI,y = cort_s2),data = filter(g,Species == "WEBL",cort_s2 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```


---

```{r}
ggplot(mapping = aes(x = meanmaxtempI,y = cort_s2),data = filter(g,Species == "TRES")) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```


---

```{r}
ggplot(mapping = aes(x = cort_s1_mother,y = cort_s1),data = filter(g,Species == "WEBL",
                                                                   cort_s1_mother < 25000,
                                                                   cort_s1 < 10000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```


---

```{r}
ggplot(mapping = aes(x = cort_s2_mother,y = cort_s2),data = filter(g,Species == "WEBL",
                                                                   cort_s2 < 100000,
                                                                   cort_s2_mother < 100000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("WEBL")
```


---

```{r}
ggplot(mapping = aes(x = cort_s1_mother,y = cort_s1),data = filter(g,Species == "TRES")) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```


---

```{r}
ggplot(mapping = aes(x = cort_s2_mother,y = cort_s2),data = filter(g,Species == "TRES",
                                                                   cort_s2_mother < 60000)) +
  geom_smooth(method = "lm",formula = y ~ poly(x,2)) +
  geom_point() +
  ggtitle("TRES")
```

## Determining main model: WEBL

- meanI_WEBL_poly: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_WEBL_linear: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_WEBL_noint: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) + habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?
```{r}
meanI_WEBL_poly <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                      !is.na(meanmaxtempI)) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_linear <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                 !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_noint <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) + habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                   !is.na(meanmaxtempI)) %>%
                                      mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                    ~ scale(.x)[,1],
                                                    .names = "{.col}_scaled"),
                                             meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_poly,meanI_WEBL_linear,meanI_WEBL_noint) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

### Is squared term significant?
```{r}

meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_notemp <- lmerTest::lmer(gweight_scaled ~ habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                        !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_poly,meanI_WEBL_nosq,meanI_WEBL_notemp) %>% tibble() %>% mutate(model = c("no temp","linear temp","sq temp"),.before = npar) %>% gt()

anova(meanI_WEBL_nosq,meanI_WEBL_linear) %>% tibble() %>% mutate(model = c("no sq","linear int"),.before = npar) %>% gt()
```

---

```{r}
plot(meanI_WEBL_nosq)
```

---

```{r}
hist(resid(meanI_WEBL_nosq))
```

---

```{r}
qqnorm(resid(meanI_WEBL_nosq))
qqline(resid(meanI_WEBL_nosq))
```

---

```{r,fig.width=8.75,fig.height=6.25}
model <- meanI_WEBL_nosq

p <- ggpredict(model,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g/day)") +
    labs(title = element_blank(),color = "Cover type") +
   # ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))

unscale_x <- function(axis_break) {
  if(is.na(axis_break)) {
    return(NA)
  } else {
    sd_x = getData(model) %>% pull(meanmaxtempI) %>% sd(na.rm = TRUE)
    mean_x = getData(model) %>% pull(meanmaxtempI) %>% mean(na.rm = TRUE)
    out <- (axis_break * sd_x + mean_x) %>% round(digits = 0)
  }
}

unscale_y <- function(axis_break) {
  if(is.na(axis_break)) {
    return(NA)
  } else {
    sd_y = getData(model) %>% pull(gweight) %>% sd(na.rm = TRUE)
    mean_y = getData(model) %>% pull(gweight) %>% mean(na.rm = TRUE)
    out <- (axis_break * sd_y + mean_y) %>% round(digits = 1)
  }
}



 (p_rescaled <- p +
   scale_x_continuous(labels = map(layer_scales(p)$x$break_positions(),unscale_x) %>% unlist()) +
   scale_y_continuous(labels = map(layer_scales(p)$y$break_positions(),unscale_y) %>% unlist()))

 ggsave("../figures/rescaled_meanI_WEBL_nosq.png",p_rescaled,height = 4,width = 6)
```

---

```{r}
t <- summary(meanI_WEBL_nosq) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(4))

```

## Determining main model: TRES

- meanI_TRES: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_TRES_linear: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_TRES_noint: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?

```{r}
meanI_TRES <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


meanI_TRES_linear <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                                      filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_noint <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                                     filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES,meanI_TRES_linear,meanI_TRES_noint) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

### Is squared temp term significant?

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_notemp <- lmerTest::lmer(gweight_scaled ~ habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES,meanI_TRES_nosq,meanI_TRES_notemp) %>% tibble() %>% mutate(model = c("no temp","linear temp","sq temp"),.before = npar) %>% gt()

```

---

```{r}
plot(meanI_TRES_nosq)
```

---

```{r}
hist(resid(meanI_TRES_nosq))
```

---

```{r}
qqnorm(resid(meanI_TRES_nosq))
qqline(resid(meanI_TRES_nosq))
```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

---

```{r}
t <- summary(meanI_TRES_nosq) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(1))

```

## Triple interaction with humidity: WEBL {.smaller}

- Main model (meanI_WEBL_nosq): gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- Additive model (meanI_WEBL_humadd): gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- Interaction with temp only (meanI_WEBL_humbytemp): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- No habitat (meanI_WEBL_humnohab): gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?

```{r}
meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_humint,meanI_WEBL_humadd,meanI_WEBL_humbytemp,meanI_WEBL_nosq,meanI_WEBL_humnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no humidity","humidity * temp","double interactions","triple interaction"),.before = npar) %>% gt()

anova(meanI_WEBL_nosq,meanI_WEBL_humint) %>% tibble() %>% mutate(model = c("main model: no humidity","triple interaction"),.before = npar) %>% gt()
anova(meanI_WEBL_humint,meanI_WEBL_humbytemp) %>% tibble() %>% mutate(model = c("humidity * temp","triple interaction"),.before = npar) %>% gt()

```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_WEBL_humint,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Humidity") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## Triple interaction with humidity: TRES {.smaller}

- Main model (meanI_TRES): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Triple interaction model (meanI_TRES_humint): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Additive model (meanI_TRES_humadd): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + habitat * meanh_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Interaction with temp only (meanI_TRES_humbytemp): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- No habitat (meanI_TRES_humnohab): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)

---

### Is interaction significant?

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                      data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES_humint,meanI_TRES_humadd,meanI_TRES_humbytemp,meanI_TRES_nosq,meanI_TRES_humnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no humidity","humidity * temp","additive model","triple interaction"),.before = npar) %>% gt()

anova(meanI_TRES_nosq,meanI_TRES_humadd) %>% tibble() %>% mutate(model = c("main model: no humidity","additive model"),.before = npar) %>% gt()
anova(meanI_TRES_humadd,meanI_TRES_humbytemp) %>% tibble() %>% mutate(model = c("humidity * temp","additive model"),.before = npar) %>% gt()

```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_TRES_humbytemp,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
   ylim(-7.5,7.5) +
    labs(title = element_blank(),color = "Humidity") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

<!-- ## Triple interaction with canopy cover: WEBL {.smaller} -->

<!-- - Main model (meanI_WEBL_nosq): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Triple interaction model (meanI_WEBL_humint): gweight_scaled ~ meanmaxtempI_scaled * habitat * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Additive model (meanI_WEBL_humadd): gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * canopy_cover_scaled + meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Interaction with temp only (meanI_WEBL_humbytemp): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - No habitat (meanI_WEBL_humnohab): gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->

<!-- --- -->

<!-- ### Is interaction significant? Not for WEBL -->

<!-- ```{r} -->
<!-- meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL", -->
<!--                                                                                                                                                                                            !is.na(meanmaxtempI), -->
<!--                                                                                                                                                                         !is.na(canopy_cover)) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_WEBL_ccint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL", -->
<!--                                                                                                                                                                                            !is.na(meanmaxtempI), -->
<!--                                                                                                                                                                         !is.na(canopy_cover)) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_WEBL_ccadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * canopy_cover_scaled + meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL", -->
<!--                                                                                                                                                                                            !is.na(meanmaxtempI), -->
<!--                                                                                                                                                                         !is.na(canopy_cover)) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_WEBL_ccbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL", -->
<!--                                                                                                                                                                                            !is.na(meanmaxtempI), -->
<!--                                                                                                                                                                         !is.na(canopy_cover)) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_WEBL_ccnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL", -->
<!--                                                                                                                                                                                            !is.na(meanmaxtempI), -->
<!--                                                                                                                                                                         !is.na(canopy_cover)) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->

<!-- anova(meanI_WEBL_ccint,meanI_WEBL_ccadd,meanI_WEBL_ccbytemp,meanI_WEBL_nosq,meanI_WEBL_ccnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no canopy cover","cc * temp","double interactions","triple interaction"),.before = npar) %>% gt() -->

<!-- anova(meanI_WEBL_nosq,meanI_WEBL_ccbytemp) %>% tibble() %>% mutate(model = c("main model: no canopy cover","cc * temp"),.before = npar) %>% gt() -->

<!-- ``` -->

<!-- --- -->

<!-- ```{r,fig.width=8.75,fig.height=6.25} -->
<!-- (p <- ggpredict(meanI_WEBL_ccbytemp,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Canopy cover") + -->
<!--    ggtitle("Predicted growth across habitat and mean max daily temp") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 13)) -->
<!-- ) -->
<!-- ``` -->

<!-- ## Triple interaction with canopy cover: TRES {.smaller} -->

<!-- - Main model (meanI_TRES): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Triple interaction model (meanI_TRES_humint): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Additive model (meanI_TRES_humadd): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + habitat * canopy_cover_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - Interaction with temp only (meanI_TRES_humbytemp): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->
<!-- - No habitat (meanI_TRES_humnohab): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id) -->

<!-- --- -->

<!-- ### Is interaction significant? -->

<!-- ```{r,message=FALSE,warning=FALSE} -->
<!-- meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(canopy_cover),                                                                                                          meanmaxtempI < 45) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_TRES_ccint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(canopy_cover),                                                                                                          meanmaxtempI < 45) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_TRES_ccadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * canopy_cover_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(canopy_cover),                                                                                                          meanmaxtempI < 45) %>% -->
<!--                                     mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                   ~ scale(.x)[,1], -->
<!--                                                   .names = "{.col}_scaled"), -->
<!--                                            meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_TRES_ccbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id), -->
<!--                                        data = filter(g,Species == "WEBL", -->
<!--                                                      !is.na(meanmaxtempI),                                                                                                   !is.na(canopy_cover),                                                                                                          meanmaxtempI < 45) %>% -->
<!--                                          mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                        ~ scale(.x)[,1], -->
<!--                                                        .names = "{.col}_scaled"), -->
<!--                                                 meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->
<!-- meanI_TRES_ccnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id), -->
<!--                                       data = filter(g,Species == "WEBL", -->
<!--                                                     !is.na(meanmaxtempI), -->
<!--                                                     !is.na(canopy_cover), -->
<!--                                                     meanmaxtempI < 45) %>% -->
<!--                                         mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover), -->
<!--                                                       ~ scale(.x)[,1], -->
<!--                                                       .names = "{.col}_scaled"), -->
<!--                                                meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)) -->

<!-- anova(meanI_TRES_ccint,meanI_TRES_ccadd,meanI_TRES_ccbytemp,meanI_TRES_nosq,meanI_TRES_ccnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no canopy cover","cc * temp","additive model","triple interaction"),.before = npar) %>% gt() -->

<!-- anova(meanI_TRES_nosq,meanI_TRES_ccbytemp) %>% tibble() %>% mutate(model = c("main model: no humidity","cc * temp"),.before = npar) %>% gt() -->


<!-- ``` -->

<!-- --- -->

<!-- ```{r,fig.width=8.75,fig.height=6.25} -->
<!-- (p <- ggpredict(meanI_TRES_ccbytemp,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Canopy cover") + -->
<!--    ggtitle("Predicted growth across habitat and mean max daily temp") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 13)) -->
<!-- ) -->
<!-- ``` -->

## Beginning cort explorations

Data prep:
```{r,echo=TRUE}
c <- read_rds("../data/cort_with_id.rds")
```

---

### Variation in baseline cort within nest and occasion : WEBL

```{r}
sum <- filter(c,Age == "L") %>%
   group_by(attempt_id,occasion,Species) %>%
   summarize(se_s1 = sd(mean_s1),
             se_s2 = sd(mean_s2),
             se_condition = sd(condition))
ggplot(mapping = aes(x = se_s1),data = filter(sum,Species == "WEBL")) + geom_histogram()
```

---

### Variation in stressed cort within attempt and occasion WEBL

```{r}
ggplot(mapping = aes(x = se_s2),data = filter(sum,Species == "WEBL")) + geom_histogram()
```

---

### Variation in condition within attempt and occasion WEBL

```{r}
ggplot(mapping = aes(x = se_condition),data = filter(sum,Species == "WEBL")) + geom_histogram()
```

---

### Variation in baseline cort within nest and occasion : TRES

```{r}
ggplot(mapping = aes(x = se_s1),data = filter(sum,Species == "TRES")) + geom_histogram()
```

---

### Variation in stressed cort within attempt and occasion TRES

```{r}
ggplot(mapping = aes(x = se_s2),data = filter(sum,Species == "TRES")) + geom_histogram()
```

---

### Variation in condition within attempt and occasion TRES

```{r}
ggplot(mapping = aes(x = se_condition),data = filter(sum,Species == "TRES")) + geom_histogram()
```

---

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
   geom_histogram())

```


---

```{r}
(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "WEBL")) +
   theme_classic() +
   geom_histogram())

```

---

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   geom_histogram())

```

---

```{r}
(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Sex == "F" & Age %in% c("SY","ASY","AHY"),
                                       Species == "TRES")) +
   theme_classic() +
   geom_histogram())

```

## WEBL models {.smaller}

### Baseline
Model: mean_s1_scaled ~ brood_size_scaled + condition_scaled + habitat

```{r}
m_s1 <- lm(s1_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL",
                   condition < 1.9) %>%
            mutate(across(c(s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```
```{r}
summary(m_s1)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## {.smaller}

### Stressed

Model: mean_s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat
```{r}

m_s2 <- lm(s2_scaled ~ brood_size_scaled * habitat + condition_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL") %>%
            mutate(across(c(s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```

```{r}
summary(m_s2)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(m_s2,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    #scale_fill_viridis() +
    #scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Instead of habitat as factor, temp * humidity * canopy cover: by condition and brood size

```{r,message=FALSE,warning=FALSE}
m_s1_althab <- lm(s1_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "WEBL") %>%
            mutate(across(c(1,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(m_s1_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### By temp and brood size

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(m_s1_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT WEBL: by condition and brood size

```{r,message=FALSE,warning=FALSE}


mmean_s2_althab <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(mmean_s2_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT WEBL: by temp and brood size

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(mmean_s2_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

## TRES models {.smaller}

Baseline model: mean_s1_scaled ~ brood_size_scaled + condition_scaled * habitat
```{r}
mmean_s1 <- lm(s1_scaled ~ brood_size_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
mmean_s1_nestlings <- lm(cort_s1_scaled ~ cort_s1_mother_scaled,
          data = g %>%
            filter(life_stage == "nestling",
                   !is.na(cort_s1),
                   Species == "TRES") %>%
            mutate(across(c(cort_s1,cort_s1_mother),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

```
```{r}
summary(mmean_s1)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(mmean_s1,terms = c("condition_scaled","brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT TRES
Model: mean_s2_scaled ~ brood_size_scaled + condition_scaled * habitat

```{r}

mmean_s2 <- lm(s2_scaled ~ brood_size_scaled + condition_scaled + habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```

```{r}
summary(mmean_s2)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(mmean_s2,terms = c("condition_scaled","brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Alternative to habitat: temp* humidity * canopy cover

```{r,message=FALSE,warning=FALSE}
mmean_s1_althab <- lm(mean_s1_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(mmean_s1_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(mmean_s1_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message=FALSE,warning=FALSE}


mmean_s2_althab <- lm(mean_s2_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(mean_s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(mmean_s2_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(mmean_s2_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```


## Is there a difference between CORT among nestling sampling occasions? {.smaller}

### WEBL: baseline

```{r}
weblmean_s1 <- aov(cort_s1 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3)))

mean((g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(3)))$cort_s1,na.rm = TRUE)
summary(weblmean_s1)
TukeyHSD(weblmean_s1)
summary(lm(cort_s1 ~ poly(brood_size,2,raw = TRUE), data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3))))
```
### WEBL: stressed

```{r}
weblmean_s2 <- aov(cort_s2 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3)))
TukeyHSD(weblmean_s2)
mean((g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2)))$cort_s2,na.rm = TRUE)

summary(weblmean_s2)
plot(cort_s2 ~ brood_size, data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3)))
summary(lm(cort_s2 ~ poly(brood_size,2,raw = TRUE), data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3))))
```

---

### TRES: baseline

```{r}
tresmean_s1 <- aov(cort_s1 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))

TukeyHSD(tresmean_s1)
summary(tresmean_s1)
plot(cort_s1 ~ brood_size, data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))
summary(lm(cort_s1 ~ poly(brood_size,2,raw = TRUE), data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3))))
```

### TRES: stressed

```{r}
tresmean_s2 <- aov(cort_s2 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))
TukeyHSD(tresmean_s2)
summary(tresmean_s2)
plot(cort_s2 ~ brood_size, data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))
summary(lm(cort_s2 ~ poly(brood_size,2,raw = TRUE), data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3))))
```

My conclusion: Occasion does not seem to matter for baseline CORT but it does for stressed CORT.

---

### baby ~ mother * habitat + condition + brood size: WEBL mean_s1

```{r,message=FALSE,warning=FALSE}
weblmean_s1 <- lm(cort_s1_scaled ~ cort_s1_mother_scaled + habitat + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL",
                                  !is.na(cort_s1),
                                  !is.na(cort_s1_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s1 < 100,
                                  cort_s1_mother < 100) %>%
                           mutate(across(c(cort_s1,cort_s1_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(weblmean_s1,terms = c("cort_s1_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)



```

## {.smaller}

```{r}
summary(weblmean_s1)
```

---

### baby ~ mother + condition + brood size + habitat: WEBL mean_s2, occasion 2

```{r,message=FALSE,warning=FALSE}
weblmean_s2o2 <- lm(cort_s2_scaled ~ cort_s2_mother_scaled * habitat + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  occasion == 2,
                                  cort_s2 < 100,
                                  cort_s2_mother < 100) %>%
                           mutate(across(c(cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(weblmean_s2o2,terms = c("cort_s2_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## {.smaller}

```{r}
summary(weblmean_s2o2)
```

---

### baby ~ mother + condition + brood size + habitat: WEBL mean_s2, occasion 3

```{r,message=FALSE,warning=FALSE}
weblmean_s2o3 <- lm(cort_s2_scaled ~ cort_s2_mother_scaled + condition_scaled + brood_size_scaled + habitat,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  occasion == 3,
                                  cort_s2 < 100,
                                  cort_s2_mother < 100) %>%
                           mutate(across(c(cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(weblmean_s2o3,terms = c("cort_s2_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(weblmean_s2o3)
```

---

### baby ~ mother * habitat + condition + brood size: TRES mean_s1

```{r,message=FALSE,warning=FALSE}
tresmean_s1 <- lm(cort_s1_scaled ~ cort_s1_mother_scaled * habitat + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "TRES",
                                  !is.na(cort_s1),
                                  !is.na(cort_s1_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s1 < 100,
                                  cort_s1_mother < 100) %>%
                           mutate(across(c(cort_s1,cort_s1_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(tresmean_s1,terms = c("cort_s1_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(tresmean_s1)
```

---

### baby ~ mother * habitat + condition + brood size: TRES mean_s2 O2

```{r,message=FALSE,warning=FALSE}
tresmean_s2o2 <- lm(cort_s2_scaled ~ cort_s2_mother_scaled * habitat + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "TRES",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s2 < 100,
                                  cort_s2_mother < 100,
                                  occasion == 2) %>%
                           mutate(across(c(cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(tresmean_s2o2,terms = c("cort_s2_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT TRES O2") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(tresmean_s2o2)
```

---

### baby ~ mother * habitat + condition + brood size: TRES mean_s2 O2

```{r,message=FALSE,warning=FALSE}
tresmean_s2o3 <- lm(cort_s2_scaled ~ cort_s2_mother_scaled * habitat + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "TRES",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s2 < 100,
                                  cort_s2_mother < 100,
                                  occasion == 3) %>%
                           mutate(across(c(cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(tresmean_s2o3,terms = c("cort_s2_mother_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mother CORT") +
    ylab("Nestling CORT") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT TRES O3") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(tresmean_s2o3)
```

---

### growth ~ baby cort + mother + condition + habitat + brood size: WEBL mean_s1

```{r,message=FALSE,warning=FALSE}
weblmean_s1 <- lm(gweight_scaled ~ cort_s1_scaled + habitat + cort_s1_mother_scaled + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL",
                                  !is.na(cort_s1),
                                  !is.na(cort_s1_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s1 < 25,
                                  cort_s1_mother < 100) %>%
                           mutate(across(c(gweight,cort_s1,cort_s1_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(weblmean_s1,terms = c("cort_s1_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Baseline nestling CORT") +
    ylab("Average daily growth over ~1wk") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(weblmean_s1)
```

---

### growth ~ baby cort + mother + condition + habitat + brood size: TRES mean_s1

```{r,message=FALSE,warning=FALSE}
tresmean_s1 <- lm(gweight_scaled ~ cort_s1_scaled * habitat + cort_s1_mother_scaled + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "TRES",
                                  !is.na(cort_s1),
                                  !is.na(cort_s1_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s1 < 19,
                                  cort_s1_mother < 100) %>%
                           mutate(across(c(gweight,cort_s1,cort_s1_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(tresmean_s1,terms = c("cort_s1_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Baseline nestling CORT") +
    ylab("Average daily growth over ~1wk") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(tresmean_s1)
```

---

### growth ~ baby cort + mother + condition + habitat + brood size: TRES mean_s2

```{r,message=FALSE,warning=FALSE}
tresmean_s2 <- lm(gweight_scaled ~ cort_s2_scaled + habitat + cort_s2_mother_scaled + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "TRES",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s2 < 100,
                                  cort_s2_mother < 100) %>%
                           mutate(across(c(gweight,cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(tresmean_s2,terms = c("cort_s2_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Stressed nestling CORT") +
    ylab("Average daily growth over ~1wk") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(tresmean_s2)

plot
```

---

### growth ~ baby cort + mother + condition + habitat + brood size: WEBL mean_s2

```{r,message=FALSE,warning=FALSE}
weblmean_s2 <- lm(gweight_scaled ~ cort_s2_scaled + habitat + cort_s2_mother_scaled + condition_scaled + brood_size_scaled,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL",
                                  !is.na(cort_s2),
                                  !is.na(cort_s2_mother),
                                  !is.na(condition),
                                  !is.na(brood_size),
                                  !is.na(habitat),
                                  cort_s2 < 100,
                                  cort_s2_mother < 100) %>%
                           mutate(across(c(gweight,cort_s2,cort_s2_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
(p <- ggpredict(weblmean_s2,terms = c("cort_s2_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Stressed nestling CORT") +
    ylab("Average daily growth over ~1wk") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)

```

## {.smaller}

```{r}
summary(weblmean_s2)
```

## Does cort vary with temp and habitat like growth?

```{r}

cort_tempbyhab_WEBL <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site),
                            data = filter(g,Species == "WEBL",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1)) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_WEBL,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)


summary(cort_tempbyhab_WEBL)

cort_s2_tempbyhab_WEBL <- lmerTest::lmer(cort_s2_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat age + juliandate_scaled + (1|year) + (1|site),
                            data = filter(g,Species == "WEBL",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s2)) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s2),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_WEBL,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted stressed cort across habitat and mean max daily temp WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)


summary(cort_s2_tempbyhab_WEBL)
```


---

```{r}
cort_tempbyhab_TRES <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site),
                            data = filter(g,Species == "TRES",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 20) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_TRES,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

summary(cort_tempbyhab_TRES)

cort_s2_tempbyhab_TRES <- lmerTest::lmer(cort_s2_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + meanmaxtempI * age + juliandate_scaled + (1|year) + (1|site),
                            data = filter(g,Species == "TRES",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s2)) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s2),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_s2_tempbyhab_TRES,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

summary(cort_s2_tempbyhab_TRES)
```

## Condition models: Nestling WEBL

```{r}
# g <- g %>% mutate(condition = weight/tarsus)

ggplot(mapping = aes(x = cort_s1,y = condition),
       data = filter(g,Species == "WEBL",
                     cort_s1 < 20,
                     condition < 3)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL")

```

---

```{r}
cort_tempbyhab_WEBL <- lmerTest::lmer(cort_s1 ~ meanmaxtempI_scaled * habitat * condition_scaled + juliandate_scaled + poly(meanmintempI_scaled,2) * habitat + age + (1|year) + (1|site/attempt_id),
                            data = filter(g,Species == "WEBL",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 20) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1,condition),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: Nestling TRES

```{r}

ggplot(mapping = aes(x = cort_s1,y = condition),
       data = filter(g,Species == "TRES",
                     cort_s1 < 25)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES")

```

---

```{r,warning = FALSE,message=FALSE}
cort_tempbyhab_TRES <- lmerTest::lmer(cort_s1 ~ meanmaxtempI_scaled * habitat * condition_scaled + juliandate_scaled + poly(meanmintempI_scaled,2) * habitat + age + (1|year) + (1|site/attempt_id),
                            data = filter(g,Species == "TRES",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 20) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1,condition),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: adult female WEBL baseline cort

```{r}
AF_mean_s1_WEBL <- lm(mean_s1_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled,
                 data = filter(c, Species == "WEBL",
                               Sex == "F",
                               Age %in% c("SY","ASY","AHY"),
                               !is.na(meanmaxtempI),
                               !is.na(mean_s1),
                               mean_s1 < 25) %>%
              mutate(across(c(mean_s1,meanmaxtempI,condition,brood_size),
                            ~ scale(.x)[,1],
                            .names = "{.col}_scaled")))

(p <- ggpredict(AF_mean_s1_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: adult female WEBL stressed cort

```{r}
AF_mean_s2_WEBL <- lm(mean_s2_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled,
                 data = filter(c, Species == "WEBL",
                               Sex == "F",
                               Age %in% c("SY","ASY","AHY"),
                               !is.na(meanmaxtempI),
                               !is.na(mean_s2),
                               mean_s2 < 50) %>%
              mutate(across(c(mean_s2,meanmaxtempI,condition,brood_size),
                            ~ scale(.x)[,1],
                            .names = "{.col}_scaled")))

(p <- ggpredict(AF_mean_s2_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: adult female TRES baseline cort

```{r,warning=FALSE,message=FALSE}

AF_mean_s1_TRES <- lm(mean_s1_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled,
                 data = filter(c, Species == "TRES",
                               Sex == "F",
                               Age %in% c("SY","ASY","AHY"),
                               !is.na(meanmaxtempI),
                               !is.na(mean_s1),
                               mean_s1 < 25) %>%
              mutate(across(c(mean_s1,meanmaxtempI,condition,brood_size),
                            ~ scale(.x)[,1],
                            .names = "{.col}_scaled")))

(p <- ggpredict(AF_mean_s1_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: adult female TRES stressed cort

```{r,warning=FALSE,message=FALSE}

AF_mean_s2_TRES <- lm(mean_s2_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled,
                 data = filter(c, Species == "TRES",
                               Sex == "F",
                               Age %in% c("SY","ASY","AHY"),
                               !is.na(meanmaxtempI),
                               !is.na(mean_s2),
                               mean_s2 < 50) %>%
              mutate(across(c(mean_s2,meanmaxtempI,condition,brood_size),
                            ~ scale(.x)[,1],
                            .names = "{.col}_scaled")))

(p <- ggpredict(AF_mean_s2_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```
