---
title: Interactive effect of temp and land use on nestling growth, nestling cort,
  and adult visitation rate
author: "Kit Lauck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
### make prez figures
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
require(gt)
library(glmmTMB)
library(dagitty)
library(ggdag)
library(ggplot2)
library(igraph)
library(tidyverse)
library(performance)
library(modelsummary)
library(car)
library(lme4)
library(hms)
# modelsummary::get_gof(my_model)
# performance::model_performance(my_model)
wmean <- read_rds("../data/wmean.rds")

g <- read_rds("../data/growth_and_provis.rds")
p <- read_rds("../data/provis_with_attempt_1h.rds") %>%
  mutate(year = year(date),
         year_fct = as.factor(year))


```

## Why was there no provisioning before 11am?

Previously, we noticed there was a strange cutoff for provisioning. It was an accidental result of the temp matching process - time zone was not handled properly and so temps were matched to the wrong times.

### Provis by time of day: WEBL, 1h

```{r}
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "WEBL",habitat == "Forest"))
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "WEBL",habitat == "Orchard"))
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "WEBL",habitat == "Grassland"))
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "WEBL",habitat == "Row crop"))
```

---

```{r}
plot(mean_temp ~ tod_h, data = p %>%
       filter(species == "WEBL"))
```

So now provisioning and temp actually both line up in a way that seems reasonable. Yay!

### Provis by time of day: TRES

```{r}
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "TRES"))
```

---

```{r}
plot(mean_temp ~ tod_h, data = p %>%
       filter(species == "TRES"))
```

## Plot raw data for WEBL

```{r}
(pl <- ggplot(data = p %>% filter(!is.na(habitat),species == "WEBL",valid_detections < 30),aes(x = mean_temp,y = valid_detections,color = habitat)) +
   geom_point() +
   facet_wrap(~ habitat,ncol = 2) +
   theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))
)
```

Looks like a lot of the outliers are in forest. Wondering if this could be caused by moving leaves being detected as birds??

## First task: Figure out what distribution to use for modeling these data.

```{r}
hist(p %>% filter(species == "WEBL") %>% pull(valid_detections))
```

This looks like a poisson distribution would do okay here. But I will start with a Gaussian distribution for completeness.


## Base model with Gaussian distribution, qqplot

```{r}
m <- lmer(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 # family = poisson,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
# pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)

```


## Base model with Poisson distribution, qqplot

```{r}
m <- glmer(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = poisson,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
# pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)

qqnorm(resid(m))
qqline(resid(m))
check_collinearity(m)
check_model(m, panel = FALSE)




```

The Poisson distribution addresses the zero skewing but not the overdispersion?

## Test for overdispersion

```{r}
get_gof(m)

check_overdispersion(m)
check_zeroinflation(m)
```

So, we do have overdispersion and zero inflation.


## Let's try binomial distribution

```{r}
m <- glmer(cbind(valid_detections,max(valid_detections,na.rm = TRUE)-valid_detections) ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = binomial,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
```
Dispersion ratio is smaller than for Poisson, but still doesn't fully account for overdispersion. 

## Negative binomial

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 #ziformula = ~ poly(tod_h_scaled,2,raw = TRUE),
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
hist(simulate_residuals(m))
```


Negative binomial seems to address overdispersion and help with zeroinflation. If we add a zeroinflation term, what happens?

## Zero inflation model

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 30,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
check_residuals(m)

```

---


```{r}
plot(simulate_residuals(m)%>% residuals() ~ fitted(m))
hist(simulate_residuals(m))
```

Test for overdispersion and zeroinflation are negative, but there appears to be some non-uniformity of residuals. Poisson instead of negative binomial results in more overdispersion.

Looks like there are some outliers. I wonder if we can justify clipping off outliers - does it make sense for birds to visit more than 60x/hour? I suspect some of those videos are from birds sitting in the entrance the whole time.

## Rows with > 60 visits/hour clipped.

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 60,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
check_residuals(m)

```

---


```{r}
plot(simulate_residuals(m)%>% residuals() ~ fitted(m))
```

---

```{r}
hist(simulate_residuals(m))
```

Still some funkiness, and fat tails. Still some non-uniformity.


## Provisioning ~ heat * habitat, WEBL, forest

Squared term is supported, but the weird thing is that the model outputs are all NaN for the squared model when the ziformula is ~ 1.

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + tod_h_scaled + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL",
					              valid_detections < 30# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + tod_h_scaled + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL",
					              valid_detections < 30# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq temp"),.before = Df) %>% gt()
summary(sqtemp)
```

```{r}
(pl <- ggpredict(sqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   #ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

This doesn't seem to fit particularly well... How about the no sq model?

---

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   #ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

Also not great.

## Provisioning ~ heat * habitat, WEBL, orchard

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

This fits a lot better.

## Provisioning ~ heat * habitat, WEBL, grassland

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

This also does not fit very well...

## Provisioning ~ heat * habitat, WEBL, row crop

Squared term is not supported.

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(sqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(sqtemp)))
   )
```

## Conclusions

Squared temp is important in forest, but the model doesn't fit great. I'm leaning no squared temp term, personally.

```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq temp |
|--------------|:-------:|
| Forest       | *       |
| Orchard      |         |
| Grassland    |         |
| Row crop     |         |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## Is the squared term supported in the overall model?

```{r}
nosq <- glmmTMB(valid_detections ~ mean_temp_scaled * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 30,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
linint <- glmmTMB(valid_detections ~ mean_temp_scaled * habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 30,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

sq <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 30,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sq,linint,nosq) %>% tibble() %>% mutate(model = c("no sq","linear temp interaction","sq max temp"),.before = Df) %>% gt()
```


## Plotting inference model

```{r}
m <- glmmTMB(valid_detections ~ mean_temp_scaled * habitat + julian_date_scaled + tod_h_scaled + mean_nestling_age_scaled + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              valid_detections < 30,
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
```

---

```{r}
qqnorm(simulate_residuals(m) %>% resid())
qqline(simulate_residuals(m) %>% resid())
```


---


```{r}
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
check_residuals(m)
```

---

```{r}
hist(simulate_residuals(m))
```

---

```{r}
plot(simulate_residuals(m)%>% residuals() ~ fitted(m))
```

---

```{r}
plot(simulate_residuals(m)%>% residuals() ~ m$frame$mean_temp_scaled)
```

---

```{r}
plot(simulate_residuals(m) %>% resid() ~ m$frame$habitat)
```

---

```{r}
(pl <- ggpredict(m,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
   facet_wrap(~ group,ncol = 2) +
   # theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   ylim(0,50) +
   annotate("text", x = -1.5, y = 50, size = 5, label = paste("N =",nobs(m)))
   )
```

---

```{r}
summary(m)
```

## Conclusions:

High temps do appear to depress provisioning behavior. Looks like the squared term interaction is supported in the overall model.


## Provis by time of day: TRES, 1h

```{r}
plot(valid_detections ~ tod_h, data = p %>%
       filter(species == "TRES"))
```

---

```{r}
plot(mean_temp ~ tod_h, data = p %>%
       filter(species == "TRES"))
```

So now provisioning and temp actually both line up in a way that seems reasonable. Yay!



## Plot raw data for TRES

```{r}
(pl <- ggplot(data = p %>% filter(!is.na(habitat),species == "TRES"),aes(x = mean_temp,y = valid_detections,color = habitat)) +
   geom_point() +
   facet_wrap(~ habitat,ncol = 2) +
   theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))
)
```

Looks like way higher average detection for TRES. I'm a little worried that TRES data is inflated because they are much more likely to sit in the hole of the nest. I think I would have to build another classification model to identify those videos, though it would certainly be possible.

## First task: Figure out what distribution to use for modeling these data.

```{r}
hist(p %>% filter(species == "TRES") %>% pull(valid_detections))
```

This looks like a Poisson distribution would be overdispersed. But I'll run through all of the other distributions for completeness.


## Base model with Gaussian distribution, qqplot

```{r}
m <- lmer(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 # family = poisson,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
# pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)

```


## Base model with Poisson distribution, qqplot

```{r}
m <- glmer(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = poisson,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
# pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)

qqnorm(resid(m))
qqline(resid(m))
check_collinearity(m)
check_model(m, panel = FALSE)




```

## Test for overdispersion

```{r}
get_gof(m)

check_overdispersion(m)
check_zeroinflation(m)
```

So, we do have overdispersion and zero inflation.


## Let's try binomial distribution

```{r}
m <- glmer(cbind(valid_detections,max(valid_detections,na.rm = TRUE)-valid_detections) ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = binomial,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
```
Dispersion ratio is accounted for, but model doesn't converge- probably the zero inflation.

## Negative binomial

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 #ziformula = ~ poly(tod_h_scaled,2,raw = TRUE),
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
hist(simulate_residuals(m))
```


Negative binomial seems to address overdispersion and help with zeroinflation. If we add a zeroinflation term, what happens?

## Zero inflation model (~1)

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              #valid_detections < 60,
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
check_residuals(m)

```

---


```{r}
plot(simulate_residuals(m)%>% residuals() ~ fitted(m))
hist(simulate_residuals(m))
```

Test for overdispersion and zeroinflation are negative, and residuals seem uniformly distributed. Are we good to go?


## Provisioning ~ heat * habitat, TRES, forest

Squared term is not supported.

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq temp"),.before = Df) %>% gt()
summary(sqtemp)
```

---

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

This seems okay, but the errors are huge.

## Provisioning ~ heat * habitat, TRES, orchard

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id),
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id),
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

---

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

Just very few data points.

## Provisioning ~ heat * habitat, TRES, grassland

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

This seems oddly high.

## Provisioning ~ heat * habitat, TRES, row crop

Squared term is supported.

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod_h >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_h_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_h_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(sqtemp)
```

```{r}
(pl <- ggpredict(sqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(sqtemp)))
   )
```

## Conclusions

Squared temp is important in row crop. Is it important to the whole model?

```{r, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq temp |
|--------------|:-------:|
| Forest       |         |
| Orchard      |         |
| Grassland    |         |
| Row crop     | *       |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## Squared temp vs no squared temp, full model

It appears to not be important overall.

```{r}
sq <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
nosq <- glmmTMB(valid_detections ~ mean_temp_scaled * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_h_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sq,nosq) %>% tibble() %>% mutate(model = c("no sq","sq temp"),.before = Df) %>% gt()
```




## Plot model fit for TRES

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod_h),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod_h,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

qqnorm(resid(m))
qqline(resid(m))
```

---

```{r}
qqnorm(simulate_residuals(m) %>% resid())
qqline(simulate_residuals(m) %>% resid())
```


---


```{r}
get_gof(m)
check_overdispersion(m)
check_zeroinflation(m)
check_residuals(m)
```

---

```{r}
hist(simulate_residuals(m))
```

---

```{r}
plot(simulate_residuals(m)%>% residuals() ~ fitted(m))
```

---

```{r}
plot(simulate_residuals(m)%>% residuals() ~ m$frame$mean_temp_scaled)
```

---

```{r}
plot(simulate_residuals(m) %>% resid() ~ m$frame$habitat)
```

---

### Plot with no squared terms

```{r}
(pl <- ggpredict(m,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
   facet_wrap(~ group,ncol = 2) +
   # theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 50, size = 5, label = paste("N =",nobs(m)))
   )
```

---

```{r}
summary(m)
```

### Plot with squared term included but not interacted

```{r}
(pl <- ggpredict(sq,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
   facet_wrap(~ group,ncol = 2) +
   # theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 50, size = 5, label = paste("N =",nobs(m)))
   )
```

---

```{r}
summary(sq)
```

## Overall conclusions:

Having the squared term in the model doesn't improve fit and increases the size of standard errors... I think 
