---
title: Interactive effect of temp and land use on nestling growth, nestling cort,
  and adult visitation rate
author: "Kit Lauck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
### make prez figures
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
require(gt)
library(glmmTMB)
library(dagitty)
library(ggdag)
library(ggplot2)
library(igraph)
library(tidyverse)
#library(performance)
# library(modelsummary)
library(car)
library(lme4)
# modelsummary::get_gof(my_model)
# performance::model_performance(my_model)
wmean <- read_rds("../data/wmean.rds")

g <- read_rds("../data/growth_and_provis.rds")
p <- read_rds("../data/provis_with_attempt_1h.rds") %>%
  mutate(year = year(date),
         year_fct = as.factor(year)) 


```

## What do the growth and cort models look like when we use the DAG to design the model?

```{r}
dag <- dagify(nestgrowth ~ s1_cort + nestcond + foodprovis + humidity + maxtemp + mintemp + attempt + nest_age,
            s1_cort ~ site + mother_s1 + habitat + foodprovis + humidity + maxtemp + mintemp + broodsize + nest_age,
            nestcond ~ s1_cort + foodprovis + broodsize,
            foodprovis ~ habitat + year + mother_s1 + site + humidity + maxtemp + mintemp + broodsize + nest_age,
            mother_s1 ~ site + maxtemp + mintemp + attempt + habitat  + jul_date + broodsize + humidity + year,
            maxtemp ~ year + habitat + jul_date + site + attempt,
            mintemp ~ year + habitat + jul_date + site + attempt,
            broodsize ~ jul_date + maxtemp + mintemp + humidity + site + year + attempt + habitat,
            humidity ~ maxtemp + mintemp + habitat + year + jul_date + site,
            # maxtemp ~~ mintemp,
            jul_date ~~ habitat,
            jul_date ~ site + year,
            attempt ~~ year,
            nest_age ~ attempt,
            site ~ year,
            exposure = c("maxtemp","habitat"),
            outcome = "nestgrowth"#,
            # latent = "attempt"#,
            # latent = "foodprovis"
            )

(plot <- ggdag_status(dag,layout = "nicely",node_size = 10) + 
  geom_dag_text(colour = "black") + theme_dag_blank() + geom_dag_edges())  # Ensure node label text is black
```

--- 

- For outcome = growth, and exposure = all four focal variables

A canonical adjustment set does not exist when exposure is all four focal variables. Does this mean I'll need to break up the SEM?

```{r}
adjSet_canon <- adjustmentSets(dag,type = 'canonical',outcome = c("nestgrowth"),exposure = c("habitat","maxtemp","foodprovis","s1_cort"))
adjSet_minimal <- adjustmentSets(dag,outcome = c("nestgrowth"),exposure = c("habitat","maxtemp","foodprovis","s1_cort"))
print(adjSet_minimal)
print(adjSet_canon)
```

---

- For outcome = growth, and exposure = habitat and max temp

```{r}
adjSet_canon <- adjustmentSets(dag,type = 'canonical',outcome = c("nestgrowth"),exposure = c("habitat","maxtemp"))

print(adjSet_canon)
```

- For outcome = cort, and exposure = habitat and max temp

```{r}
adjSet_canon <- adjustmentSets(dag,type = 'canonical',outcome = c("s1_cort"),exposure = c("habitat","maxtemp"))

print(adjSet_canon)
```


- For outcome = provis, and exposure = habitat and max temp

```{r}
adjSet_canon <- adjustmentSets(dag,type = 'canonical',outcome = c("foodprovis"),exposure = c("habitat","maxtemp"))

print(adjSet_canon)
```

It looks like all three of these outcomes need the same covariates in the model. This makes sense to me, if foodprovis and cort are bound together the way we think they are. Would appreciate any thoughts/feedback on this DAG or idea.

## Do we need squared temp in the model?

- I am thinking no: go over my notes
- Land uses plotted individually with and without squared terms
- Like with NestWatch paper, compare individual land use models with and without squared terms.

I wasn't sure where to start with this part: with new model determined by DAG or with old model so we have some reference to the previous fit. So I started with the old model and then replicated for the new model to compare.

## growth ~ temp * habitat: WEBL

Original model with min temp (support in danny_meeting_20240213):

lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

Updated model based on DAG above:

lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

## Raw growth by temp and habitat, for referencing while looking at the modeling results

```{r}
(plot <- ggplot(data = g %>% filter(Species == "WEBL"),mapping = aes(x = meanmaxtempI, y = gweight, color = habitat)) +
  geom_point() +
    theme_classic() +
   facet_wrap(~ habitat,ncol = 2) +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))# +
    #annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)
```


## Growth across temp and habitat: WEBL, forest {.smaller}

For original model with min temp:

```{r}
meanI_WEBL_sq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nomaxsq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nominsq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_forest,meanI_WEBL_nominsq_forest,meanI_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_WEBL_sq_forest,meanI_WEBL_nomaxsq_forest,meanI_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_WEBL_nosq_forest)
```

Essentially, it looks like min and max function interchangeably, more or less. Neither adds much to the fit for forest.

---

```{r}
(plot <- ggpredict(meanI_WEBL_nosq_forest,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq_forest)))
)

```


## Growth across temp and habitat: WEBL, forest {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
meanI_WEBL_sq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_forest,meanI_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(meanI_WEBL_nosq_forest)
```

---

```{r}
(plot <- ggpredict(meanI_WEBL_nosq_forest,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq_forest)))
)

```


## Predicted growth across temp and habitat: WEBL, orchard {.smaller}

For original model with min temp:

```{r}
meanI_WEBL_sq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nomaxsq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nominsq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_orchard,meanI_WEBL_nominsq_orchard,meanI_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_WEBL_sq_orchard,meanI_WEBL_nomaxsq_orchard,meanI_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_WEBL_nosq_orchard)
```

Similar story for orchard as for forest.

---

```{r}
(plot <- ggpredict(meanI_WEBL_nosq_orchard,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq_orchard)))
)

```

## Predicted growth across temp and habitat: WEBL, orchard {.smaller}

For updated model based on DAG, squared max temp does not add much:


```{r}
meanI_WEBL_sq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_orchard,meanI_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()
summary(meanI_WEBL_nosq_orchard)
```

---

```{r}
(plot <- ggpredict(meanI_WEBL_nosq_orchard,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq_orchard)))
)

```

## Predicted growth across temp and habitat: WEBL, grassland {.smaller}

For original model with min temp, squared min temp helps:

```{r}
meanI_WEBL_sq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nomaxsq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nominsq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_grass,meanI_WEBL_nominsq_grass,meanI_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_WEBL_sq_grass,meanI_WEBL_nomaxsq_grass,meanI_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_WEBL_nomaxsq_grass)
```


Adding squared min when you already have squared max does add some fit, but adding squared max when you have squared min does not add fit. So the squared min term is more important in grassland than the squared max term.

---

```{r}
(plot <- ggpredict(meanI_WEBL_nomaxsq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nomaxsq_grass)))
)

```

## Predicted growth across temp and habitat: WEBL, grassland {.smaller}

For updated model based on DAG, squared term helps fit:


```{r}
meanI_WEBL_sq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_grass,meanI_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()
summary(meanI_WEBL_sq_grass)
```

---

```{r}
(plot <- ggpredict(meanI_WEBL_sq_grass,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_sq_grass)))
)

```

## Predicted growth across temp and habitat: WEBL, row crop {.smaller}

For original model with min temp:

```{r}
meanI_WEBL_sq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nomaxsq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nominsq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_rc,meanI_WEBL_nominsq_rc,meanI_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_WEBL_sq_rc,meanI_WEBL_nomaxsq_rc,meanI_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_WEBL_nomaxsq_rc)
```

Squared min helps fit, but squared max does not appear to help fit

---

```{r}
(plot <- ggpredict(meanI_WEBL_nomaxsq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nomaxsq_rc)))
)

```

## Predicted growth across temp and habitat: WEBL, row crop {.smaller}


For updated model based on DAG, squared term is not supported:


```{r}
meanI_WEBL_sq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_nosq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_WEBL_sq_rc,meanI_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(meanI_WEBL_nosq_rc)
```

---

```{r}
(plot <- ggpredict(meanI_WEBL_nosq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq_rc)))
)

```

## Conclusions

Squared min temp (but not squared max temp) is important in grassland and row crop with the original model, and squared max temp is important in grassland with the updated model. Can we decide to not use squared max temp for WEBL?

```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       |               |               |                 |
| Orchard      |               |               |                 |
| Grassland    |               | *             | *               |
| Row crop     |               | *             |                 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


## Revisiting growth ~ temp * habitat: TRES

Original model (support in danny_meeting_20240213):

lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

Updated model:

lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

## Raw growth by temp and habitat, for referencing while looking at the modeling results

```{r}
(plot <- ggplot(data = g %>% filter(Species == "TRES"),mapping = aes(x = meanmaxtempI, y = gweight, color = habitat)) +
  geom_point() +
    theme_classic() +
   facet_wrap(~ habitat,ncol = 2) +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))# +
    #annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)
```


## Growth across temp and habitat: TRES, forest {.smaller}

For original model with min temp:

```{r}
meanI_TRES_sq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nomaxsq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nominsq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_forest,meanI_TRES_nominsq_forest,meanI_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_TRES_sq_forest,meanI_TRES_nomaxsq_forest,meanI_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_TRES_nominsq_forest)
```

For TRES in forest, it looks like squared max is more important than squared min. But looking at the graph, I'm suspecting this model is overfit to forest.

---

```{r}
(plot <- ggpredict(meanI_TRES_nominsq_forest,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nominsq_forest)))
)

```


## Growth across temp and habitat: TRES, forest {.smaller}

For updated model based on DAG, squared temp is supported, but again, I'm suspecting some overfitting here.


```{r}
meanI_TRES_sq_forest <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_forest <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_forest,meanI_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(meanI_TRES_sq_forest)
```

---

```{r}
(plot <- ggpredict(meanI_TRES_sq_forest,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nosq_forest)))
)

```


## Predicted growth across temp and habitat: TRES, orchard {.smaller}

For original model with min temp:

```{r}
meanI_TRES_sq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nomaxsq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nominsq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_orchard,meanI_TRES_nominsq_orchard,meanI_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_TRES_sq_orchard,meanI_TRES_nomaxsq_orchard,meanI_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_TRES_nominsq_orchard)
```

Similar story for orchard as for forest: max is more important than min, but this looks overfit to me.

---

```{r}
(plot <- ggpredict(meanI_TRES_nominsq_orchard,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nominsq_orchard)))
)

```

## Predicted growth across temp and habitat: TRES, orchard {.smaller}

For updated model based on DAG, squared max temp does not add to the fit:


```{r}
meanI_TRES_sq_orchard <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_orchard <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_orchard,meanI_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()
summary(meanI_TRES_nosq_orchard)
```

---

```{r}
(plot <- ggpredict(meanI_TRES_nosq_orchard,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nosq_orchard)))
)

```

## Predicted growth across temp and habitat: TRES, grassland {.smaller}

For original model with min temp, squared min temp helps:

```{r}
meanI_TRES_sq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nomaxsq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nominsq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_grass,meanI_TRES_nominsq_grass,meanI_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_TRES_sq_grass,meanI_TRES_nomaxsq_grass,meanI_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_TRES_nomaxsq_grass)
```


Adding squared min when you already have squared max does add some fit, but adding squared max when you have squared min does not add fit. So the squared min term is more important in grassland than the squared max term.

---

```{r}
(plot <- ggpredict(meanI_TRES_nomaxsq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nomaxsq_grass)))
)

```

## Predicted growth across temp and habitat: TRES, grassland {.smaller}

For updated model based on DAG, squared term also does not help fit:


```{r}
meanI_TRES_sq_grass <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_grass <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_grass,meanI_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()
summary(meanI_TRES_nosq_grass)
```

---

```{r}
(plot <- ggpredict(meanI_TRES_nosq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nosq_grass)))
)

```

## Predicted growth across temp and habitat: TRES, row crop {.smaller}

For original model with min temp:

```{r}
meanI_TRES_sq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nomaxsq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nominsq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_rc,meanI_TRES_nominsq_rc,meanI_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(meanI_TRES_sq_rc,meanI_TRES_nomaxsq_rc,meanI_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(meanI_TRES_nomaxsq_rc)
```

Squared min is more important than squared max for fit, but when squared max is added to squared min, it's marginally significantly better?

---

```{r}
(plot <- ggpredict(meanI_TRES_nomaxsq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nomaxsq_rc)))
)

```

## Predicted growth across temp and habitat: TRES, row crop {.smaller}


For updated model based on DAG, squared term is supported:


```{r}
meanI_TRES_sq_rc <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_nosq_rc <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(meanI_TRES_sq_rc,meanI_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(meanI_TRES_sq_rc)
```

---

```{r}
(plot <- ggpredict(meanI_TRES_sq_rc,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_sq_rc)))
)

```

## Conclusions

Squared max temp (but not min temp) is important in forest and orchard with the original model, and squared min temp is important in grassland and row crop. For the updated model, squared max temp is important in forest, orchard, and row crop, but it looks really overfit in forest and orchard. I'm less convinced that we don't need a squared term for TRES?

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       | *             |               | *               |
| Orchard      | *             |               | *               |
| Grassland    |               | *             |                 |
| Row crop     |               | *             | *               |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## Revisiting nestling cort ~ temp * habitat: WEBL

Base model:

cort_meanI_WEBL <- log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Inferential model cort ~ temp * habitat (WEBL):

log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Updated model: log(cort_s1) ~ poly(meanmaxtempI_scaled,2) * habitat + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

## Raw cort by temp and habitat, for referencing while looking at the modeling results

```{r}
(plot <- ggplot(data = g %>% filter(Species == "WEBL"),mapping = aes(x = meanmaxtempI, y = log(cort_s1), color = habitat)) +
  geom_point() +
    theme_classic() +
   facet_wrap(~ habitat,ncol = 2) +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))# +
    #annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)
```


## Cort across temp and habitat: WEBL, forest {.smaller}

For original model with min temp:

```{r}
cort_WEBL_sq_forest <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nomaxsq_forest <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nominsq_forest <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nosq_forest <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_WEBL_sq_forest,cort_WEBL_nominsq_forest,cort_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_WEBL_sq_forest,cort_WEBL_nomaxsq_forest,cort_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_WEBL_nosq_forest)
```

Neither squared temp term adds much to this fit.

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_forest,terms = c("meanmaxtempI_scaled"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_forest)))
)

```


## Cort across temp and habitat: WEBL, forest {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
cort_WEBL_sq_forest <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_WEBL_nosq_forest <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_WEBL_sq_forest,cort_WEBL_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_WEBL_nosq_forest)
```

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_forest,terms = c("meanmaxtempI_scaled"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_forest)))
)

```


## Cort across temp and habitat: WEBL, orchard {.smaller}

For original model with min temp:

```{r}
cort_WEBL_sq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nomaxsq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nominsq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nosq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_WEBL_sq_orchard,cort_WEBL_nominsq_orchard,cort_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_WEBL_sq_orchard,cort_WEBL_nomaxsq_orchard,cort_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_WEBL_sq_orchard)
```

Neither squared term contributes much to this fit.

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_orchard,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_orchard)))
)

```


## Cort across temp and habitat: WEBL, orchard {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
cort_WEBL_sq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_WEBL_nosq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_WEBL_sq_orchard,cort_WEBL_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_WEBL_nosq_orchard)
```

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_orchard,terms = c("meanmaxtempI_scaled"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_orchard)))
)

```

## Cort across temp and habitat: WEBL, grass {.smaller}

For original model with min temp:

```{r}
cort_WEBL_sq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nomaxsq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nominsq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nosq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_WEBL_sq_grass,cort_WEBL_nominsq_grass,cort_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_WEBL_sq_grass,cort_WEBL_nomaxsq_grass,cort_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_WEBL_sq_grass)
```

Max temp contributes to this fit. I dunno, this looks overfit to me.

---

```{r}
(plot <- ggpredict(cort_WEBL_nominsq_grass,terms = c("meanmaxtempI_scaled [all]")) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nominsq_grass)))
)

```


## Cort across temp and habitat: WEBL, grass {.smaller}

For updated model based on DAG, squared temp is marginally supported:


```{r}
cort_WEBL_sq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_WEBL_nosq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_WEBL_sq_grass,cort_WEBL_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_WEBL_sq_grass)
```

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_grass)))
)

```

## Cort across temp and habitat: WEBL, rc {.smaller}

For original model with min temp:

```{r}
cort_WEBL_sq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nomaxsq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nominsq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_WEBL_nosq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_WEBL_sq_rc,cort_WEBL_nominsq_rc,cort_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_WEBL_sq_rc,cort_WEBL_nomaxsq_rc,cort_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_WEBL_sq_rc)
```

Squared min temp contributes to this fit, but I don't think it really fits the data very well. May be a case of "getting the priors back"

---

```{r}
(plot <- ggpredict(cort_WEBL_nomaxsq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nomaxsq_rc)))
)

```


## Cort across temp and habitat: WEBL, rc {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
cort_WEBL_sq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_WEBL_nosq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "WEBL",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_WEBL_sq_rc,cort_WEBL_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_WEBL_nosq_rc)
```

---

```{r}
(plot <- ggpredict(cort_WEBL_nosq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_WEBL_nosq_rc)))
)

```

## Conclusions

Some concerns with overfitting

```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       |               |               |                 |
| Orchard      |               |               |                 |
| Grassland    | *             |               | *               |
| Row crop     |               | *             |                 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```



## Revisiting nestling cort ~ temp * habitat: TRES

Base model:

cort_meanI_TRES <- log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Inferential model cort ~ temp * habitat (TRES):

log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Updated model: log(cort_s1) ~ poly(meanmaxtempI_scaled,2) * habitat + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)


## Raw cort by temp and habitat, for referencing while looking at the modeling results

```{r}
(plot <- ggplot(data = g %>% filter(Species == "TRES"),mapping = aes(x = meanmaxtempI, y = cort_s1, color = habitat)) +
  geom_point() +
    theme_classic() +
   facet_wrap(~ habitat,ncol = 2) +
    xlab("Max temperature (\u00B0C)") +
    ylab("baseline cort") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))# +
    #annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_TRES_nosq)))
)
```


## Cort across temp and habitat: TRES, forest {.smaller}

For original model with min temp:

```{r}
cort_TRES_sq_forest <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nomaxsq_forest <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nominsq_forest <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nosq_forest <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Forest",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_TRES_sq_forest,cort_TRES_nominsq_forest,cort_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_TRES_sq_forest,cort_TRES_nomaxsq_forest,cort_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_TRES_nosq_forest)
```

Yikes, not sure which term is responsible, but I think I just don't have enough data here to estimate anything.

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_forest,terms = c("meanmaxtempI_scaled"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nosq_forest)))
)

```


## Cort across temp and habitat: TRES, forest {.smaller}

For updated model based on DAG, squared temp is supported, but the model is super over fit and looks awful:


```{r}
cort_TRES_sq_forest <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_TRES_nosq_forest <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Forest",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_TRES_sq_forest,cort_TRES_nosq_forest) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_TRES_sq_forest)
```

---

```{r}
(plot <- ggpredict(cort_TRES_sq_forest,terms = c("meanmaxtempI_scaled [all]"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_sq_forest)))
)

```


## Cort across temp and habitat: TRES, orchard {.smaller}

For original model with min temp:

```{r}
cort_TRES_sq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nomaxsq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nominsq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nosq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Orchard",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_TRES_sq_orchard,cort_TRES_nominsq_orchard,cort_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_TRES_sq_orchard,cort_TRES_nomaxsq_orchard,cort_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_TRES_sq_orchard)
```

Same problem as for forest

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_orchard,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nosq_orchard)))
)

```


## Cort across temp and habitat: TRES, orchard {.smaller}

For updated model based on DAG, squared temp is supported, but my guess is also that this is way overfit to too few data:


```{r}
cort_TRES_sq_orchard <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_TRES_nosq_orchard <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Orchard",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_TRES_sq_orchard,cort_TRES_nosq_orchard) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_TRES_nosq_orchard)
```

---

```{r}
(plot <- ggpredict(cort_TRES_sq_orchard,terms = c("meanmaxtempI_scaled [all]"),back_transform = FALSE) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_sq_orchard)))
)

```

## Cort across temp and habitat: TRES, grass {.smaller}

For original model with min temp:

```{r}
cort_TRES_sq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nomaxsq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nominsq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nosq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Grassland",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_TRES_sq_grass,cort_TRES_nominsq_grass,cort_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_TRES_sq_grass,cort_TRES_nomaxsq_grass,cort_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_TRES_nosq_grass)
```

Neither term contributes to this fit.

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nominsq_grass)))
)

```


## Cort across temp and habitat: TRES, grass {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
cort_TRES_sq_grass <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_TRES_nosq_grass <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Grassland",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_TRES_sq_grass,cort_TRES_nosq_grass) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_TRES_sq_grass)
```

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_grass,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nosq_grass)))
)

```

## Cort across temp and habitat: TRES, rc {.smaller}

For original model with min temp:

```{r}
cort_TRES_sq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nomaxsq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nominsq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + meanmintempI_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_TRES_nosq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + meanmintempI_scaled + meanmaxtempI_scaled * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,habitat == "Row crop",Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))




anova(cort_TRES_sq_rc,cort_TRES_nominsq_rc,cort_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no min sq","sq max and min"),.before = npar) %>% gt()

anova(cort_TRES_sq_rc,cort_TRES_nomaxsq_rc,cort_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","no max sq","sq max and min"),.before = npar) %>% gt()

summary(cort_TRES_sq_rc)
```

Neither squared term contributes much to this fit.

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nosq_rc)))
)

```


## Cort across temp and habitat: TRES, rc {.smaller}

For updated model based on DAG, squared temp is not supported:


```{r}
cort_TRES_sq_rc <- lmerTest::lmer(cort_s1_scaled ~ poly(meanmaxtempI_scaled,2) + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

cort_TRES_nosq_rc <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,habitat == "Row crop",Species == "TRES",!is.na(meanmaxtempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,cort_s1),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


anova(cort_TRES_sq_rc,cort_TRES_nosq_rc) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = npar) %>% gt()

summary(cort_TRES_nosq_rc)
```

---

```{r}
(plot <- ggpredict(cort_TRES_nosq_rc,terms = c("meanmaxtempI_scaled")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE,facets = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("log baseline cort") +
    #labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
  #                      ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       # ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(cort_TRES_nosq_rc)))
)

```

## Conclusions

I have concerns with overfitting in forest and orchard (too few data), but I think we can safely leave squared terms out of this model

```{r table4, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       | NA            | NA            | *               |
| Orchard      | NA            | NA            | *               |
| Grassland    |               |               |                 |
| Row crop     |               |               |                 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## New data! Provisioning ~ temp * habitat: WEBL

Used DAG version 3 in code/dag.Rmd to support model. Below model is canonical adjustment set given outcome = food provisioning and exposure = temp and habitat

Base model: provis ~ temp^2 * habitat + julian_date + nest_age + time_of_day^2 + 1|attempt_id + 1|year

Note: The model was not able to handle the nested random effect of site/attempt_id, so I figured attempt_id could soak up some of that variation and was the more important one. Should I also add folder as a random effect? That could soak up some of the sampling error (some cameras worked better than others, or had slightly different operation)

I have re-aggregated the results to 1 hr, hopefully eliminating the need for a zero-inflated model. There are still zero counts, so hopefully we can discuss how to find out if I still need a zero-inflated model.

Need to answer two questions:
- Is the interaction of temp and habitat significant?
- Is the second-order term of max temp significant?

In this presentation, I will take a different tack than before: separating across habitats and looking at fit and squared terms individually. But first, let's see if a poisson distribution fits the count data. Another option would be a binomial distribution since theoretically birds can't visit their nests an infinite number of times in an hour.


## Provis by time of day: WEBL

```{r}
plot(valid_detections ~ tod_hours, data = p %>% mutate(tod_hours = as.numeric(tod)/3600) %>%
       filter(species == "WEBL"))
```

## Provis by time of day: TRES

```{r}
plot(valid_detections ~ tod_hours, data = p %>% mutate(tod_hours = as.numeric(tod)/3600) %>%
       filter(species == "TRES"))
```


## Histogram of provis 

```{r}
hist(p$valid_detections)
```

This looks like a poisson distribution would do okay here?


## Base model with poisson distribution

```{r}
m <- glmer(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = poisson,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
m %>% vif()
pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)

```

This looks like it does not adequately fit the data.

## Let's try binomial distribution!

```{r}
m <- glmer(cbind(valid_detections,max(valid_detections,na.rm = TRUE)-valid_detections) ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + year_fct,
						 # ziformula = ~1,
						 family = binomial,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)
```
This ran but also doesn't look like it fits the data well. We may have to use zero inflation after all.

## Let's try zero inflation!

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + year_fct,
						 ziformula = ~ poly(tod_scaled,2,raw = TRUE),
						 family = nbinom2(),
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()
pchisq(summary(m)$AICtab["deviance"], summary(m)$AICtab["df.resid"],lower.tail=FALSE)
```

That also doesn't fit! yikes. Not sure what to do about this. I guess I have to start adding predictors to the zero dispersion??

I tried a few predictors but did not manage to find a zero inflation factor that helps this model fit a little bit better. Hope we can figure this out! For now I'm going to go with the glmmTMB model because it's most complicated so I'll work through all the potential problems on the way.

## Plot raw data for WEBL

```{r}
(pl <- ggplot(data = p %>% filter(!is.na(habitat),species == "WEBL"),aes(x = mean_temp,y = valid_detections,color = habitat)) +
   geom_point() +
   facet_wrap(~ habitat,ncol = 2) +
   theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))
)
```


## Provisioning ~ heat * habitat, WEBL, forest

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Provisioning ~ heat * habitat, WEBL, orchard

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Provisioning ~ heat * habitat, WEBL, grassland

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Provisioning ~ heat * habitat, WEBL, row crop

Squared term is supported! Woww

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(sqtemp)
```

```{r}
(pl <- ggpredict(sqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "WEBL") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(sqtemp)))
   )
```

## Conclusions

Squared temp is important in row crop. Let's discuss!

```{r table5, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       | NA            | NA            |                 |
| Orchard      | NA            | NA            |                 |
| Grassland    | NA            | NA            |                 |
| Row crop     | NA            | NA            | *               |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## Plot raw data for TRES

```{r}
(pl <- ggplot(data = p %>% filter(!is.na(habitat),species == "TRES"),aes(x = mean_temp,y = valid_detections,color = habitat)) +
   geom_point() +
   facet_wrap(~ habitat,ncol = 2) +
   theme_classic() +
    xlab("Average hourly temp") +
    ylab("Nest visits per hour") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))
)
```


## Provisioning ~ heat * habitat, TRES, forest

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Forest",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp)  %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Provisioning ~ heat * habitat, TRES, orchard

Squared term supported - but looks overfit to me?

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Orchard",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp)  %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(sqtemp)
```

```{r}
(pl <- ggpredict(sqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(sqtemp)))
   )
```

## Provisioning ~ heat * habitat, TRES, grassland

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Grassland",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp) %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Provisioning ~ heat * habitat, TRES, row crop

Squared term not supported

```{r}
sqtemp <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2,raw = TRUE) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

nosqtemp <- glmmTMB(valid_detections ~ mean_temp_scaled + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2,raw = TRUE) + (1|attempt_id) + year_fct,
						 ziformula = ~ 1,
						 family = nbinom2(),
					data = dplyr::filter(p,habitat == "Row crop",!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

anova(sqtemp,nosqtemp)  %>% tibble() %>% mutate(model = c("no sq","sq max temp"),.before = Df) %>% gt()
summary(nosqtemp)
```

```{r}
(pl <- ggpredict(nosqtemp,terms = c("mean_temp_scaled [all]"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 60 mins") +
    ylab("Visits/60 mins") +
    labs(title = "TRES") +
   ylim(0,100) +
   annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(nosqtemp)))
   )
```

## Conclusions

Squared temp is important in none of these models, but I do like the fit to the data better than I did before.

```{r table6, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Habitat      | Sq max (orig) | Sq min (orig) | Sq max (update) |
|--------------|:-------------:|:-------------:|:---------------:|
| Forest       | NA            | NA            |                 |
| Orchard      | NA            | NA            |                 |
| Grassland    | NA            | NA            |                 |
| Row crop     | NA            | NA            |                 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


