---
title: Interactive effect of temp and land use on nestling growth, nestling cort,
  and adult visitation rate
author: "Kit Lauck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
### make prez figures
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
require(gt)
library(glmmTMB)
wmean <- read_rds("../data/wmean.rds")

g <- read_rds("../data/growth_and_provis.rds")
p <- read_rds("../data/provis_with_attempt.rds") %>%
  mutate(year = year(date))


```

## Revisiting growth ~ temp * habitat: WEBL

Inferential model (support in danny_meeting_20240213):

lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

Data wrangling: 

dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI)) %>% mutate(across(c(gweight, meanmaxtempI, meanmintempI, juliandate, brood_size), ~ scale(.x)[,1],.names = "{.col}_scaled"),
meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

## Predicted growth across temp and habitat: WEBL {.smaller}

```{r}
meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
mean_temp <- mean(dplyr::filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(dplyr::filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(dplyr::filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(dplyr::filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(plot <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)
```

## Raw growth across max temp: WEBL {.smaller}

```{r}

(plot <- ggplot(dplyr::filter(g,Species == "WEBL"),aes(x = meanmaxtempI,y = gweight)) +
 	geom_point() +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL) +
    theme(text = element_text(size = 16)) +
    annotate("text", x = 22, y = 2.8,size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)
```


## Revisiting growth ~ temp * habitat: TRES

Inferential model (support in danny_meeting_20240213):

lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id))

Data wrangling: 

dplyr::filter(g,Species == "TRES", !is.na(meanmaxtempI)) %>% dplyr::filter(meanmaxtempI < 45) %>% mutate(across(c(gweight, meanmaxtempI, meanmintempI, juliandate, brood_size),  ~ scale(.x)[,1], .names = "{.col}_scaled"), meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

## Predicted growth across temp and habitat: TRES {.smaller}

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               dplyr::filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
mean_temp <- mean(dplyr::filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(dplyr::filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(dplyr::filter(g,Species == "TRES") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(dplyr::filter(g,Species=="TRES") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})


(plot <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,5)
                       ) +
    annotate("text", x = -2.35, y = 4.9, size = 5, label = paste("N =",nobs(meanI_TRES_nosq)))
)
```


## Raw growth across max temp: TRES {.smaller}

```{r}

(plot <- ggplot(dplyr::filter(g,Species == "TRES"),aes(x = meanmaxtempI,y = gweight)) +
 	geom_point() +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = NULL) +
    theme(text = element_text(size = 16)) +
    annotate("text", x = 25, y = 2.8,size = 5, label = paste("N =",nobs(meanI_TRES_nosq)))
)
```

## Revisiting nestling cort ~ temp * habitat: WEBL

<!-- C:/Users/kathe/projects/nestbox-temp-monitoring/code/cort_analyses_D&P.Rmd to source base models. Need to go through process used for growth models to find out which model structure is supported. -->

Base model:

cort_meanI_WEBL <- log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Need to answer two questions:
- Is the interaction of temp and habitat significant?
- Is the second-order term of max temp significant?

## Is interaction significant? (WEBL) {.smaller}

Models:

- no int: log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- linear int: log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- squared int: log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_poly_WEBL <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_meanI_linear_WEBL <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_meanI_noint_WEBL <- lmerTest::lmer(log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

anova(cort_meanI_poly_WEBL,cort_meanI_linear_WEBL,cort_meanI_noint_WEBL) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

## Is squared term significant? (WEBL) {.smaller}

Models:

- no squared term: log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- no temp term: log(cort_s1) ~ habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- squared int: log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_nosq_WEBL <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,1,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))
cort_meanI_notemp_WEBL <- lmerTest::lmer(log(cort_s1) ~ habitat + poly(meanmintempI_scaled,2) * habitat + meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))
anova(cort_meanI_linear_WEBL,cort_meanI_nosq_WEBL,cort_meanI_notemp_WEBL) %>% tibble() %>% mutate(model = c("no temp","no squared term","sq int"),.before = npar) %>% gt()
```

Note to Danny: I'm not sure whether I should have removed the squared temp interaction with humidity or not.

## Inferential model cort ~ temp * habitat (WEBL) {.smaller}

log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_linear_WEBL <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

t <- summary(cort_meanI_linear_WEBL) %>% coef()
predict <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = predict, .before = Estimate) %>% tibble() %>%
  dplyr::select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(4))
```

---

```{r}

mean_temp <- mean(dplyr::filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(dplyr::filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})


(plot <- ggpredict(cort_meanI_linear_WEBL,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling blood corticosterone concentration") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,5)
  #                      ) +
    ylim(0,20) + 
    annotate("text", x = -2.35, y = 4.9, size = 5, label = paste("N =",nobs(cort_meanI_nosq_WEBL)))
)
```


## Revisiting nestling cort ~ temp * habitat: TRES

<!-- C:/Users/kathe/projects/nestbox-temp-monitoring/code/cort_analyses_D&P.Rmd to source base models. Need to go through process used for growth models to find out which model structure is supported. -->

Base model:

cort_meanI_TRES <- log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

Need to answer two questions:
- Is the interaction of temp and habitat significant?
- Is the second-order term of max temp significant?

## Is interaction significant? (TRES) {.smaller}

Models:

- no int: log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- linear int: log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- squared int: log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_poly_TRES <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_meanI_linear_TRES <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

cort_meanI_noint_TRES <- lmerTest::lmer(log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

anova(cort_meanI_poly_TRES,cort_meanI_linear_TRES,cort_meanI_noint_TRES) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

## Is squared term significant? (TRES) {.smaller}

Models:

- no squared term: log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- no temp term: log(cort_s1) ~ habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)
- squared int: log(cort_s1) ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_nosq_TRES <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,1,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))
cort_meanI_notemp_TRES <- lmerTest::lmer(log(cort_s1) ~ habitat + poly(meanmintempI_scaled,2) * habitat + meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))
anova(cort_meanI_poly_TRES,cort_meanI_nosq_TRES,cort_meanI_notemp_TRES) %>% tibble() %>% mutate(model = c("no temp","no squared term","sq int"),.before = npar) %>% gt()
```

Note to Danny: I'm not sure whether I should have removed the squared temp interaction with humidity or not.

## Inferential model cort ~ temp * habitat (TRES) {.smaller}

log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id)

```{r}
cort_meanI_noint_TRES <- lmerTest::lmer(log(cort_s1) ~ habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (dplyr::filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

t <- summary(cort_meanI_noint_TRES) %>% coef()
predict <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = predict, .before = Estimate) %>% tibble() %>%
  dplyr::select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(4))
```

---

```{r}

mean_temp <- mean(dplyr::filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(dplyr::filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})


(plot <- ggpredict(cort_meanI_noint_TRES,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling blood corticosterone concentration") +
    labs(title = NULL,color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,5)
  #                      ) +
    #ylim(0,20) + 
    annotate("text", x = 1, y = 25, size = 5, label = paste("N =",nobs(cort_meanI_nosq_TRES)))
)
```

## New data! Provisioning ~ temp * habitat: WEBL

Used DAG version 3 in code/dag.Rmd to support model. Below model is canonical adjustment set given outcome = food provisioning and exposure = temp and habitat

Base model: provis ~ temp^2 * habitat + julian_date + nest_age + time_of_day^2 + 1|attempt_id + 1|year

Note: The model was not able to handle the nested random effect of site/attempt_id, so I figured attempt_id could soak up some of that variation and was the more important one. Should I also add folder as a random effect? That could soak up some of the sampling error (some cameras worked better than others, or had slightly different operation)

Need to answer two questions:
- Is the interaction of temp and habitat significant?
- Is the second-order term of max temp significant?

## Graphing base model (WEBL)

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()

# (tod <- ggpredict(m,terms = c("tod_scaled [all]"),bias_correction = TRUE) %>% 
# 		plot(line_size = 1.5,alpha = .2,show_data = FALSE) +
#     theme_classic() +
#     xlab("Time of day") +
#     ylab("Visits/30 mins") +
#     labs(title = "WEBL") +
#    #ggtitle("Predicted growth across habitat and mean max daily temp") +
#     #theme(text = element_text(size = 16)) +
#     # scale_x_continuous(trans = temp_trans,
#     #                    breaks = c((20-mean_temp)/sd_temp,
#     #                               (30-mean_temp)/sd_temp,
#     #                               (40-mean_temp)/sd_temp,
#     #                               (50-mean_temp)/sd_temp),
#     #                    # breaks = c(20,30,40,50),
#     #                    # labels = c("20","30","40","50"),
#     #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
#     #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
#     #                    # limits = c(18,5)
#     #                    ) +
#   # scale_y_continuous(trans = growth_trans,
#   #                      breaks = c((-2-mean_growth)/sd_growth,
#   #                        (0-mean_growth)/sd_growth,
#   #                        (2-mean_growth)/sd_growth,
#   #                        (4-mean_growth)/sd_growth),
#   #                      # breaks = c(0,1,2,3,4),
#   #                      # labels = c("-2","0","2","4"),
#   #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
#   #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
#   #                      limits = c(-3,3)
#   #                      ) +
#     annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(m)))
# )
```

```{r}
(avg_temp <- ggpredict(m,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>% plot(line_size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Mean temp over 30 mins") +
    ylab("Visits/30 mins") +
    labs(title = "WEBL") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,3)
  #                      ) +
   ylim(0,25) +
    annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(m)))
)
```

## Graphing base model (TRES)

```{r}
m <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

# m %>% summary()
# m %>% vif()

# (tod <- ggpredict(m,terms = c("tod_scaled [all]"),bias_correction = TRUE) %>% 
# 		plot(line_size = 1.5,alpha = .2,show_data = FALSE) +
#     theme_classic() +
#     xlab("Time of day") +
#     ylab("Visits/30 mins") +
#     labs(title = "TRES") +
#    #ggtitle("Predicted growth across habitat and mean max daily temp") +
#     #theme(text = element_text(size = 16)) +
#     # scale_x_continuous(trans = temp_trans,
#     #                    breaks = c((20-mean_temp)/sd_temp,
#     #                               (30-mean_temp)/sd_temp,
#     #                               (40-mean_temp)/sd_temp,
#     #                               (50-mean_temp)/sd_temp),
#     #                    # breaks = c(20,30,40,50),
#     #                    # labels = c("20","30","40","50"),
#     #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
#     #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
#     #                    # limits = c(18,5)
#     #                    ) +
#   # scale_y_continuous(trans = growth_trans,
#   #                      breaks = c((-2-mean_growth)/sd_growth,
#   #                        (0-mean_growth)/sd_growth,
#   #                        (2-mean_growth)/sd_growth,
#   #                        (4-mean_growth)/sd_growth),
#   #                      # breaks = c(0,1,2,3,4),
#   #                      # labels = c("-2","0","2","4"),
#   #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
#   #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
#   #                      limits = c(-3,3)
#   #                      ) +
#     annotate("text", x = -1.5, y = 7, size = 5, label = paste("N =",nobs(m)))
# )
```

```{r}
(avg_temp <- ggpredict(m,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>% plot(line_size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Mean temp over 30 mins") +
    ylab("Visits/30 mins") +
    labs(title = "TRES") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,3)
  #                      ) +
    ylim(0,25) +
    annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(m)))
)
```

## Is the interaction of temp and habitat significant? (WEBL)

```{r}
poly_WEBL <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
linear_WEBL <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,1) * habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
noint_WEBL <- glmmTMB(valid_detections ~ habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
anova(poly_WEBL,linear_WEBL,noint_WEBL) %>% tibble() %>% mutate(model = c("no int","linear","sq int"),.before = Df) %>% gt()
```

## Is the squared term significant? (WEBL)

```{r}
nosq_WEBL <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,1) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
notemp_WEBL <- glmmTMB(valid_detections ~ habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
anova(linear_WEBL,nosq_WEBL,notemp_WEBL) %>% tibble() %>% mutate(model = c("no temp","no squared term","linear int term"),.before = Df) %>% gt()
```

## Inferential model provis ~ temp + habitat (WEBL) {.smaller}


```{r}
linear_WEBL <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,1) * habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "WEBL"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

(avg_temp <- ggpredict(linear_WEBL,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 30 mins") +
    ylab("Visits/30 mins") +
    labs(title = "WEBL") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,3)
  #                      ) +
    ylim(0,50) +
    annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(m)))
)
```

## Is the interaction of temp and habitat significant? (TRES)

```{r}
poly_TRES <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
linear_TRES <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,1) * habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
noint_TRES <- glmmTMB(valid_detections ~ habitat + poly(mean_temp_scaled,2) + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
anova(linear_TRES,poly_TRES,noint_TRES) %>% tibble() %>% mutate(model = c("no int","linear","sq int"),.before = Df) %>% gt()
```

## Is the squared term significant? (TRES)

```{r}
nosq_TRES <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,1) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
notemp_TRES <- glmmTMB(valid_detections ~ habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))
anova(poly_TRES,nosq_TRES,notemp_TRES) %>% tibble() %>% mutate(model = c("no temp","no squared term","squared int term"),.before = Df) %>% gt()
```


## Inferential model provis ~ temp^2 * habitat (TRES) {.smaller}


```{r}
poly_TRES <- glmmTMB(valid_detections ~ poly(mean_temp_scaled,2) * habitat + julian_date_scaled + mean_nestling_age_scaled + poly(tod_scaled,2) + (1|attempt_id) + (1|year),
						 ziformula = ~1,
						 family = nbinom2,
					data = dplyr::filter(p,!is.na(mean_temp),
					              !is.na(julian_date),
					              !is.na(mean_nestling_age),
					              !is.na(tod),
					              !is.na(site),
					              !is.na(attempt_id),
					              !is.na(year),
					              species == "TRES"# ,
												# tod >= hms::as.hms('11:00:00', tz = "America/Los_Angeles"),
												# tod_end <= hms::as.hms('17:00:00',tz = "America/Los_Angeles"),
												# tod_end >= hms::as.hms('11:00:00', tz = "America/Los_Angeles")
												) %>%
						mutate(across(c(tod,mean_temp,julian_date,mean_nestling_age),
													~ scale(.x)[,1],
													.names = "{.col}_scaled")))

(avg_temp <- ggpredict(poly_TRES,terms = c("mean_temp_scaled [all]","habitat"),bias_correction = TRUE) %>% plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Mean temp over 30 mins") +
    ylab("Visits/30 mins") +
    labs(title = "TRES") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    #theme(text = element_text(size = 16)) +
    # scale_x_continuous(trans = temp_trans,
    #                    breaks = c((20-mean_temp)/sd_temp,
    #                               (30-mean_temp)/sd_temp,
    #                               (40-mean_temp)/sd_temp,
    #                               (50-mean_temp)/sd_temp),
    #                    # breaks = c(20,30,40,50),
    #                    # labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    # limits = c(18,5)
    #                    ) +
  # scale_y_continuous(trans = growth_trans,
  #                      breaks = c((-2-mean_growth)/sd_growth,
  #                        (0-mean_growth)/sd_growth,
  #                        (2-mean_growth)/sd_growth,
  #                        (4-mean_growth)/sd_growth),
  #                      # breaks = c(0,1,2,3,4),
  #                      # labels = c("-2","0","2","4"),
  #                      # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                      # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
  #                      limits = c(-3,3)
  #                      ) +
    # ylim(0,25) +
    annotate("text", x = -1.5, y = 20, size = 5, label = paste("N =",nobs(m)))
)
```
