---
title: "Advisor meeting"
author: "Katie Lauck"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
library(tidyverse)
require(ggeffects)
require(lme4)
require(viridis)
library(car)
library(gt)
g <- read_rds("../data/growth.rds")
```

<!-- ## Some important correlations -->

<!-- ```{r,warning =FALSE,message=FALSE} -->
<!-- ggplot(mapping = aes(x = habitat,y = meanmaxtempO),data = g) + -->
<!--   geom_boxplot() -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = canopy_cover),data = g) + -->
<!--   geom_boxplot() -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = meanh),data = g) + -->
<!--   geom_boxplot() -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = gweight),data = filter(g,Species == "WEBL")) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = gweight),data = filter(g,Species == "TRES",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = age,y = gweight),data = filter(g,Species == "WEBL",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = age,y = gweight),data = filter(g,Species == "TRES",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = juliandate,y = gweight),data = filter(g,Species == "WEBL",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->

<!-- nrow(g %>% filter(!is.na(gweight),Species == "WEBL")) -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = juliandate,y = gweight),data = filter(g,Species == "TRES",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->

<!-- nrow(g %>% filter(!is.na(gweight),Species == "TRES")) -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = brood_size,y = gweight),data = filter(g,Species == "TRES",meanmaxtempI < 40)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = gweight),data = filter(g,Species == "WEBL")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = gweight),data = filter(g,Species == "TRES")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = cort_s1),data = filter(g,Species == "WEBL")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = cort_s2),data = filter(g,Species == "WEBL")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = cort_s1),data = filter(g,Species == "TRES")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = habitat,y = cort_s2),data = filter(g,Species == "TRES")) + -->
<!--   geom_boxplot() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- hist(filter(g,cort_s1 < 100000)$cort_s1) -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r } -->
<!-- hist(filter(g,cort_s2 < 100000)$cort_s2) -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s1,y = gweight),data = filter(g,Species == "WEBL",cort_s1 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s1,y = gweight),data = filter(g,Species == "TRES",cort_s1 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = cort_s1),data = filter(g,Species == "WEBL",cort_s1 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = cort_s1),data = filter(g,Species == "TRES",cort_s1 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s2,y = gweight),data = filter(g,Species == "WEBL",cort_s2 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s2,y = gweight),data = filter(g,Species == "TRES")) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = cort_s2),data = filter(g,Species == "WEBL",cort_s2 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = meanmaxtempI,y = cort_s2),data = filter(g,Species == "TRES")) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s1_mother,y = cort_s1),data = filter(g,Species == "WEBL", -->
<!--                                                                    cort_s1_mother < 25000, -->
<!--                                                                    cort_s1 < 10000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s2_mother,y = cort_s2),data = filter(g,Species == "WEBL", -->
<!--                                                                    cort_s2 < 100000, -->
<!--                                                                    cort_s2_mother < 100000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("WEBL") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s1_mother,y = cort_s1),data = filter(g,Species == "TRES")) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->


<!-- --- -->

<!-- ```{r} -->
<!-- ggplot(mapping = aes(x = cort_s2_mother,y = cort_s2),data = filter(g,Species == "TRES", -->
<!--                                                                    cort_s2_mother < 60000)) + -->
<!--   geom_smooth(method = "lm",formula = y ~ poly(x,2)) + -->
<!--   geom_point() + -->
<!--   ggtitle("TRES") -->
<!-- ``` -->

## Determining main model: WEBL

- meanI_WEBL_poly: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_WEBL_linear: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_WEBL_noint: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) + habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?
```{r}
meanI_WEBL_poly <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                      !is.na(meanmaxtempI)) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_linear <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                 !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_noint <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) + habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                                   !is.na(meanmaxtempI)) %>%
                                      mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                    ~ scale(.x)[,1],
                                                    .names = "{.col}_scaled"),
                                             meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_poly,meanI_WEBL_linear,meanI_WEBL_noint) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

### Is squared term significant?
```{r}

meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_notemp <- lmerTest::lmer(gweight_scaled ~ habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                        !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_poly,meanI_WEBL_nosq,meanI_WEBL_notemp) %>% tibble() %>% mutate(model = c("no temp","linear temp","sq temp"),.before = npar) %>% gt()

anova(meanI_WEBL_nosq,meanI_WEBL_linear) %>% tibble() %>% mutate(model = c("no sq","linear int"),.before = npar) %>% gt()
```

---

```{r}
plot(meanI_WEBL_nosq)
```

---

```{r}
hist(resid(meanI_WEBL_nosq))
```

---

```{r}
qqnorm(resid(meanI_WEBL_nosq))
qqline(resid(meanI_WEBL_nosq))
```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

---

```{r}
t <- summary(meanI_WEBL_nosq) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(4))

```

## Determining main model: TRES

- meanI_TRES: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_TRES_linear: gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- meanI_TRES_noint: gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?

```{r}
meanI_TRES <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


meanI_TRES_linear <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,1,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                                      filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_noint <- lmerTest::lmer(gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) + habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                                     filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES,meanI_TRES_linear,meanI_TRES_noint) %>% tibble() %>% mutate(model = c("no int","linear int","sq int"),.before = npar) %>% gt()
```

### Is squared temp term significant?

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_notemp <- lmerTest::lmer(gweight_scaled ~ habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES,meanI_TRES_nosq,meanI_TRES_notemp) %>% tibble() %>% mutate(model = c("no temp","linear temp","sq temp"),.before = npar) %>% gt()

```

---

```{r}
plot(meanI_TRES_nosq)
```

---

```{r}
hist(resid(meanI_TRES_nosq))
```

---

```{r}
qqnorm(resid(meanI_TRES_nosq))
qqline(resid(meanI_TRES_nosq))
```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

---

```{r}
t <- summary(meanI_TRES_nosq) %>% coef()
p <- row.names(t)
t <- t %>% data.frame()
names(t) <- c("Estimate","SE","df","t","P-value")
t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  select(!c(t,df)) %>%
  mutate_at(c("Estimate", "SE"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  gt() %>% tab_options(data_row.padding = px(1))

```

## Triple interaction with humidity: WEBL {.smaller}

- Main model (meanI_WEBL_nosq): gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- Additive model (meanI_WEBL_humadd): gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- Interaction with temp only (meanI_WEBL_humbytemp): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)
- No habitat (meanI_WEBL_humnohab): gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id)

---

### Is interaction significant?

```{r}
meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_humnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_humint,meanI_WEBL_humadd,meanI_WEBL_humbytemp,meanI_WEBL_nosq,meanI_WEBL_humnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no humidity","humidity * temp","double interactions","triple interaction"),.before = npar) %>% gt()

anova(meanI_WEBL_nosq,meanI_WEBL_humint) %>% tibble() %>% mutate(model = c("main model: no humidity","triple interaction"),.before = npar) %>% gt()
anova(meanI_WEBL_humint,meanI_WEBL_humbytemp) %>% tibble() %>% mutate(model = c("humidity * temp","triple interaction"),.before = npar) %>% gt()

```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_WEBL_humint,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Humidity") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## Triple interaction with humidity: TRES {.smaller}

- Main model (meanI_TRES): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Triple interaction model (meanI_TRES_humint): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Additive model (meanI_TRES_humadd): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + habitat * meanh_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Interaction with temp only (meanI_TRES_humbytemp): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- No habitat (meanI_TRES_humnohab): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * meanh_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)

---

### Is interaction significant?

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * meanh_scaled + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humbytemp <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_humnohab <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                      data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES_humint,meanI_TRES_humadd,meanI_TRES_humbytemp,meanI_TRES_nosq,meanI_TRES_humnohab) %>% tibble() %>% mutate(model = c("no habitat","main model: no humidity","humidity * temp","additive model","triple interaction"),.before = npar) %>% gt()

anova(meanI_TRES_nosq,meanI_TRES_humadd) %>% tibble() %>% mutate(model = c("main model: no humidity","additive model"),.before = npar) %>% gt()
anova(meanI_TRES_humadd,meanI_TRES_humbytemp) %>% tibble() %>% mutate(model = c("humidity * temp","additive model"),.before = npar) %>% gt()

anova(meanI_TRES_humadd,meanI_TRES_humint) %>% tibble() %>% mutate(model = c("additive model","triple interaction"),.before = npar) %>% gt()

```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_TRES_humbytemp,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
   ylim(-7.5,7.5) +
    labs(title = element_blank(),color = "Humidity") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## Triple interaction with canopy cover: WEBL {.smaller}

- Main model (meanI_WEBL_nosq): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Triple interaction model (meanI_WEBL_humint): gweight_scaled ~ meanmaxtempI_scaled * habitat * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Additive model (meanI_WEBL_humadd): gweight_scaled ~ meanmaxtempI_scaled * habitat + habitat * canopy_cover_scaled + meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Interaction with temp only (meanI_WEBL_humbytemp): gweight_scaled ~ meanmaxtempI_scaled * habitat + meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- No habitat (meanI_WEBL_humnohab): gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)

---

### Is interaction significant? Not for WEBL

```{r}
meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_cctempsq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmaxtempI_scaled,2) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_WEBL_ccint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_WEBL_ccadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_WEBL_ccint,meanI_WEBL_ccadd,meanI_WEBL_nosq,meanI_WEBL_cctempsq) %>% tibble() %>% mutate(model = c("additive","interactive","cc int with sq temp","no cc"),.before = npar) %>% gt()

anova(meanI_WEBL_nosq,meanI_WEBL_cctempsq) %>% tibble() %>% mutate(model = c("cc int with sq temp","main model: no canopy cover"),.before = npar) %>% gt()

```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_WEBL_ccbytemp,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Canopy cover") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## Triple interaction with canopy cover: TRES {.smaller}

- Main model (meanI_TRES): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Triple interaction model (meanI_TRES_humint): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Additive model (meanI_TRES_humadd): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + habitat * canopy_cover_scaled + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- Interaction with temp only (meanI_TRES_humbytemp): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * habitat + poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)
- No habitat (meanI_TRES_humnohab): gweight_scaled ~ poly(meanmaxtempI_scaled,2,raw = TRUE) * canopy_cover_scaled + meanmintempI_scaled + juliandate_scaled + year + site + (1|attempt_id)

---

### Is interaction significant?

```{r,message=FALSE,warning=FALSE}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_cctempsq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmaxtempI_scaled,2) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

meanI_TRES_ccint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
meanI_TRES_ccadd <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled + canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

anova(meanI_TRES_ccint,meanI_TRES_ccadd,meanI_TRES_nosq,meanI_TRES_cctempsq) %>% tibble() %>% mutate(model = c("additive","interactive","cc int with sq temp","no cc"),.before = npar) %>% gt()

anova(meanI_TRES_nosq,meanI_TRES_cctempsq) %>% tibble() %>% mutate(model = c("cc int with sq temp","main model: no canopy cover"),.before = npar) %>% gt()


```

---

```{r,fig.width=8.75,fig.height=6.25}
(p <- ggpredict(meanI_TRES_ccbytemp,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Maximum temperature (z-scaled; ~20-55C)") +
    ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Canopy cover") +
   ggtitle("Predicted growth across habitat and mean max daily temp") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

## Beginning cort explorations

Data prep:
```{r,echo=TRUE}
g <- g %>% mutate(cort_s1 = cort_s1/1000,
                  cort_s2 = cort_s2/1000,
                  cort_s1_mother = cort_s1_mother/1000,
                  cort_s2_mother = cort_s2_mother/1000,
                  condition = weight/tarsus)
c <- read_rds("../data/cort_with_id.rds")  %>%
  mutate(condition = weight/tarsus,
         s1 = s1/1000,
         s2 = s2/1000,
         cort_s1_mother = cort_s1_mother/1000,
         cort_s2_mother = cort_s2_mother/1000)

hist(only_adultf$s2[which(only_adultf$Species == "TRES")])

```

## WEBL models {.smaller}

### Baseline
Model: s1_scaled ~ brood_size_scaled + condition_scaled + habitat

```{r}
ms1 <- lm(s1_scaled ~ brood_size_scaled + condition_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL") %>%
            mutate(across(c(s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```
```{r}
summary(ms1)

hist()
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(ms1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13))
)
```

---

### Stressed {.smaller}

Model: s2_scaled ~ brood_size_scaled + condition_scaled + habitat
```{r}

ms2 <- lm(s2_scaled ~ brood_size_scaled + condition_scaled + habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "WEBL") %>%
            mutate(across(c(s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```

```{r}
summary(ms2)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(ms2,terms = c("condition_scaled","brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Instead of habitat as factor, temp * humidity * canopy cover: by condition and brood size

```{r,message=FALSE,warning=FALSE}
ms1_althab <- lm(s1_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "WEBL") %>%
            mutate(across(c(s1,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(ms1_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### By temp and brood size

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(ms1_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT WEBL: by condition and brood size

```{r,message=FALSE,warning=FALSE}


ms2_althab <- lm(s2_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "WEBL") %>%
            mutate(across(c(s2,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(ms2_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT WEBL: by temp and brood size

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(ms2_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

## TRES models {.smaller}

Baseline model: s1_scaled ~ brood_size_scaled + condition_scaled + habitat
```{r}
ms1 <- lm(s1_scaled ~ brood_size_scaled + condition_scaled * habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(s1,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
ms1 <- lm(cort_s1_scaled ~ cort_s1_mother_scaled,
          data = g %>%
            filter(life_stage == "nestling",
                   !is.na(cort_s1),
                   Species == "TRES") %>%
            mutate(across(c(cort_s1,cort_s1_mother),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )

```
```{r}
summary(ms1)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(ms1,terms = c("condition_scaled","brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Stressed CORT TRES
Model: s2_scaled ~ brood_size_scaled + condition_scaled + habitat

```{r}

ms2 <- lm(s2_scaled ~ brood_size_scaled + condition_scaled + habitat,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   Species == "TRES") %>%
            mutate(across(c(s2,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
```

```{r}
summary(ms2)
```

---

```{r,message=FALSE,warning=FALSE}
(p <- ggpredict(ms2,terms = c("condition_scaled","brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

### Alternative to habitat: temp* humidity * canopy cover

```{r,message=FALSE,warning=FALSE}
ms1_althab <- lm(s1_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s1),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "TRES") %>%
            mutate(across(c(s1,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(ms1_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(ms1_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Baseline adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message=FALSE,warning=FALSE}


ms2_althab <- lm(s2_scaled ~ brood_size_scaled + condition_scaled + meanmaxtempI_scaled * meanh_scaled * canopy_cover_scaled,
          data = c %>%
            filter(Sex == "F" & Age %in% c("AHY","ASY","SY"),
                   !is.na(s2),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(meanmaxtempI),
                   !is.na(meanh),
                   !is.na(canopy_cover),
                   Species == "TRES") %>%
            mutate(across(c(s2,brood_size,condition,meanmaxtempI,meanh,canopy_cover),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"))
          )
(p <- ggpredict(ms2_althab,terms = c("condition_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```

---

```{r,message = FALSE,warning=FALSE}
(p <- ggpredict(ms2_althab,terms = c("meanmaxtempI_scaled","brood_size_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Temperature (scaled)") +
    ylab("Stressed adult female CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES") +
    scale_fill_viridis() +
    scale_color_viridis() +
    theme(text = element_text(size = 13))
)
```


## Is there a difference between CORT among nestling sampling occasions? {.smaller}

### WEBL: baseline

```{r}
webls1 <- aov(cort_s1 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3)))
summary(webls1)
```
### WEBL: stressed

```{r}
webls2 <- aov(cort_s2 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "WEBL",
             occasion %in% c(2,3)))
summary(webls2)
```

---

### TRES: baseline

```{r}
tress1 <- aov(cort_s1 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))
summary(tress1)
```

### TRES: stressed

```{r}
tress2 <- aov(cort_s2 ~ factor(attempt_id) + factor(occasion),
    data = g %>%
      filter(life_stage == "nestling",
             Species == "TRES",
             occasion %in% c(2,3)))
summary(tress2)
```

My conclusion: Occasion does not seem to matter for baseline CORT but it does for stressed CORT.

---

```{r}
webls1 <- lmerTest::lmer(cort_s1_scaled ~ cort_s1_mother_scaled + condition_scaled + brood_size_scaled + habitat,
                         data = g %>%
                           filter(life_stage == "nestling",
                                  Species == "WEBL") %>%
                           mutate(across(c(cort_s1,cort_s1_mother,condition,brood_size),
                                         ~ scale(.x)[,1],
                                         .names = "{.col}_scaled")))
```

---

```{r}

cort_tempbyhab_WEBL <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                            data = filter(g,Species == "WEBL",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 10) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_WEBL,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```


---

```{r}
cort_tempbyhab_TRES <- lmerTest::lmer(cort_s1_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),
                            data = filter(g,Species == "TRES",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 20000) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_TRES,terms = c("meanmaxtempI_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Cover type") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: Nestling WEBL

```{r}
g <- g %>% mutate(condition = weight/tarsus)

ggplot(mapping = aes(x = cort_s1,y = condition),
       data = filter(g,Species == "WEBL",
                     cort_s1 < 25000)) +
  geom_smooth() +
  geom_point() +
  ggtitle("WEBL")

```

---

```{r}
cort_tempbyhab_WEBL <- lmerTest::lmer(cort_s1 ~ meanmaxtempI_scaled * habitat * condition_scaled + juliandate_scaled + year + site + (1|attempt_id),
                            data = filter(g,Species == "WEBL",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 10000) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1,condition),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

## Condition models: Nestling TRES

```{r}

ggplot(mapping = aes(x = cort_s1,y = condition),
       data = filter(g,Species == "TRES",
                     cort_s1 < 25000)) +
  geom_smooth() +
  geom_point() +
  ggtitle("TRES")

```

---

```{r,warning = FALSE,message=FALSE}
cort_tempbyhab_TRES <- lmerTest::lmer(cort_s1 ~ meanmaxtempI_scaled * habitat * condition_scaled + juliandate_scaled + year + site + (1|attempt_id),
                            data = filter(g,Species == "TRES",
                                          !is.na(meanmaxtempI),
                                          !is.na(cort_s1),
                                          cort_s1 < 10000) %>%
                              mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,cort_s1,condition),
                                            ~ scale(.x)[,1],
                                            .names = "{.col}_scaled"),
                                     meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

(p <- ggpredict(cort_tempbyhab_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    # xlab("Maximum temperature (z-scaled; ~20-55C)") +
    # ylab("Daily nestling growth (z-scaled; ~-2-8g)") +
    labs(title = element_blank(),color = "Condition") +
   ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") +
    # scale_fill_viridis(discrete = TRUE) +
    # scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 12))
)

```

<!-- ## Condition models: adult female WEBL baseline cort -->

<!-- ```{r} -->


<!-- AF_s1_WEBL <- lm(s1_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled, data = filter(only_adultf, Species == "WEBL", -->
<!--                                                                                         !is.na(meanmaxtempI), -->
<!--                                                                                         !is.na(s1)) %>% -->
<!--               mutate(across(c(s1,meanmaxtempI,condition,brood_size), -->
<!--                             ~ scale(.x)[,1], -->
<!--                             .names = "{.col}_scaled"))) -->

<!-- (p <- ggpredict(AF_s1_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     # xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     # ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Condition") + -->
<!--    ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 12)) -->
<!-- ) -->

<!-- ``` -->

<!-- ## Condition models: adult female WEBL stressed cort -->

<!-- ```{r} -->
<!-- c <- read_rds("../data/cort_with_id.rds")  %>% -->
<!--   mutate(condition = weight/tarsus) -->
<!-- only_adultf <- c %>% filter(Sex == "F" & Age %in% c("AHY","ASY","SY")) -->

<!-- AF_s2_WEBL <- lm(s2_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled, data = filter(only_adultf, Species == "WEBL", -->
<!--                                                                                         !is.na(meanmaxtempI), -->
<!--                                                                                         !is.na(s2)) %>% -->
<!--               mutate(across(c(s2,meanmaxtempI,condition,brood_size), -->
<!--                             ~ scale(.x)[,1], -->
<!--                             .names = "{.col}_scaled"))) -->

<!-- (p <- ggpredict(AF_s2_WEBL,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     # xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     # ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Condition") + -->
<!--    ggtitle("Predicted baseline cort across habitat and mean max daily temp WEBL") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 12)) -->
<!-- ) -->

<!-- ``` -->

<!-- ## Condition models: adult female TRES baseline cort -->

<!-- ```{r,warning=FALSE,message=FALSE} -->

<!-- AF_s1_TRES <- lm(s1_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled, data = filter(only_adultf, Species == "TRES", -->
<!--                                                                                         !is.na(meanmaxtempI), -->
<!--                                                                                         !is.na(s1)) %>% -->
<!--               mutate(across(c(s1,meanmaxtempI,condition,brood_size), -->
<!--                             ~ scale(.x)[,1], -->
<!--                             .names = "{.col}_scaled"))) -->

<!-- (p <- ggpredict(AF_s1_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     # xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     # ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Condition") + -->
<!--    ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 12)) -->
<!-- ) -->

<!-- ``` -->

<!-- ## Condition models: adult female TRES stressed cort -->

<!-- ```{r,warning=FALSE,message=FALSE} -->

<!-- AF_s2_TRES <- lm(s2_scaled ~ habitat * meanmaxtempI_scaled * condition_scaled + brood_size_scaled, data = filter(only_adultf, Species == "TRES", -->
<!--                                                                                         !is.na(meanmaxtempI), -->
<!--                                                                                         !is.na(s2)) %>% -->
<!--               mutate(across(c(s2,meanmaxtempI,condition,brood_size), -->
<!--                             ~ scale(.x)[,1], -->
<!--                             .names = "{.col}_scaled"))) -->

<!-- (p <- ggpredict(AF_s2_TRES,terms = c("meanmaxtempI_scaled","condition_scaled","habitat")) %>% plot(line.size = 1.5, -->
<!--                                                                                             alpha = .2,show_data = TRUE) + -->
<!--     theme_classic() + -->
<!--     # xlab("Maximum temperature (z-scaled; ~20-55C)") + -->
<!--     # ylab("Daily nestling growth (z-scaled; ~-2-8g)") + -->
<!--     labs(title = element_blank(),color = "Condition") + -->
<!--    ggtitle("Predicted baseline cort across habitat and mean max daily temp TRES") + -->
<!--     # scale_fill_viridis(discrete = TRUE) + -->
<!--     # scale_color_viridis(discrete = TRUE) + -->
<!--     theme(text = element_text(size = 12)) -->
<!-- ) -->

<!-- ``` -->
