---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Make figures for ESA 2024 presentation


```{r setup}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
### make prez figures
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
library(gt)
wmean <- read_rds("../data/wmean.rds")

g <- read_rds("../data/growth.rds") %>%
  filter(!is.na(gweight),!is.infinite(gweight),!is.infinite(meanmaxtempI),
         !is.infinite(meanmaxtempO))


```


## Question 1: How do heat waves affect nestling birds across land cover types?

### Hypothesis 1: forest is coolest, then orchard, grassland, row crop

```{r}
(out <- filter(wmean,logger_position == "O") %>%
    ggplot(mapping = aes(x = habitat, y = resid)) +
    geom_boxplot(aes(fill = habitat)) +
    xlab("Cover type") +
    ylab("\u00B0C above mean max") +
    #stat_summary(fun.y = median, fun.ymax = length,
    #geom = "text", aes(label = ..ymax..), vjust = -1) +
    labs(title = element_blank(),fill = "Cover type") +
    annotate("text",x = c(1:4),y = 16,label = c("a","b","c","d")) +
    scale_fill_viridis(discrete = TRUE) +
    theme_classic() +
    theme(text = element_text(size = 15),legend.position = "none"))
ggsave("../figures/max-weightedmean_outside.png",out,width = 5,height = 4)
ggsave("../figures/max-weightedmean_outside_small.png",out + theme(text = element_text(size = 11),legend.position = "none"),width = 3,height = 2)

(tuk_names <- TukeyHSD(aov(resid~habitat, filter(wmean,logger_position == "O")),conf.level = .95)[[1]] %>% as_tibble(rownames = "comparison") %>%
    mutate(across(diff:`p adj`,~round(.x,digits = 2)),
           `p adj` = if_else(`p adj` < .001, "<0.001",as.character(`p adj`))) %>% gt())

gtsave(tuk_names, "../figures/tukeytable_tempbylanduse.html")
```

### Hypothesis 2: Nestling growth declines with temperature

```{r}

(box <- g %>% filter(Species == "WEBL",gweight>-5,gweight<5,meanmaxtempI<50  ) %>% ggplot(aes(x = meanmaxtempI, y = gweight)) +
    geom_smooth(method = "lm",formula = y ~ x + I(x^2), se = TRUE,color = "black") +
    geom_point() +
    scale_fill_viridis(discrete = TRUE) +
    theme_classic()
  +
    labs(x = "Maximum temperature (\u00B0C)",
         y = "Nestling growth (g)",
         title = "WEBL") +
    theme(text = element_text(size = 16))
  # scale_y_continuous(trans = temp_trans,
  #                    breaks = c((20-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (30-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (40-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (50-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE)),
  #                    labels = c("20","30","40","50"),
  #                    limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE)))
)
lm(gweight ~ meanmaxtempI + I(meanmaxtempI^2),data = g%>% filter(Species=="WEBL")) %>% summary()

ggsave("../figures/weblgrowthbytemp.png",box,width = 6,height = 4)

```


```{r}

(box <- g %>% filter(Species == "TRES",gweight<3.7,meanmaxtempI<50) %>% ggplot(aes(x = meanmaxtempI, y = gweight)) +
    geom_smooth(method = "lm",formula = y ~ x + I(x^2), se = TRUE,color = "black") +
    geom_point() +
    scale_fill_viridis(discrete = TRUE) +
    theme_classic()
  +
    labs(x = "Maximum temperature (\u00B0C)",
         y = "Nestling growth (g)",
         title = "TRES") +
    theme(text = element_text(size = 16))
  # scale_y_continuous(trans = temp_trans,
  #                    breaks = c((20-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (30-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (40-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (50-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE)),
  #                    labels = c("20","30","40","50"),
  #                    limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
  #                               (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE)))
)
lm(gweight ~ meanmaxtempI + I( meanmaxtempI^2),data = g%>% filter(Species=="TRES")) %>% summary()

ggsave("../figures/tresgrowthbytemp.png",box,width = 6,height = 4)
```


## Question 2: How does the effect of heat on growth vary across land cover types?

### Hypothesis 1: Forest and orchard have relatively more canopy cover than grassland and row crop

Should use canopy cover instead of wmean, or filter wmean down to unique combos of year & cc & box

```{r}




unique_canopy_measures <- wmean %>%
  ungroup(date) %>%
  dplyr::select(c(year, box, canopy_cover,habitat)) %>%
  distinct()

TukeyHSD(aov(canopy_cover~habitat,unique_canopy_measures,conf.level = .95))

(box <- unique_canopy_measures %>% ggplot(mapping = aes(x = habitat,y = canopy_cover)) +
    geom_boxplot(aes(fill = habitat)) +
    scale_fill_viridis(discrete = TRUE) +
    theme_classic() +
    annotate("label",x = c(1:4),y = 100,label = c("a","b","c","c"),fill = "white",label.size = NA) +
    labs(x = "Cover type",
         y = "Canopy cover",
         title = element_blank(),
         fill = "Cover type") +
    theme(text = element_text(size = 11),legend.position="none") +
    scale_y_continuous(#trans = canopy_trans,
                       #breaks = c((0-mean(g$canopy_cover,na.rm = TRUE))/sd(g$canopy_cover,na.rm = TRUE),
                        #          (50-mean(g$canopy_cover,na.rm = TRUE))/sd(g$canopy_cover,na.rm = TRUE),
                         #         (100-mean(g$canopy_cover,na.rm = TRUE))/sd(g$canopy_cover,na.rm = TRUE)),
                       breaks = c(0,50,100),
                       labels = c("0%","50%","100%")))


ggsave("../figures/canopybyhabitat.png",box,width = 3,height = 2)

```


### Hypothesis 2: Internal nest box temp decreases with increasing canopy cover

```{r}
(box <- wmean %>% ggplot(aes(x = canopy_cover,y = resid)) +
    geom_point(alpha = .3) +
   geom_smooth(method = "lm", se = TRUE,color = "#35B779FF") +
    scale_fill_viridis(discrete = TRUE) +
    theme_classic()
  +
    labs(x = "Canopy cover",
         y = "\u00B0C above mean max",
         title = element_blank()) +
    theme(text = element_text(size = 11)) # +
    # scale_x_continuous(trans = canopy_trans,
    #                    breaks = c(0,50,100),
    #                    labels = c("0%","50%","100%")) +
    # scale_y_continuous(trans = temp_trans,
    #                    # breaks = c((20-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (30-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (40-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (50-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE)),
    #                    breaks = c(20,30,40,50),
    #                    labels = c("20","30","40","50"),
    #                    # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
    #                    #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
    #                    limits = c(18,52)
    #                    )
)
lm(resid ~ canopy_cover,data = wmean) %>% summary()

ggsave("../figures/tempbycanopy.png",box,width = 3,height = 2)

```

### Hypothesis 3: Agriculture makes nestlings more vulnerable to the negative effects of heat. Prediction: After accounting for the direct effects of heat, heat will still cause growth to decline more in agricultural land uses compared to natural land uses (i.e. there will still be an interactive effect of heat and land cover)

For explanation of why this model is best, check code/danny_meeting_20240213.html

## WEBL

```{r}
meanI_WEBL_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


```

```{r}

mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(p <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    annotate("text", x = -2.16, y = 3, size = 5, label = paste("N =",nobs(meanI_WEBL_nosq)))
)

ggsave("../figures/growthbytemp_WEBL.png",width = 6,height = 4)
```


```{r}
(p <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16, color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("transparent","transparent","transparent","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","transparent","transparent","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16,color = "transparent"),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )


ggsave("../figures/growthbytemp_WEBL_rowcrop.png",width = 6,height = 4)
```

```{r, include=FALSE}
(p <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16,color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("transparent","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )
ggsave("../figures/growthbytemp_WEBL_rowcrop_grassland.png",width = 6,height = 4)
```

```{r}
(p <- ggpredict(meanI_WEBL_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16,color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("#440154FF","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("#440154FF","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )
ggsave("../figures/growthbytemp_WEBL_rowcrop_grassland_forest.png",width = 6,height = 4)
```

## TRES

```{r}
meanI_TRES_nosq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                            !is.na(meanmaxtempI)) %>%
                               filter(meanmaxtempI < 45) %>%
                               mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size),
                                             ~ scale(.x)[,1],
                                             .names = "{.col}_scaled"),
                                      meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


```

```{r}

mean_temp <- mean(filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "TRES") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="TRES") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})


(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,5)
                       ) +
    annotate("text", x = -2.35, y = 4.9, size = 5, label = paste("N =",nobs(meanI_TRES_nosq)))
)

ggsave("../figures/growthbytemp_TRES.png",width = 6,height = 4)
```


```{r}
(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16, color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,5)
                       ) +
    scale_fill_manual(values = c("transparent","transparent","transparent","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","transparent","transparent","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )


ggsave("../figures/growthbytemp_TRES_rowcrop.png",width = 6,height = 4)
```

```{r}
(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16,color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,5)
                       ) +
    scale_fill_manual(values = c("transparent","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )
ggsave("../figures/growthbytemp_TRES_rowcrop_grassland.png",width = 6,height = 4)
```

```{r}
(p <- ggpredict(meanI_TRES_nosq,terms = c("meanmaxtempI_scaled [all]","habitat")) %>% plot(line_size = 1.5,
                                                                                            alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Max temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Cover type") +
   #ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16,color = "transparent")) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,5)
                       ) +
    scale_fill_manual(values = c("#440154FF","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("#440154FF","transparent","#35B779FF","#FDE725FF"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )
ggsave("../figures/growthbytemp_TRES_rowcrop_grassland_forest.png",width = 6,height = 4)
```

## Question 3: Why is nestling growth disproportionately low under extreme heat in row crop?

### Hypothesis 1: Canopy cover availability reduces costs of behavioral thermoregulation

## WEBL

```{r}
meanI_WEBL_cctempsq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmaxtempI_scaled,2) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
```

```{r}
mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(p <- ggpredict(meanI_WEBL_cctempsq,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled")) %>%
    filter(group != 0) %>%
    plot(line.size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Canopy cover") +
   # ggtitle("WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("#E14209FF","#30123BFF"),labels = c("Low","High")) +
   scale_color_manual(values = c("#E14209FF","#30123BFF"),labels = c("Low","High")) +
    annotate("text", x = -2, y = 3, size = 5, label = paste("NS; N =",nobs(meanI_WEBL_cctempsq)))
)

ggsave("../figures/tempintcanopy_cover_WEBL.png",width = 6, height = 4)
```



```{r}
mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(p <- ggpredict(meanI_WEBL_cctempsq,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled")) %>%
    filter(group != 0) %>%
    plot(line.size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = element_text("WEBL",color = "transparent"),color = "Canopy cover") +
   # ggtitle("WEBL") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-2-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("transparent","#30123BFF"),labels = c("Low","High"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","#30123BFF"),labels = c("Low","High"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
         plot.title = element_text(colour = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )

ggsave("../figures/tempintcanopy_cover_high_WEBL.png",width = 6, height = 4)
```
## TRES

```{r}
meanI_TRES_cctempsq <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * canopy_cover_scaled + poly(meanmaxtempI_scaled,2) * canopy_cover_scaled + poly(meanmintempI_scaled,2) * canopy_cover_scaled + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(canopy_cover)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,canopy_cover),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
```

```{r}
mean_temp <- mean(filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "TRES") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="TRES") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(p <- ggpredict(meanI_TRES_cctempsq,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled")) %>%
    filter(group != 0) %>%
    plot(line.size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Canopy cover") +
   # ggtitle("TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((25-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (35-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (45-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((1-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (3-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth,
                         (5-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       #limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("#E14209FF","#30123BFF"),labels = c("Low","High")) +
   scale_color_manual(values = c("#E14209FF","#30123BFF"),labels = c("Low","High")) +
    annotate("text", x = -1.8, y = -.9, size = 5, label = paste("NS; N =",nobs(meanI_TRES_cctempsq)))
)

ggsave("../figures/tempintcanopy_cover_TRES.png",width = 6, height = 4)
```



```{r}
mean_temp <- mean(filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "TRES") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="TRES") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

(p <- ggpredict(meanI_TRES_cctempsq,terms = c("meanmaxtempI_scaled [all]","canopy_cover_scaled")) %>%
    filter(group != 0) %>%
    plot(line.size = 1.5,alpha = .2,show_data = FALSE) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = element_text("TRES",color = "transparent"),color = "Canopy cover") +
   # ggtitle("TRES") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((25-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (35-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (45-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((1-mean_growth)/sd_growth,
                         (2-mean_growth)/sd_growth,
                         (3-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth,
                         (5-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       #limits = c(-3,3)
                       ) +
    scale_fill_manual(values = c("transparent","#30123BFF"),labels = c("Low","High"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   scale_color_manual(values = c("transparent","#30123BFF"),labels = c("Low","High"),guide = guide_legend(override.aes = list(alpha = 0) )) +
   theme(text = element_text(size = 16),legend.title = element_text(color = "transparent"),
         plot.title = element_text(colour = "transparent"),
    legend.text = element_text(color = "transparent"),axis.text = element_text(color = "transparent"),axis.ticks = element_line(color = "transparent"),axis.line = element_line(color = "transparent"),axis.title = element_text(color = "transparent"),panel.background = element_rect(fill = "transparent"),plot.background = element_rect(fill = "transparent"),panel.border = element_rect(color = "transparent",fill = "transparent"),legend.background = element_rect(fill = "transparent"),legend.box.background = element_rect(color = "transparent",fill = "transparent"))
   )

ggsave("../figures/tempintcanopy_cover_high_TRES.png",width = 6, height = 4)
```




### Hypothesis 2: Irrigation supplements dietary water and facilitates evaporative cooling

## WEBL

```{r}
meanI_WEBL_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "WEBL",
                                                                                                                                                                                           !is.na(meanmaxtempI),
                                                                                                                                                                        !is.na(meanh)) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

```

```{r}
mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})


(p <- ggpredict(meanI_WEBL_humint,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% 
    # mutate(group = recode_factor(group,`-0.98`="-1 SD",`-0.02` = "Mean",`0.94`="+1 SD")) %>%
    plot(line.size = 1.5,alpha = .2) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Humidity") +
    #guides(color = guide_legend(reverse = TRUE)) +
   # ggtitle("Humidity preliminary results: WEBL") +
    #binned_scale(aesthetics = "color",palette = function(x) c("#f0f921", "#cc4778","#0d0887"), labels = c(NA,"-1 SD", "Mean", "+1 SD",NA,NA)) +
    scale_color_manual(labels = c("Low","Mean","High"),values = c("#f0f921", "#cc4778","#0d0887")) +
    scale_fill_manual(labels = c("Low","Mean","High"),values = c("#f0f921", "#cc4778","#0d0887")) +
    theme(text = element_text(size = 14)) +
  scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-4-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth,
                         (8-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(-3,3)
                       )
)

ggsave("../figures/humint_WEBL.png",width=6, height = 4)
```

## TRES

```{r}
meanI_TRES_humint <- lmerTest::lmer(gweight_scaled ~ meanmaxtempI_scaled * habitat * meanh_scaled + poly(meanmintempI_scaled,2) * habitat + age + juliandate_scaled + (1|year) + (1|site/attempt_id),data = filter(g,Species == "TRES",                                                                                                    !is.na(meanmaxtempI),                                                                                                   !is.na(meanh),                                                                                                          meanmaxtempI < 45) %>%
                                    mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,meanh),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
```

```{r}
mean_temp <- mean(filter(g,Species == "TRES") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="TRES") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "TRES") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="TRES") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})


(p <- ggpredict(meanI_TRES_humint,terms = c("meanmaxtempI_scaled [all]","meanh_scaled","habitat")) %>% 
    # mutate(group = recode_factor(group,`-0.98`="-1 SD",`-0.02` = "Mean",`0.94`="+1 SD")) %>%
    plot(line.size = 1.5,alpha = .2) +
    theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling growth (g)") +
    labs(title = "TRES",color = "Humidity") +
    #guides(color = guide_legend(reverse = TRUE)) +
   # ggtitle("Humidity preliminary results: TRES") +
    #binned_scale(aesthetics = "color",palette = function(x) c("#f0f921", "#cc4778","#0d0887"), labels = c(NA,"-1 SD", "Mean", "+1 SD",NA,NA)) +
    scale_color_manual(labels = c("Low","Mean","High"),values = c("#f0f921", "#cc4778","#0d0887")) +
    scale_fill_manual(labels = c("Low","Mean","High"),values = c("#f0f921", "#cc4778","#0d0887")) +
    theme(text = element_text(size = 14)) +
  scale_x_continuous(trans = temp_trans,
                       breaks = c((20-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp,
                                  (50-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
  scale_y_continuous(trans = growth_trans,
                       breaks = c((-4-mean_growth)/sd_growth,
                         (0-mean_growth)/sd_growth,
                         (4-mean_growth)/sd_growth,
                         (8-mean_growth)/sd_growth),
                       # breaks = c(0,1,2,3,4),
                       # labels = c("-2","0","2","4"),
                       # # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       # #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       limits = c(-3.5,5.5)
                       )
)

ggsave("../figures/humint_TRES.png",width=6, height = 4)
```

### Hypothesis 3: Forest has 0/2 stressors, Orchard has ag stressors, grassland has heat stressor, row crop has ag and heat stressors. So if this is the cause of interactive effect, and the stressors are chronic, baseline cort should be lowest in row crop. There is a lot of evidence that increased cort is adaptive, so growth should increase with increasing baseline cort.

## WEBL

```{r, echo = TRUE}
s1bytemphabitat_WEBL_poly <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2) * habitat + poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1bytemphabitat_WEBL_add <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1bytemphabitat_WEBL_notemp <- lmerTest::lmer(log(cort_s1) ~ poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1bytemphabitat_WEBL_tempnohab <- lmerTest::lmer(log(cort_s1) ~ poly(meanmaxtempI_scaled,2) + poly(meanmintempI_scaled,2) + meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

anova(s1bytemphabitat_WEBL_tempnohab,s1bytemphabitat_WEBL_poly,s1bytemphabitat_WEBL_add,s1bytemphabitat_WEBL_notemp)

```

```{r}

mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

plot_data <- ggpredict(s1bytemphabitat_WEBL_tempnohab,terms = c("meanmaxtempI_scaled [all]"))

(p <- plot_data %>% 
    plot(line.size = 1.5,alpha = .2,) +
   # autoplot(aes(color = habitat)) +
   #  layer_fit_data(alpha = .5,position = position_jitterdodge(0.4,0.7), size = 2) +
   #  geom_CI_bar(type = "linerange", size = 3, color = "black") +
   #  geom_expected_point(shape = 21, size = 4, stroke = 2, color = "black",mapping = aes(fill = habitat)) +
   theme_classic() +
    xlab("Maximum temperature (\u00B0C)") +
    ylab("Nestling cort (\U00B5g/mL)") +
    labs(title = "WEBL",color = "Cover type", fill = "Cover type") +
   # ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((25-mean_temp)/sd_temp,
                                  (30-mean_temp)/sd_temp,
                                  (35-mean_temp)/sd_temp,
                                  (40-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
    theme(text = element_text(size = 16))# +
  #annotate("text",x = c(1:4), y = rep(13,4), label = c("a","ab","b.","ab"))
)

# multcomp::glht(s1bytemphabitat_WEBL_add,linfct = mcp(habitat = "Tukey"), test = adjusted("fdr")) %>% summary()

ggsave("../figures/cortbytemphabitat_WEBL.png", width = 6, height = 4)
```



```{r, echo = TRUE}
s1byhabitat_WEBL_poly <- lmerTest::lmer(log(cort_s1) ~ poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1byhabitat_WEBL_poly_lmer <- lme4::lmer(log(cort_s1) ~ poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

summary(s1byhabitat_WEBL_poly)

s1byhabtemp_WEBL_poly <- lmerTest::lmer(log(cort_s1) ~ habitat * meanmaxtempI_scaled + poly(meanmintempI_scaled,2) * habitat + meanh_scaled * habitat + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1byhabnotemp_WEBL_poly <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) * habitat + meanh_scaled * habitat + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

anova(s1byhabtemp_WEBL_poly,s1byhabnotemp_WEBL_poly,s1byhabitat_WEBL_poly)

```

```{r}
plot_data <- ggpredict(s1byhabitat_WEBL_poly,terms = c("habitat [all]"))

(p <- plot_data %>% 
   autoplot(aes(color = habitat)) +
    layer_fit_data(alpha = .5,position = position_jitterdodge(0.4,0.7), size = 2) +
    geom_CI_bar(type = "linerange", size = 3, color = "black") +
    geom_expected_point(shape = 21, size = 4, stroke = 2, color = "black",mapping = aes(fill = habitat)) +
   theme_classic() +
    xlab("Cover type") +
    ylab("Nestling cort (\U00B5g/mL)") +
    labs(title = "WEBL",color = "Cover type", fill = "Cover type") +
   # ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
  annotate("text",x = c(1:4), y = rep(13,4), label = c("a","ab","b.","ab"))
)

multcomp::glht(s1byhabitat_WEBL_poly_lmer,linfct = mcp(habitat = "Tukey"), test = adjusted("fdr")) %>% summary()

ggsave("../figures/cortbyhabitat_WEBL.png")

#color = c("#440154FF","#31688e","#35B779FF","#FDE725FF"
```

```{r}
growthbycort <- lmerTest::lmer(gweight ~ poly(cort_s1_scaled,2) + meanmaxtempI_scaled * habitat + poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "WEBL",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

# summary(growthbycort)
```

```{r}
mean_temp <- mean(filter(g,Species == "WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)
sd_temp <- sd(filter(g,Species=="WEBL") %>% pull(meanmaxtempI),na.rm = TRUE)

mean_growth <- mean(filter(g,Species == "WEBL") %>% pull(gweight),na.rm = TRUE)
sd_growth <- sd(filter(g,Species=="WEBL") %>% pull(gweight),na.rm = TRUE)

mean_cort <- mean(filter(g,Species == "WEBL") %>% pull(cort_s1),na.rm = TRUE)
sd_cort <- sd(filter(g,Species=="WEBL") %>% pull(cort_s1),na.rm = TRUE)

temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

growth_trans <- trans_new("growth_trans",
                          transform = function(x){(x * sd_growth) + mean_growth},
                          inverse = function(x){x})

cort_trans <- trans_new("cort_trans",
                          transform = function(x){(x * sd_cort) + mean_cort},
                          inverse = function(x){x})

plot_data <- ggpredict(growthbycort,terms = c("cort_s1_scaled"))

(p <- plot_data %>% 
    plot(line.size = 1.5,alpha = .2,show_data = TRUE) +
   # autoplot(aes(color = habitat)) +
   #  layer_fit_data(alpha = .5,position = position_jitterdodge(0.4,0.7), size = 2) +
   #  geom_CI_bar(type = "linerange", size = 3, color = "black") +
   #  geom_expected_point(shape = 21, size = 4, stroke = 2, color = "black",mapping = aes(fill = habitat)) +
   theme_classic() +
    xlab("Nestling cort (\U00B5g/mL)") +
    ylab("Nestling growth (g)") +
    labs(title = "WEBL",color = "Cover type", fill = "Cover type") +
   # ggtitle("Predicted growth across habitat and mean max daily temp") +
    #xlim(0,NA) +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    scale_x_continuous(trans = cort_trans,
                       breaks = c((0-mean_cort)/sd_cort,
                                  (5-mean_cort)/sd_cort,
                                  (10-mean_cort)/sd_cort,
                                  (15-mean_cort)/sd_cort),
                       # breaks = c(20,30,40,50),
                       labels = c("0","5","10","15"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
    scale_y_continuous(trans = growth_trans,
                       breaks = c((1.5-mean_growth)/sd_growth,
                                  (2-mean_growth)/sd_growth,
                                  (2.5-mean_growth)/sd_growth,
                                  (3-mean_growth)/sd_growth,
                                  (3.5-mean_growth)/sd_growth),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
    theme(text = element_text(size = 16))# +
  #annotate("text",x = c(1:4), y = rep(13,4), label = c("a","ab","b.","ab"))
)

# multcomp::glht(s1bytemphabitat_WEBL_add,linfct = mcp(habitat = "Tukey"), test = adjusted("fdr")) %>% summary()
# 
ggsave("../figures/growthbycort_WEBL.png",width = 6, height = 4)
```



## TRES

```{r, echo = TRUE}
s1byhabitat_TRES_poly <- lmerTest::lmer(log(cort_s1) ~ poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1byhabitat_TRES_poly_lmer <- lme4::lmer(log(cort_s1) ~ poly(meanmintempI_scaled,2) * habitat + habitat * meanh_scaled + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

summary(s1byhabitat_TRES_poly)

s1byhabtemp_TRES_poly <- lmerTest::lmer(log(cort_s1) ~ habitat * meanmaxtempI_scaled + poly(meanmintempI_scaled,2) * habitat + meanh_scaled * habitat + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

s1byhabnotemp_TRES_poly <- lmerTest::lmer(log(cort_s1) ~ meanmaxtempI_scaled + poly(meanmintempI_scaled,2) * habitat + meanh_scaled * habitat + brood_size + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),
                                       data = (filter(g,Species == "TRES",
                                                     # !is.nan(cort_s1),
                                                     !is.na(meanmaxtempI),
                                                     !is.na(cort_s1)) %>%
                                    mutate(across(c(cort_s1,
                                                    meanmaxtempI,
                                                    meanmintempI,
                                                    meanh,
                                                    cort_s1_mother,
                                                    age,
                                                    juliandate),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = 
                                             meanmaxtempI_scaled * meanmaxtempI_scaled)))

anova(s1byhabtemp_TRES_poly,s1byhabnotemp_TRES_poly,s1byhabitat_TRES_poly)

```

```{r}
plot_data <- ggpredict(s1byhabitat_TRES_poly,terms = c("habitat [all]"))

(p <- plot_data %>% 
   autoplot(aes(color = habitat)) +
    layer_fit_data(alpha = .5,position = position_jitterdodge(0.4,0.7), size = 2) +
    geom_CI_bar(type = "linerange", size = 2, color = "black") +
    geom_expected_point(shape = 21, size = 4, stroke = 2, color = "black",mapping = aes(fill = habitat)) +
   theme_classic() +
    xlab("Cover type") +
    ylab("Nestling cort (\U00B5g/mL)") +
    labs(title = "TRES",color = "Cover type", fill = "Cover type") +
   # ggtitle("Predicted growth across habitat and mean max daily temp") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16))# +
  #annotate("text",x = c(1:4), y = rep(13,4), label = c("a","a","a","a"))
)

multcomp::glht(s1byhabitat_TRES_poly_lmer,linfct = mcp(habitat = "Tukey"), test = adjusted("fdr")) %>% summary()

ggsave("../figures/cortbyhabitat_TRES.png")

#color = c("#440154FF","#31688e","#35B779FF","#FDE725FF"
```
