---
title: "growth models eval"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
#knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
### make prez figures
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
require(gt)
library(glmmTMB)
library(dagitty)
library(ggdag)
library(ggplot2)
library(egg)
library(igraph)
library(tidyverse)
library(performance)
library(modelsummary)
library(car)
library(lme4)
library(hms)
library(emmeans)
library(patchwork)
# modelsummary::get_gof(my_model)
# performance::model_performance(my_model)
wmean <- read_rds("../data/wmean.rds")

g <- read_rds("../data/growth_and_provis_combined_mobilenetv3-original_dataset.h5.rds") %>%
  mutate(abs_change_cort = cort_s2-cort_s1,
         prop_change_cort = (cort_s2-cort_s1)/cort_s1,
         year_fct = as.factor(year))
p <- read_rds("../data/provis_with_attempt_1h_combined_mobilenetv3-original_dataset.h5.rds") %>%
  mutate(year = year(date),
         year_fct = as.factor(year))

b <- read_csv("../data/banding-and-morphometrics_proofed.csv")

```




## Objectives

1. Does growth satisfy normality?
1. Produce one model with max and one model with min, look at graphically to see what looks nicest
1. Evaluate model:
  - fit
  - qqplots
  - outliers
  - residuals vs temp

## Does growth satisfy normality?

### WEBL

```{r}
hist(g %>% filter(Species == "WEBL") %>% pull(gweight))
qqnorm(g %>% filter(Species == "WEBL") %>% pull(gweight))
qqline(g %>% filter(Species == "WEBL") %>% pull(gweight))
```

It's a little funky, but seems mostly okay. Let's see if sqrt can rein this in like it did for cort.


```{r}
hist(g %>% filter(Species == "WEBL") %>% pull(gweight) %>% sqrt())
qqnorm(g %>% filter(Species == "WEBL") %>% pull(gweight) %>% sqrt())
qqline(g %>% filter(Species == "WEBL") %>% pull(gweight) %>% sqrt())
```

Nyope. So our options are to reflect & transform or just to leave it. My gut is to leave it as is. Let's just try natural log for shiggles.


```{r}
hist(g %>% filter(Species == "WEBL") %>% pull(gweight) %>% log())
qqnorm(g %>% filter(Species == "WEBL") %>% mutate(gweight = if_else(gweight<=0,.001,gweight)) %>% pull(gweight) %>% log())
qqline(g %>% filter(Species == "WEBL") %>% mutate(gweight = if_else(gweight<=0,.001,gweight)) %>% pull(gweight) %>% log())
```


Yeah that's a no from me dog


### TRES

```{r}
hist(g %>% filter(Species == "TRES") %>% pull(gweight))
qqnorm(g %>% filter(Species == "TRES") %>% pull(gweight))
qqline(g %>% filter(Species == "TRES") %>% pull(gweight))
```

It's a little funky, but seems mostly okay. Let's see if sqrt can rein this in like it did for cort.


```{r}
hist(g %>% filter(Species == "TRES") %>% pull(gweight) %>% sqrt())
qqnorm(g %>% filter(Species == "TRES") %>% pull(gweight) %>% sqrt())
qqline(g %>% filter(Species == "TRES") %>% pull(gweight) %>% sqrt())
```

Nyope. So our options are to reflect & transform or just to leave it. My gut is to leave it as is. Let's just try natural log for shiggles.


```{r}
hist(g %>% filter(Species == "TRES") %>% pull(gweight) %>% log())
qqnorm(g %>% filter(Species == "TRES") %>% mutate(gweight = if_else(gweight<=0,.001,gweight)) %>% pull(gweight) %>% log())
qqline(g %>% filter(Species == "TRES") %>% mutate(gweight = if_else(gweight<=0,.001,gweight)) %>% pull(gweight) %>% log())
```


Yeah that's a no from me dog


## Produce one model with linear min and max, and one with squared temp

### WEBL

```{r}
s1_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

s1_sqmax <- lmerTest::lmer(gweight ~ poly(meanmaxtempI_scaled,2) * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
```

#### Plots

```{r}
(pl <- ggpredict(s1_lintemp,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week") +
    ylab("Growth") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = "WEBL; linear max and min") +
   # ylim(0,100) +
   annotate("text", x = -1.5, y = 15, size = 5, label = paste("N =",nobs(s1_lintemp)))
   )
```

```{r}
summary(s1_lintemp)
```


```{r}
(pl <- ggpredict(s1_sqmax,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week") +
    ylab("Growth") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = "WEBL; sq max") +
   # ylim(0,100) +
   annotate("text", x = -1.5, y = 15, size = 5, label = paste("N =",nobs(s1_lintemp)))
   )
```

```{r}
summary(s1_sqmax)
```



```{r}
performance::check_predictions(s1_lintemp)
performance::check_predictions(s1_sqmax)
```

```{r}
performance::check_collinearity(s1_lintemp)
```

```{r}
performance::check_collinearity(s1_sqmax)
```

High VIFs all seem to come from interactions so probably not a huge issue. But maybe the second model is the best one because there is a moderate VIF for max and min temp.

#### What happens to VIFs for linear model without interactions?

This should tell us whether max and min are worryingly collinear with each other.

```{r}
s1_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
check_collinearity(s1_lintemp)
```

It looks like they aren't, which is what I thought. So we should be good there.


### TRES

```{r}
s1_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

s1_sqmax <- lmerTest::lmer(gweight ~ poly(meanmaxtempI_scaled,2) * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                  .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
```

#### Plots

```{r}
(pl <- ggpredict(s1_lintemp,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week") +
    ylab("Growth") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = "TRES; linear max and min") +
   # ylim(0,100) +
   annotate("text", x = -1.5, y = 15, size = 5, label = paste("N =",nobs(s1_lintemp)))
   )
```

```{r}
summary(s1_lintemp)
```


```{r}
(pl <- ggpredict(s1_sqmax,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week") +
    ylab("Growth") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = "TRES; sq max") +
   ylim(-5,5) +
   annotate("text", x = -1.5, y = 15, size = 5, label = paste("N =",nobs(s1_sqmax)))
   )
```

```{r}
summary(s1_sqmax)
```



```{r}
performance::check_predictions(s1_lintemp)
performance::check_predictions(s1_sqmax)
```

```{r}
performance::check_collinearity(s1_lintemp)
```

```{r}
performance::check_collinearity(s1_sqmax)
```

High VIFs all seem to come from interactions so probably not a huge issue. But maybe the second model is the best one because there is a moderate VIF for max and min temp.

#### What happens to VIFs for linear model without interactions?

This should tell us whether max and min are worryingly collinear with each other.

```{r}
s1_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + (1|year) + (1|site/attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
check_collinearity(s1_lintemp)
```

It looks like they aren't, which is what I thought. So we should be good there.

### Conclusions: linear max and min are the way to go. yussss

## Evaluate chosen models

### WEBL

```{r}
webl_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

check_residuals(webl_lintemp)
hist(simulate_residuals(webl_lintemp))
plot(simulate_residuals(webl_lintemp)%>% residuals() ~ fitted(webl_lintemp))
plot(simulate_residuals(webl_lintemp)%>% residuals() ~ webl_lintemp@frame$meanmaxtempI_scaled)
```


This seems totally fine, actually.


### TRES

```{r}
TRES_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

check_residuals(TRES_lintemp)
hist(simulate_residuals(TRES_lintemp))
plot(simulate_residuals(TRES_lintemp)%>% residuals() ~ fitted(TRES_lintemp))
plot(simulate_residuals(TRES_lintemp)%>% residuals() ~ TRES_lintemp@frame$meanmaxtempI_scaled)
```


This is looking like there's still some structure in the residuals - they increase with fitted values. How much is this a problem?

### Conclusions: mostly okay besides some non-uniformity in residuals for TRES.

## Test for interaction with habitat



### WEBL

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmax <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmin <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_noint <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

c1 <- anova(g_lintemp,g_lintemp_addmin,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

c2 <- anova(g_lintemp,g_lintemp_addmax,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

(tab <- bind_rows(c1,c2) %>%
  as.tibble() %>%
  mutate(across(where(is.numeric),~round(.x,digits = 4)),
         P = `Pr(>Chisq)`) %>%
  dplyr::select(Model,AIC,Chisq,P) %>%
  mutate(max_or_min = c(rep("Max temp",times = 3),rep("Min temp",times = 3)),
         across(c(AIC,Chisq), ~ round(.x, digits = 2)),
         P = if_else(P < 0.001,"<0.001",as.character(P))) %>%
  group_by(max_or_min) %>% gt())
gtsave(tab,"../figures/int_tab_growth_webl.html")
summary(g_lintemp)
```


### Conclusion: growth interacts with max and min.

### Sample sizes:

```{r}
samp_year_webl <- g_lintemp@frame %>% group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>% ungroup() %>% mutate(Total = `2021` + `2022` + `2023`)
(t_samp_year_webl <- samp_year_webl %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.)))
  
  
  t_samp_year_webl %>% gtsave("../figures/ss_year_webl.html")

samp <- g_lintemp@frame %>% group_by(habitat) %>% summarize(count = n())
samp %>% gt() %>% gtsave("../figures/ss_webl.html")


dat_text_webl <- data.frame(
  label = paste("N =",samp$count),
  group   = factor(c("Forest","Orchard","Grassland","Row crop"))
)
```


```{r}

data_webl = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)


mean_temp_webl <- mean(data_webl %>% pull(meanmaxtempI))
sd_temp_webl <- sd(data_webl %>% pull(meanmaxtempI))


temp_trans_webl <- trans_new("temp_trans_webl",
                          transform = function(x){(x * sd_temp_webl) + mean_temp_webl},
                          inverse = function(x){x})

(fig2_webl <- ggpredict(g_lintemp,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week (\u00b0C)") +
    ylab("Growth (g/day)") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank()) +
    scale_x_continuous(trans = temp_trans_webl,
                       breaks = c((20-mean_temp_webl)/sd_temp_webl,
                                  (25-mean_temp_webl)/sd_temp_webl,
                                  (30-mean_temp_webl)/sd_temp_webl,
                                  (35-mean_temp_webl)/sd_temp_webl,
                                  (40-mean_temp_webl)/sd_temp_webl),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
   #ylim(-5,5) +
   geom_text(data = dat_text_webl, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) + 
    theme(legend.position = "none")
   )

ggsave("../figures/growthbytempxhab_WEBL.png",plot =  fig2_webl, width = 10, height = 6.6)
```

```{r}
summary(g_lintemp)
```

```{r}
(t <- emtrends(g_lintemp,specs = ~ habitat, var = c("meanmaxtempI_scaled")) %>% test() %>%
   mutate(across(where(is.numeric), ~ round(.x, digits = 3)),
          df = round(df),
          p.value = if_else(p.value == 0.000,"<0.001",as.character(p.value))) %>%
   rename(Habitat = "habitat", `Max temp trend` = "meanmaxtempI_scaled.trend",Df = "df", `T-ratio` = "t.ratio", P = "p.value") %>%
   gt())


gtsave(t,"../figures/weblgrowthtrendmax.html")

data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_lintemp,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(meanmaxtempI_scaled = (meanmaxtempI_scaled * sd(data$meanmaxtempI)) + mean(data$meanmaxtempI),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    meanmaxtempI_scaled = round(meanmaxtempI_scaled),
    meanmaxtempI_scaled = paste0(meanmaxtempI_scaled,"\u00b0C")) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("Maximum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(Habitat = "habitat",`Max temperature` = "meanmaxtempI_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
  group_by(`Max temperature`) %>%
  mutate(row=row_number()) %>% 
  pivot_longer(-c(`Max temperature`, row,Habitat)) %>%
  pivot_wider(names_from=c(`Max temperature`, name), values_from=value) %>%
  dplyr::select(-row) %>%
  #mutate(`Maximum TA_P` = if_else(`Maximum TA_P` == 0.000,"<0.001",as.character(`Maximum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"
  ))

gtsave(t,"../figures/weblgrowthdeltamax.html")

((emmeans(g_lintemp,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_lintemp,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_lintemp,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

emmeans(g_lintemp,specs = pairwise ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2,0,2))) %>% plot(comparisons = TRUE)
emmip(g_lintemp,formula = habitat ~ meanmaxtempI_scaled, at = list(meanmaxtempI_scaled = seq(from = -2.5, to = 2.5, by = .1)),CIs = TRUE, plotit = FALSE) %>% emmip_ggplot() + theme_classic()

```

## Emmeans to check for effect of habitat

```{r}
(t <- emmeans(g_lintemp,"habitat") %>% regrid() %>% pairs() %>% as_tibble() %>% 
   mutate(across(estimate:t.ratio,~round(.x,digits = 2)),
          across(p.value,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growthbyhabitat_webl.html")
```

### Check for effect of temperature

```{r}
(t <- summary(g_lintemp) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
   # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
   mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
          across(`Pr(>|t|)`,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growthbyhabitat_summary_webl.html")
```

## min temp


```{r}
data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)


mean_temp <- mean(data %>% pull(meanmintempI))
sd_temp <- sd(data %>% pull(meanmintempI))


temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

(pl <- ggpredict(g_lintemp,terms = c("meanmintempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily min temp over preceding week (\u00b0C)") +
    ylab("Growth (g/day)") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank()) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((8-mean_temp)/sd_temp,
                                  (12-mean_temp)/sd_temp,
                                  (16-mean_temp)/sd_temp,
                                  (20-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmintempI,na.rm = TRUE))/sd(g$meanmintempI,na.rm = TRUE),
                       #            (55-mean(g$meanmintempI,na.rm = TRUE))/sd(g$meanmintempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
   #ylim(-5,5) +
   geom_text(data = dat_text_webl, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) + 
    theme(legend.position = "none")
   )

ggsave("../figures/growthbymintempxhab_WEBL.png",plot =  pl, width = 10, height = 6.6)
```

```{r}
summary(g_lintemp)
```

```{r}
(t <- emtrends(g_lintemp,specs = ~ habitat, var = c("meanmintempI_scaled")) %>% test() %>%
   mutate(across(where(is.numeric), ~ round(.x, digits = 3)),
          df = round(df),
          p.value = if_else(p.value == 0.000,"<0.001",as.character(p.value))) %>%
   rename(Habitat = "habitat", `Min temp trend` = "meanmintempI_scaled.trend",Df = "df", `T-ratio` = "t.ratio", P = "p.value") %>%
   gt())


gtsave(t,"../figures/weblgrowthtrendmin.html")

data = dplyr::filter(g,Species == "WEBL",!is.na(meanmintempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmintempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmintempI_scaled_sq = meanmintempI_scaled * meanmintempI_scaled)

(t <- emmeans(g_lintemp,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(meanmintempI_scaled = (meanmintempI_scaled * sd(data$meanmintempI)) + mean(data$meanmintempI),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    meanmintempI_scaled = round(meanmintempI_scaled),
    meanmintempI_scaled = paste0(meanmintempI_scaled,"\u00b0C")) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(Habitat = "habitat",`min temperature` = "meanmintempI_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
  group_by(`min temperature`) %>%
  mutate(row=row_number()) %>% 
  pivot_longer(-c(`min temperature`, row,Habitat)) %>%
  pivot_wider(names_from=c(`min temperature`, name), values_from=value) %>%
  dplyr::select(-row) %>%
  #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"
  ))

gtsave(t,"../figures/weblgrowthdeltamin.html")

((emmeans(g_lintemp,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_lintemp,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_lintemp,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

emmeans(g_lintemp,specs = pairwise ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2,0,2))) %>% plot(comparisons = TRUE)
emmip(g_lintemp,formula = habitat ~ meanmintempI_scaled, at = list(meanmintempI_scaled = seq(from = -2.5, to = 2.5, by = .1)),CIs = TRUE, plotit = FALSE) %>% emmip_ggplot() + theme_classic()

```


#### Check whether controlling for brood size explains the habitat * temp differences.

Because higher temps reduce survival, especially in forest, we are thinking that brood size is the outcome of the habitat * temp interaction. So, if we include brood size and the relationship growth ~ habitat * temp disappears, we think that's what's going on.

## create brood size by week measure

```{r}
brood_size <- b %>% group_by(`Banding Date`,Nestbox) %>% summarize(brood_size_weekly = n()) %>% ungroup() %>% mutate(date = mdy(`Banding Date`)) %>% dplyr::select(!`Banding Date`)

g <- left_join(g %>% ungroup(),brood_size, by = c("date","Nestbox"))
```

If this is so, then the main driver of growth and survival may be predation.

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmax <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled * habitat + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmin <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_noint <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

c1 <- anova(g_lintemp,g_lintemp_addmin,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

c2 <- anova(g_lintemp,g_lintemp_addmax,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

(tab <- bind_rows(c1,c2) %>%
  as.tibble() %>%
  mutate(across(where(is.numeric),~round(.x,digits = 4)),
         P = `Pr(>Chisq)`) %>%
  dplyr::select(Model,AIC,Chisq,P) %>%
  mutate(max_or_min = c(rep("Max temp",times = 3),rep("Min temp",times = 3)),
         across(c(AIC,Chisq), ~ round(.x, digits = 2)),
         P = if_else(P < 0.001,"<0.001",as.character(P))) %>%
  group_by(max_or_min) %>% gt())
gtsave(tab,"../figures/int_tab_growth_with_broodsize_webl.html")

summary(g_lintemp)
```

Is brood_size significant if I remove temp and habitat?

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))



summary(g_lintemp)

g_lintemp <- lmerTest::lmer(gweight ~ age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))



summary(g_lintemp)
```


### TRES

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmax <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled * habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmin <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_noint <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

c1 <- anova(g_lintemp,g_lintemp_addmin,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

c2 <- anova(g_lintemp,g_lintemp_addmax,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

(tab <- bind_rows(c1,c2) %>%
  as.tibble() %>%
  mutate(across(where(is.numeric),~round(.x,digits = 4)),
         P = `Pr(>Chisq)`) %>%
  dplyr::select(Model,AIC,Chisq,P) %>%
  mutate(max_or_min = c(rep("Max temp",times = 3),rep("Min temp",times = 3)),
         across(c(AIC,Chisq), ~ round(.x, digits = 2)),
         P = if_else(P < 0.001,"<0.001",as.character(P))) %>%
  group_by(max_or_min) %>% gt())
gtsave(tab,"../figures/int_tab_growth_tres.html")
```


```{r}
summary(g_lintemp_noint)
```


### Conclusion: growth interacts with max but not min.



#### Check whether controlling for brood size explains the habitat * temp differences.

Because higher temps reduce survival, especially in forest, we are thinking that brood size is the outcome of the habitat * temp interaction. So, if we include brood size and the relationship growth ~ habitat * temp disappears, we think that's what's going on.

## create brood size by week measure

```{r}
brood_size <- b %>% group_by(`Banding Date`,Nestbox) %>% summarize(brood_size_weekly = n()) %>% ungroup() %>% mutate(date = mdy(`Banding Date`)) %>% dplyr::select(!`Banding Date`)

g <- left_join(g %>% ungroup(),brood_size, by = c("date","Nestbox"))
```

If this is so, then the main driver of growth and survival may be predation.

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled * habitat + age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmax <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled * habitat + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_addmin <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled * habitat + meanmintempI_scaled + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

g_lintemp_noint <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + brood_size_weekly_scaled + age_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))

c1 <- anova(g_lintemp,g_lintemp_addmin,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

c2 <- anova(g_lintemp,g_lintemp_addmax,g_lintemp_noint) %>% tibble() %>% mutate(Model = c("no interaction","single interaction","both interacting"),.before = npar)

(tab <- bind_rows(c1,c2) %>%
  as.tibble() %>%
  mutate(across(where(is.numeric),~round(.x,digits = 4)),
         P = `Pr(>Chisq)`) %>%
  dplyr::select(Model,AIC,Chisq,P) %>%
  mutate(max_or_min = c(rep("Max temp",times = 3),rep("Min temp",times = 3)),
         across(c(AIC,Chisq), ~ round(.x, digits = 2)),
         P = if_else(P < 0.001,"<0.001",as.character(P))) %>%
  group_by(max_or_min) %>% gt())
gtsave(tab,"../figures/int_tab_growth_with_broodsize_TRES.html")

summary(g_lintemp)
```

Is brood_size significant if I remove temp and habitat?

```{r}
g_lintemp <- lmerTest::lmer(gweight ~ meanmaxtempI_scaled + meanmintempI_scaled + habitat + age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))



summary(g_lintemp)

g_lintemp <- lmerTest::lmer(gweight ~ age_scaled + brood_size_weekly_scaled + juliandate_scaled + year_fct + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size_weekly,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))



summary(g_lintemp)
```

### Sample sizes:

```{r}
samp_year_tres <- g_lintemp_addmin@frame %>% group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>% ungroup() %>% mutate(Total = `2021` + `2022` + `2023`)
(t_samp_year_tres <- samp_year_tres %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.)))
  t_samp_year_tres %>% gtsave("../figures/ss_year_tres.html")

samp <- g_lintemp_addmin@frame %>% group_by(habitat) %>% summarize(count = n())
samp %>% gt() %>% gtsave("../figures/ss_tres.html")


dat_text_tres <- data.frame(
  label = paste("N =",samp$count),
  group   = factor(c("Forest","Orchard","Grassland","Row crop"))
)
```

#### Combined sample sizes for growth

```{r}

rbind(t_samp_year_webl$`_data`,t_samp_year_tres$`_data`) %>% dplyr::select(Habitat, `2021`, `2022`, `2023`) %>% 
  mutate(Species = c(rep("WEBL",4),rep("TRES",4)),
         Response = "Growth") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value) %>%
  # dplyr::select(-row) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_")
```



```{r}

data_tres = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)


mean_temp_tres <- mean(data_tres %>% pull(meanmaxtempI))
sd_temp_tres <- sd(data_tres %>% pull(meanmaxtempI))


temp_trans_tres <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp_tres) + mean_temp_tres},
                          inverse = function(x){x})

(fig2_tres <- ggpredict(g_lintemp_addmin,terms = c("meanmaxtempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily max temp over preceding week (\u00b0C)") +
    ylab("Growth (g/day)") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank()) +
    scale_x_continuous(trans = temp_trans_tres,
                       breaks = c((20-mean_temp_tres)/sd_temp_tres,
                                  (25-mean_temp_tres)/sd_temp_tres,
                                  (30-mean_temp_tres)/sd_temp_tres,
                                  (35-mean_temp_tres)/sd_temp_tres,
                                  (40-mean_temp_tres)/sd_temp_tres),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE),
                       #            (55-mean(g$meanmaxtempI,na.rm = TRUE))/sd(g$meanmaxtempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
   #ylim(-5,5) +
   geom_text(data = dat_text_tres, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) + 
    theme(legend.position = "none")
   )

ggsave("../figures/growthbytempxhab_TRES.png",plot =  fig2_tres, width = 10, height = 6.6)
```

```{r}
summary(g_lintemp_addmin)
```

```{r}
(t <- emtrends(g_lintemp_addmin,specs = ~ habitat, var = c("meanmaxtempI_scaled")) %>% test() %>%
   mutate(across(where(is.numeric), ~ round(.x, digits = 3)),
          df = round(df),
          p.value = if_else(p.value == 0.000,"<0.001",as.character(p.value))) %>%
   rename(Habitat = "habitat", `Max temp trend` = "meanmaxtempI_scaled.trend",Df = "df", `T-ratio` = "t.ratio", P = "p.value") %>%
   gt())


gtsave(t,"../figures/tresgrowthtrendmax.html")

data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(meanmaxtempI_scaled = (meanmaxtempI_scaled * sd(data$meanmaxtempI)) + mean(data$meanmaxtempI),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    meanmaxtempI_scaled = round(meanmaxtempI_scaled),
    meanmaxtempI_scaled = paste0(meanmaxtempI_scaled,"\u00b0C")) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("Maximum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(Habitat = "habitat",`Max temperature` = "meanmaxtempI_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
  group_by(`Max temperature`) %>%
  mutate(row=row_number()) %>% 
  pivot_longer(-c(`Max temperature`, row,Habitat)) %>%
  pivot_wider(names_from=c(`Max temperature`, name), values_from=value) %>%
  dplyr::select(-row) %>%
  #mutate(`Maximum TA_P` = if_else(`Maximum TA_P` == 0.000,"<0.001",as.character(`Maximum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"
  ))

gtsave(t,"../figures/tresgrowthdeltamax.html")

((emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

emmeans(g_lintemp_addmin,specs = pairwise ~ habitat,by = c("meanmaxtempI_scaled"), at = list(meanmaxtempI_scaled = c(-2,0,2))) %>% plot(comparisons = TRUE)
emmip(g_lintemp_addmin,formula = habitat ~ meanmaxtempI_scaled, at = list(meanmaxtempI_scaled = seq(from = -2.5, to = 2.5, by = .1)),CIs = TRUE, plotit = FALSE) %>% emmip_ggplot() + theme_classic()

```

## Emmeans to check for effect of habitat

```{r}
(t <- emmeans(g_lintemp_addmin,"habitat") %>% regrid() %>% pairs() %>% as_tibble() %>% 
   mutate(across(estimate:t.ratio,~round(.x,digits = 2)),
          across(p.value,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growthbyhabitat_tres.html")
```

## min temp


```{r}
data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)


mean_temp <- mean(data %>% pull(meanmintempI))
sd_temp <- sd(data %>% pull(meanmintempI))


temp_trans <- trans_new("temp_trans",
                          transform = function(x){(x * sd_temp) + mean_temp},
                          inverse = function(x){x})

(pl <- ggpredict(g_lintemp_addmin,terms = c("meanmintempI_scaled [all]","habitat"),bias_correction = TRUE) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE) +
    theme_classic() +
   facet_wrap(~ group, ncol = 2) +
    xlab("Mean daily min temp over preceding week (\u00b0C)") +
    ylab("Growth (g/day)") +
   scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank()) +
    scale_x_continuous(trans = temp_trans,
                       breaks = c((8-mean_temp)/sd_temp,
                                  (12-mean_temp)/sd_temp,
                                  (16-mean_temp)/sd_temp,
                                  (20-mean_temp)/sd_temp),
                       # breaks = c(20,30,40,50),
                       # labels = c("20","30","40","50"),
                       # limits = c((15-mean(g$meanmintempI,na.rm = TRUE))/sd(g$meanmintempI,na.rm = TRUE),
                       #            (55-mean(g$meanmintempI,na.rm = TRUE))/sd(g$meanmintempI,na.rm = TRUE))
                       # limits = c(18,5)
                       ) +
   #ylim(-5,5) +
   geom_text(data = dat_text_tres, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) + 
    theme(legend.position = "none")
   )

ggsave("../figures/growthbymintempxhab_TRES.png",plot =  pl, width = 10, height = 6.6)
```

```{r}
summary(g_lintemp_addmin)
```

```{r}
(t <- emtrends(g_lintemp_addmin,specs = ~ habitat, var = c("meanmintempI_scaled")) %>% test() %>%
   mutate(across(where(is.numeric), ~ round(.x, digits = 3)),
          df = round(df),
          p.value = if_else(p.value == 0.000,"<0.001",as.character(p.value))) %>%
   rename(Habitat = "habitat", `Min temp trend` = "meanmintempI_scaled.trend",Df = "df", `T-ratio` = "t.ratio", P = "p.value") %>%
   gt())


gtsave(t,"../figures/tresgrowthtrendmin.html")

data = dplyr::filter(g,Species == "TRES",!is.na(meanmintempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmintempI,meanmintempI,juliandate,brood_size,age),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmintempI_scaled_sq = meanmintempI_scaled * meanmintempI_scaled)

(t <- emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(meanmintempI_scaled = (meanmintempI_scaled * sd(data$meanmintempI)) + mean(data$meanmintempI),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    meanmintempI_scaled = round(meanmintempI_scaled),
    meanmintempI_scaled = paste0(meanmintempI_scaled,"\u00b0C")) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(Habitat = "habitat",`min temperature` = "meanmintempI_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
  group_by(`min temperature`) %>%
  mutate(row=row_number()) %>% 
  pivot_longer(-c(`min temperature`, row,Habitat)) %>%
  pivot_wider(names_from=c(`min temperature`, name), values_from=value) %>%
  dplyr::select(-row) %>%
  #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"
  ))

gtsave(t,"../figures/tresgrowthdeltamin.html")

((emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_lintemp_addmin,specs = ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

emmeans(g_lintemp_addmin,specs = pairwise ~ habitat,by = c("meanmintempI_scaled"), at = list(meanmintempI_scaled = c(-2,0,2))) %>% plot(comparisons = TRUE)
emmip(g_lintemp_addmin,formula = habitat ~ meanmintempI_scaled, at = list(meanmintempI_scaled = seq(from = -2.5, to = 2.5, by = .1)),CIs = TRUE, plotit = FALSE) %>% emmip_ggplot() + theme_classic()

```

## Combined WEBL and TRES growth plots

```{r}
ggplot_build(fig2_webl)$layout$panel_scales_y
(p_full <- ggarrange(fig2_webl + theme(text = element_text(size = 12),axis.title.x = element_blank()),fig2_tres + ylim(-1.09,3.42) + theme(axis.text.y = element_blank(),
                                        axis.ticks.y = element_blank(),
                                        text = element_text(size = 12),
                                        axis.title.y = element_blank(),
                                        axis.title.x = element_text(hjust = 2.8)),ncol = 2,
          labels = c("(a): Western Bluebird","(b): Tree Swallow")))

ggsave("../figures/fig2_growth_by_temp_hab.png",p_full,width = 6.25,height = 4)
```



# Models to estimate the unbiased causal effect of cort and provisioning on growth

Model structure pulled from DAG: will use a minimal adjustment set to estimate the total effect of cort and provisioning on growth. 
{ attempt, humidity, nest_age, nestcond, surftemp }

I could subtract the direct from the total effect to get the indirect effect. I'm still vacillating between thinking that I should be measuring the total effect or the direct effect. I think because nestcond is really the only mediator in the DAG that I actually want total effect?

The question I'd like to ask: Does the direct effect of these two factors on growth change depending on habitat? I'm not sure that this causal structure is the correct one for that question. Is that a mediation analysis? After reading some papers, I think that actually the question is, do cort and provisioning mediate the effect of habitat and temperature on growth? I still think there may be other questions in this dataset. Maybe the answer is to do this paper just linear modeling with causal inference support, and then get Sage in on a paper that delves more deeply into a structural causal modeling framework.

The following focuses on the more simple question: how do cort and provisioning affect growth (total effect)? I will do the same model structure for survival in that notebook.

adjustment set: { attempt, humidity, nest_age, nestcond, surftemp }

```{r}

g_provis_cort <- lmerTest::lmer(gweight ~ cort_s1_scaled + provis_mean_scaled + meanmaxtempI_scaled + meanmintempI_scaled + meanh_scaled + age_scaled + condition_scaled + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


summary(g_provis_cort)

(t <- summary(g_provis_cort) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
   # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
   mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
          across(`Pr(>|t|)`,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growth_by_cort_provis_summary_webl.html")

data = dplyr::filter(g,Species == "WEBL",!is.na(gweight),!is.na(cort_s1),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_provis_cort,specs = ~ provis_mean_scaled,by = c("provis_mean_scaled"), at = list(provis_mean_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(provis_mean_scaled = (provis_mean_scaled * sd(data$provis_mean, na.rm = TRUE)) + mean(data$provis_mean,na.rm = TRUE),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    provis_mean_scaled = round(provis_mean_scaled)) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(`Provisioning` = "provis_mean_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
    #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)))
gtsave(t,"../figures/growth_by_basecort_provis_delta_webl.html")

((emmeans(g_provis_cort,specs = ~ provis_mean_scaled,by = c("provis_mean_scaled"), at = list(provis_mean_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_provis_cort,specs = ~ provis_mean_scaled,by = c("provis_mean_scaled"), at = list(provis_mean_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_provis_cort,specs = ~ provis_mean_scaled,by = c("provis_mean_scaled"), at = list(provis_mean_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))
```


```{r}

g_provis_abscort <- lmerTest::lmer(gweight ~ abs_change_cort_scaled + provis_mean_scaled + meanmaxtempI_scaled + meanmintempI_scaled + meanh_scaled + age_scaled + condition_scaled + (1|attempt_id),data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,abs_change_cort,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))


summary(g_provis_abscort)

(t <- summary(g_provis_abscort) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
   # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
   mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
          across(`Pr(>|t|)`,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growth_by_abscort_provis_summary_webl.html")

data = dplyr::filter(g,Species == "WEBL",!is.na(gweight),!is.na(abs_change_cort),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_provis_abscort,specs = ~ provis_mean_scaled,by = c("provis_mean_scaled"), at = list(provis_mean_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(provis_mean_scaled = (provis_mean_scaled * sd(data$provis_mean,na.rm = TRUE)) + mean(data$provis_mean,na.rm = TRUE),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    provis_mean_scaled = round(provis_mean_scaled)) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(`max temperature` = "provis_mean_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
    #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)))
gtsave(t,"../figures/growth_by_abscort_provis_delta_webl.html")

```

#### Sample size

```{r}
data_webl = dplyr::filter(g,Species == "WEBL",!is.na(gweight),!is.na(cort_s1),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)
samp_webl <- data_webl %>%
  group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>%
  # relocate(`2021`,.before = `2022`) %>%
  ungroup() %>%
  mutate(across(c(`2022`,`2023`),~ replace_na(.x,0)),
         Total = `2022`+`2023`)
samp_webl %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)) %>%
  gtsave("../figures/ss_year_webl_growthbybasecortprovis.html")
data = dplyr::filter(g,Species == "WEBL",!is.na(gweight),!is.na(abs_change_cort),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)
samp <- data %>%
  group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>%
  # relocate(`2021`,.before = `2022`) %>%
  ungroup() %>%
  mutate(across(c(`2022`,`2023`),~ replace_na(.x,0)),
         Total = `2022`+`2023`)
samp %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)) %>%
  gtsave("../figures/ss_year_webl_growthbyabscortprovis.html")
```



```{r}
mean_provis_webl <- mean(data_webl %>% pull(provis_mean))
sd_provis_webl <- sd(data_webl %>% pull(provis_mean))


provis_trans_webl <- trans_new("provis_trans_webl",
                          transform = function(x){(x * sd_provis_webl) + mean_provis_webl},
                          inverse = function(x){x})

(fig6_webl <- predict_response(g_provis_cort,terms = c("provis_mean_scaled","cort_s1_scaled [-2,2]"),bias_correction = TRUE,margin = "empirical") %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE,colors = "viridis") +
    theme_classic() +
   #facet_wrap(~ group, ncol = 2) +
    xlab("Provisioning") +
    ylab("Growth (g/day)") +
   #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank())  +
    scale_x_continuous(trans = provis_trans_webl,
                       breaks = c((0-mean_provis_webl)/sd_provis_webl,
                                  (5-mean_provis_webl)/sd_provis_webl,
                                  (10-mean_provis_webl)/sd_provis_webl,
                                  (15-mean_provis_webl)/sd_provis_webl,
                                  (20-mean_provis_webl)/sd_provis_webl)
    ) +
   #ylim(-5,5) +
   # geom_text(data = dat_text, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) # + 
    theme(legend.position = "none") +
    annotate(geom = "text",label = "N = 40",x = -Inf,y = -Inf,hjust = -.2,vjust = -.5)
   )

ggsave("../figures/growthbycort+provis_WEBL.png",plot =  fig6_webl, width = 10, height = 6.6)
```


## Canonical adjustment set overloads the data:

{ attempt, broodsize, habitat, humidity, jul_date, mother_s1, nest_age, site, surftemp, year }

```{r}

g_provis_cort_canon <- lmerTest::lmer(gweight ~ cort_s1_scaled + provis_mean_scaled + (1|attempt_id) + brood_size_scaled + habitat + meanh_scaled + juliandate_scaled + cort_s1_mother_scaled + age_scaled + meanmaxtempI_scaled + meanmintempI_scaled + year_fct,data = dplyr::filter(g,Species == "WEBL",!is.na(meanmaxtempI),meanmaxtempI < 45,!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,cort_s1_mother,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
summary(g_provis_cort_canon)

```

## TRES

```{r}

g_provis_cort <- lmerTest::lmer(gweight ~ cort_s1_scaled + provis_mean_scaled + meanmaxtempI_scaled + meanmintempI_scaled + meanh_scaled + age_scaled + condition_scaled + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
summary(g_provis_cort)

(t <- summary(g_provis_cort) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
   # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
   mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
          across(`Pr(>|t|)`,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growth_by_cort_provis_summary_tres.html")

data = dplyr::filter(g,Species == "TRES",!is.na(gweight),!is.na(cort_s1),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_provis_cort,specs = ~ cort_s1_scaled,by = c("cort_s1_scaled"), at = list(cort_s1_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(cort_s1_scaled = (cort_s1_scaled * sd(data$cort_s1, na.rm = TRUE)) + mean(data$cort_s1,na.rm = TRUE),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    cort_s1_scaled = round(cort_s1_scaled)) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(`Baseline cort` = "cort_s1_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
    #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)))
gtsave(t,"../figures/growth_by_basecort_provis_delta_tres.html")

((emmeans(g_provis_cort,specs = ~ cort_s1_scaled,by = c("cort_s1_scaled"), at = list(cort_s1_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_provis_cort,specs = ~ cort_s1_scaled,by = c("cort_s1_scaled"), at = list(cort_s1_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_provis_cort,specs = ~ cort_s1_scaled,by = c("cort_s1_scaled"), at = list(cort_s1_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

```

#### Abs diff cort

```{r}

g_provis_abscort <- lmerTest::lmer(gweight ~ abs_change_cort_scaled + provis_mean_scaled + meanmaxtempI_scaled + meanmintempI_scaled + meanh_scaled + age_scaled + condition_scaled + (1|attempt_id),data = dplyr::filter(g,Species == "TRES",!is.na(meanmaxtempI),!is.na(meanmintempI)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,abs_change_cort,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled))
summary(g_provis_cort)

(t <- summary(g_provis_abscort) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
   # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
   mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
          across(`Pr(>|t|)`,~round(.x,digits = 3))) %>% gt())
gtsave(t,"../figures/growth_by_cort_provis_summary_tres.html")

data = dplyr::filter(g,Species == "TRES",!is.na(gweight),!is.na(abs_change_cort),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,abs_change_cort,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)

(t <- emmeans(g_provis_abscort,specs = ~ abs_change_cort_scaled,by = c("abs_change_cort_scaled"), at = list(abs_change_cort_scaled = c(-2,0,2)),type = "response") %>% as.tibble() %>% #gt() %>%
  mutate(abs_change_cort_scaled = (abs_change_cort_scaled * sd(data$abs_change_cort, na.rm = TRUE)) + mean(data$abs_change_cort,na.rm = TRUE),
    across(where(is.numeric), ~ round(.x, digits = 2)),
    abs_change_cort_scaled = round(abs_change_cort_scaled)) %>%
  #tibble() %>%
  dplyr::select(-df) %>%
  #mutate(Model = rep(c("TA2 * LU + TA * LU", "TA2 + TA * LU", "TA2 + TA + LU"),2), type = c(rep("minimum TA", 3),rep("Minimum TA",3)), .before = AIC) %>%
  rename(`Baseline cort` = "abs_change_cort_scaled",`Predicted growth` = "emmean",`2.5%` = "lower.CL",`97.5%` = "upper.CL" ) %>%
    #mutate(`minimum TA_P` = if_else(`minimum TA_P` == 0.000,"<0.001",as.character(`minimum TA_P`))) %>%
  #mutate(`Minimum TA_P` = if_else(`Minimum TA_P` == 0.000,"<0.001",as.character(`Minimum TA_P`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)))
gtsave(t,"../figures/growth_by_basecort_provis_delta_tres.html")

((emmeans(g_provis_abscort,specs = ~ abs_change_cort_scaled,by = c("abs_change_cort_scaled"), at = list(abs_change_cort_scaled = c(2)),type = "response") %>% as.tibble() %>% pull(emmean))-(emmeans(g_provis_abscort,specs = ~ abs_change_cort_scaled,by = c("abs_change_cort_scaled"), at = list(abs_change_cort_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean)))/(emmeans(g_provis_abscort,specs = ~ abs_change_cort_scaled,by = c("abs_change_cort_scaled"), at = list(abs_change_cort_scaled = c(-2)),type = "response") %>% as.tibble() %>% pull(emmean))

```

#### Sample size

```{r}
data_tres = dplyr::filter(g,Species == "TRES",!is.na(gweight),!is.na(cort_s1),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)
samp_tres <- data_tres %>%
  group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>%
  # relocate(`2021`,.before = `2022`) %>%
  ungroup() %>%
  mutate(across(c(`2022`,`2023`),~ replace_na(.x,0)),
         Total = `2022`+`2023`)
samp_tres %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)) %>%
  gtsave("../figures/ss_year_TRES_growthbybasecortprovis.html")
data = dplyr::filter(g,Species == "TRES",!is.na(gweight),!is.na(abs_change_cort),!is.na(provis_mean),!is.na(meanmaxtempI),
                     !is.na(meanmintempI),!is.na(meanh),!is.na(age),!is.na(condition)) %>%
  mutate(across(c(gweight,meanmaxtempI,meanmintempI,juliandate,brood_size,age,meanh,cort_s1,condition,provis_mean),
                                                  ~ scale(.x)[,1],
                                                   .names = "{.col}_scaled"),
                                           meanmaxtempI_scaled_sq = meanmaxtempI_scaled * meanmaxtempI_scaled)
samp <- data %>%
  group_by(habitat,year_fct) %>% summarize(count = n()) %>% pivot_wider(values_from = count,names_from = year_fct) %>% as.tibble() %>% rename(Habitat = 'habitat') %>%
  # relocate(`2021`,.before = `2022`) %>%
  ungroup() %>%
  mutate(across(c(`2022`,`2023`),~ replace_na(.x,0)),
         Total = `2022`+`2023`)
samp %>% gt() %>% 
  grand_summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)) %>%
  gtsave("../figures/ss_year_TRES_growthbyabscortprovis.html")
```



```{r}
mean_provis_tres <- mean(data_tres %>% pull(provis_mean))
sd_provis_tres <- sd(data_tres %>% pull(provis_mean))


provis_trans_tres <- trans_new("provis_trans_tres",
                          transform = function(x){(x * sd_provis_tres) + mean_provis_tres},
                          inverse = function(x){x})

(fig6_tres <- predict_response(g_provis_cort,terms = c("provis_mean_scaled","cort_s1_scaled [-2,2]"),bias_correction = TRUE) %>%
   #filter(group != 0.35) %>%
    # mutate(group = as_factor(group) %>% fct_collapse(Low = "-0.93",High = "1.63")) %>%
   plot(line_size = 1.5,alpha = .2,show_data = TRUE,limit_range = TRUE,colors = "viridis") +
   #scale_fill_discrete(labels = c("Low","High")) +
   #scale_color_discrete(labels = c("Low","High")) +
   # geom_point(show.legend = FALSE) +
    theme_classic() +
   #facet_wrap(~ group, ncol = 2) +
    xlab("Provisioning (mean visits/hr)") +
    ylab("Growth (g/day)") +
   #scale_fill_viridis(discrete = TRUE) +
    #scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 16)) +
    labs(title = element_blank(),color = "Baseline cort") +
    scale_x_continuous(trans = provis_trans_tres,
                       breaks = c((0-mean_provis_tres)/sd_provis_tres,
                                  (10-mean_provis_tres)/sd_provis_tres,
                                  (20-mean_provis_tres)/sd_provis_tres,
                                  (30-mean_provis_tres)/sd_provis_tres,
                                  (40-mean_provis_tres)/sd_provis_tres,
                                  (50-mean_provis_tres)/sd_provis_tres)
    ) +
   #ylim(-5,5) #+
   # geom_text(data = dat_text, mapping = aes(x = -Inf, y = Inf,label = label),hjust = -.2, vjust = 1.2,inherit.aes = FALSE) # + 
  theme(legend.position = "none") +
    annotate("text",x = -Inf,y = -Inf,hjust = -.2,vjust = -.5,label = "N = 16")
   )

ggsave("../figures/growthbycort+provis_TRES.png",plot =  fig6_tres, width = 10, height = 6.6)
```

## Combined WEBL and TRES growth plots

```{r}
ggplot_build(fig6_webl)$layout$panel_scales_y
ggplot_build(fig6_tres)$layout$panel_scales_y
(p_full <- ggarrange(fig6_webl + theme(text = element_text(size = 12),legend.position = "none",axis.title.x = element_blank()) + ylim(-.115,2.87),fig6_tres + theme(axis.text.y = element_blank(),
                                        axis.ticks.y = element_blank(),
                                        text = element_text(size = 12),
                                        axis.title.y = element_blank(),
                                        legend.position = 'none',
                                        axis.title.x = element_text(hjust = -1.5)),ncol = 2,
          labels = c("(a): Western Bluebird","(b): Tree Swallow")))

ggsave("../figures/fig6_growth_by_temp_hab.png",p_full,width = 6.25,height = 4)
```
