---
title: "CORT covariates for chicks"
author: "Katherine Lauck"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE,fig.width = 3, fig.height = 2)
library(tidyverse)
require(ggeffects)
require(lme4)
require(viridis)
library(car)
library(gt)
library(ggpubr)
library(cowplot)
library(magick)
g <- read_rds("../data/growth.rds")
c <- read_rds("../data/cort_with_id.rds")

fun_peak <- function(x, adjust = 1) {
  d <- density(x, adjust = adjust)
  d$x[c(F, diff(diff(d$y) >= 0) < 0)]
}

peaks <- filter(c,
               Sex == "F",
               Age %in% c("SY","ASY","AHY")) %>%
  group_by(year,Species) %>%
  summarize(peaks = fun_peak(juliandate))

af <- filter(c,
               Sex == "F",
               Age %in% c("SY","ASY","AHY")) %>%
  arrange(desc(date.x)) %>%
  distinct(blood_num,.keep_all = TRUE) %>%
  group_by(year,ind_id) %>%
  group_map(~ {
    if(nrow(.x) > 1) {
      .x <- arrange(.x,juliandate) %>%
        mutate(mother_attempt_num = seq(from = 1, to = nrow(.x)))
    } else {
      peak <- filter(peaks,year == .y$year,Species == .x$Species)
      difference <- abs(.x$juliandate-peak)
      .x <- mutate(.x,mother_attempt_num = which.min(difference$peaks))
    }
  }) %>% list_rbind() %>%
  mutate(mother_attempt_num = factor(mother_attempt_num))

c <- left_join(c,
               select(af,blood_num,mother_attempt_num),
               by = c("blood_num_mother" = "blood_num"))
```
Objective: What factors affect CORT of nestling WEBL and TRES?

## Nestligs
### Distribution of the data
#### WEBL

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Age == "L",
                                       Species == "WEBL")) +
   theme_classic() +
   ggtitle("S1") +
   geom_density(fill = "grey"))


(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Age == "L",
                                       Species == "WEBL")) +
   theme_classic() +
    ggtitle("S2") +
   geom_density(fill = "grey"))

```

#### TRES

```{r}
(p <- ggplot(aes(x = mean_s1),data = filter(c,
                                       Age == "L",
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("S1") +
   geom_density(fill = "grey"))


(p <- ggplot(aes(x = mean_s2),data = filter(c,
                                       Age == "L",
                                       Species == "TRES")) +
   theme_classic() +
    ggtitle("S2") +
   geom_density(fill = "grey"))

```

### Cort coviariate candidates for nestlings

1. Day of year: Later in the season, the weather is hotter and dryer, and food is less abundant, and females may have already had a first clutch, so they may have higher baseline cort later in the season.

2. Mother cort
- Mother baseline cort: Mothers may pass on cort characteristics in eggs, or more stressed mothers may not provide optimal care to chicks
- Mother stressed cort: Mothers may pass on cort characteristics in eggs, or more stressed mothers may not provide optimal care to chicks.
- Mother stressed - baseline cort: Mothers may pass on cort characteristics in eggs, or more stressed mothers may not provide optimal care to chicks

N.B.: All three of these covariates will likely be part of the final analysis. I will choose one measure (likely baseline cort) to use for the following analyses.

3. Whether the cort sample was taken on week 2 or week 3 of chick development: older chicks will have a more developed stress response. We expect baseline cort to be mostly the same but stressed cort to be more elevated in older chicks.
4. Brood size: larger broods mean more competition, increasing nestlings' baseline and stress response cort. This may interact with habitat (why?)
5. Body condition of nestling: This could be either low condition -> high baseline cort or high baseline cort -> low condition. This may interact with habitat (why?)
    a. Lower condition requires individuals to mobilize more emergency energy in order to compete with siblings, which requires increasing cort levels in blood
    b. An exogenous source of stress (predation pressure, competition, low food supply) increases baseline cort, which mobilizes more stored energy, lowering body condition.



To investigate these covariates, I ran a full model:

cort ~ mother cort (s1, s2, or diff) + week2/week3 + brood_size * habitat + condition * habitat + juliandate or nestingattemptfemale + (1|attempt_id)

For each of the covariates, I:

1. Plotted the distribution of the covariate
2. Plotted how the covariate changed over julian date (seasonal variation) and how it was associated with female attempt number
3. Plotted the observed correlation between the covariate and nestling
4. Plotted the model-predicted relationship between the covariate and nestling cort
5. Used maximum-likelihood model comparison to determine whether the inclusion of the covariate improves the model. 

Plots and models are per species and separated between s1 & s2 where appropriate.

### Summary of findings - not yet updated with full results

First off, whether to use julian day or mother attempt number. I found very few differences in significance of covariates and no differences in model selection between models using julian day or mother attempt number (results compared throughout details of findings #1 and #2. I think julian day is more holistic and will soak up more unwanted variation, so I think that's what we should use.

```{r}
t <- expand.grid(model = c("covar + habitat","covar * habitat"),
                 sample = c("s1","s2","s2-s1"),
                 species = c("WEBL","TRES"),
                 factor = c("Julian day","Mother cort","occasion","Brood size","Condition")) %>%
  tibble() %>%
  mutate(significant = c("-0.05",NA,"-0.23.",NA,"-0.22",NA, # WEBL julian date
                         "0.12",NA,"0.13",NA,"0.05",NA, # TRES julian date
                         "-0.24",NA,"0.26.",NA,"0.21",NA, # WEBL mother cort
                         "-0.23*",NA,"0.39*",NA,"0.28",NA, # TRES mother cort
                         "0.83***",NA,"0.36",NA,"0.39",NA, # WEBL occasion
                         "0.60*",NA,"0.34",NA,"-0.03",NA, # TRES occasion
                         "-0.34","-0.36, 0.01, -0.12**","0.36","-0.43, 0.18, -0.27","0.62","-0.87, -0.42, -0.78", # WEBL brood size
                         "0.11","-0.43, 0.18, -0.27","-0.03","-0.36, 0.01, -0.12","-1.62","1.57, 1.53, 1.20", # TRES brood size
                         "0.30","-1.26, -0.04, 0.11","0.07","-0.17, 0.29, -0.20","-0.11","-0.02, 0.31, -0.03", # WEBL condition
                         "0.07.","-0.17, 0.29, -0.20.","0.30","-1.26, -0.04, 0.11","0.35","1.20, -1.39, -0.04*" # TRES condition
                         )) %>%
  arrange(sample) %>%
   pivot_wider(names_from = c(sample,model),values_from = significant)

 
(tab <- t %>% gt() %>%
   tab_style(
    style = cell_fill(color = "lightgreen"),
    locations = select(t,matches(".*s1.*|.*s2.*")) %>%
      map2(.y = names(.),.f = function(.x,.y) {cells_body(columns = .y,
                   rows = str_which(.x,"(.*\\.$)|(.*\\*$)"))}))  %>%
   tab_spanner_delim(
    delim="_"
  ))
```

This table summarizes my findings. The values present the mean effect size for each factor under investigation. A green fill indicates a model in which the specified factor (column 2) significantly improved the parsimony of the model. I used likelihood ratio tests for all comparisons to compare a model with and without the factor. For brood size and condition, I also compared a model with the additive factor to a model with the factor interacted with habitat (indicated by the column names). The column spanners indicate whether the response variable was baseline, stressed cort, or stressed - baseline cort. In all models, I used the same measure of mother cort and nestling cort, e.g. if response was baseline nestling cort, I used baseline mother cort as a covariate in that model.

### Details of findings

#### 1. How does juliandate relate to cort?

##### Distribution of juliandate

```{r}
ggplot(mapping = aes(x = juliandate),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("WEBL")

ggplot(mapping = aes(x = juliandate),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("TRES")
```

##### Variation in cort across juliandate

```{r}

ggplot(mapping = aes(x = juliandate,y = mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s1")

ggplot(mapping = aes(x = juliandate,y = mean_s2),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s2")

ggplot(mapping = aes(x = juliandate,y = mean_s2-mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s2-s1")
ggplot(mapping = aes(x = juliandate,y = mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s1")

ggplot(mapping = aes(x = juliandate,y = mean_s2),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s2")

ggplot(mapping = aes(x = juliandate,y = mean_s2-mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s2-s1")
```

##### Variation in juliandate between occasions

```{r}

ggplot(mapping = aes(x = occasion,y = juliandate,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL")

ggplot(mapping = aes(x = occasion,y = juliandate,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_violin() +
  geom_point() +
  ggtitle("TRES")

```

##### Model-predicted relationship between juliandate and cort

Reminder: full model is 
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate + rand(attempt_id)

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))
```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

Stressed cort - baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor juliandate"))
```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares a model with and without juliandate.
 
###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

I do not know why the best fit line is above the data!! Really weird.

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```


###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

Stressed cort - baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor juliandate"))
```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("juliandate") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no juliandate","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares models with and without juliandate.
 
#### 2. How does mother attempt number relate to cort?

##### Distribution of mother attempt number over juliandate

```{r}
ggplot(mapping = aes(x = mother_attempt_num,y = juliandate,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL")

ggplot(mapping = aes(x = mother_attempt_num,y = juliandate,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES")
```

##### Variation in cort across mother attempt number

```{r}
ggplot(mapping = aes(x = mother_attempt_num,y = mean_s1,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S1")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S2")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2-mean_s1,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S2-S1")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s1,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S1")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S2")

ggplot(mapping = aes(x = mother_attempt_num,y = mean_s2-mean_s1,group = mother_attempt_num),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S2-S1")
```

##### Model-predicted relationship between mother attempt number and cort

Reminder: full model is 
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate + rand(attempt_id)

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT WEBL; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT WEBL; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

```

Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT WEBL; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

```

This table compares models with and without mother attempt number.

 
###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT TRES; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor mother attempt number")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT TRES; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

```

Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + mother_attempt_num + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and mother attempt number:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("mother_attempt_num")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother attempt number") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT TRES; predictor mother_attempt_num") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother attempt number improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(mother_attempt_num),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no mother attempt number","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor mother attempt number")

```

This table compares models with and without mother attempt number.

#### 3. How does mother cort relate to nestling cort?

##### Distribution of mother cort

```{r}
ggplot(mapping = aes(x = cort_s1_mother),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("WEBL S1")

ggplot(mapping = aes(x = cort_s2_mother),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("WEBL S2")

ggplot(mapping = aes(x = cort_s2_mother-cort_s1_mother),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("WEBL S2-S1")

ggplot(mapping = aes(x = cort_s1_mother),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("TRES S1")

ggplot(mapping = aes(x = cort_s2_mother),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("TRES S2")

ggplot(mapping = aes(x = cort_s2_mother-cort_s1_mother),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_density(fill = "grey") +
  ggtitle("TRES S2-S1")
```

##### Variation in mother cort across nestling cort

```{r}

ggplot(mapping = aes(x = cort_s1_mother,y = mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s1")

ggplot(mapping = aes(x = cort_s2_mother,y = mean_s2),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s2")

ggplot(mapping = aes(x = cort_s2_mother - cort_s1_mother,y = mean_s2-mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL s2-s1")

ggplot(mapping = aes(x = cort_s1_mother,y = mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s1")

ggplot(mapping = aes(x = cort_s2_mother,y = mean_s2),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s2")

ggplot(mapping = aes(x = cort_s2_mother - cort_s1_mother,y = mean_s2-mean_s1),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES s2-s1")
```

##### Model-predicted relationship between mother cort and nestling cort

Reminder: full model is 
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate + rand(attempt_id)

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("cort_s1_mother_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("baseline mother cort") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother cort improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no mother baseline cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))
```

This table presents the full model results.

###### Plot of predicted relationship between stressed nestling cort and stressed mother cort:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("cort_s2_mother_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("stressed mother cort") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother cort improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```
 
 Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(juliandate),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and stressed-baseline mother cort:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("mother_cort_diff_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother stressed-baseline cort") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother cort improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(juliandate),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no mother cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table presents results with and without mother cort.
 
###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("cort_s1_mother_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother baseline cort") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

I do not know why the best fit line is above the data!! Really weird.

###### Does the inclusion of juliandate improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no mother baseline cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed nestling cort and stressed mother cort:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("juliandate_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("stressed mother cort") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```


###### Does the inclusion of stressed mother cort improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled +  (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no mother stressed cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(juliandate),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and stressed-baseline mother cort:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("mother_cort_diff_scaled")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("mother stressed-baseline cort") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of mother cort improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   !is.na(juliandate),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no mother cort","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table presents models with and without mother cort.

#### 4. How does occasion relate to cort?

##### Distribution of occasion over juliandate

```{r}
ggplot(mapping = aes(x = occasion,y = juliandate,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL")

ggplot(mapping = aes(x = occasion,y = juliandate,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES")
```

##### Variation in cort across occasion

```{r}
ggplot(mapping = aes(x = occasion,y = mean_s1,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S1")

ggplot(mapping = aes(x = occasion,y = mean_s2,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S2")

ggplot(mapping = aes(x = occasion,y = mean_s2-mean_s1,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "WEBL",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("WEBL S2-S1")

ggplot(mapping = aes(x = occasion,y = mean_s1,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S1")

ggplot(mapping = aes(x = occasion,y = mean_s2,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S2")

ggplot(mapping = aes(x = occasion,y = mean_s2-mean_s1,group = occasion),
       data = filter(c,
                     Age == "L",
                     Species == "TRES",
                     occasion %in% c(2,3))) +
  theme_classic() +
  geom_violin() +
  geom_point() +
  ggtitle("TRES S2-S1")
```

##### Model-predicted relationship between occasion and cort

Reminder: full model is 
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate + rand(attempt_id)

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor occasion"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and occasion:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor occasion")

```

Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and occasion:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor occasion")

```

This table compares models with and without occasion.
 
###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor occasion"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and occasion:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and juliandate:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor occasion")

```

Stressed-baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )

t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df,t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor mother attempt number"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed - baseline nestling cort and occasion:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("occasion")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("occasion") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Occasion") +
   ggtitle("Stressed-baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of occasion improve the model?


```{r,fig.height=4,fig.width=5}
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1) %>%
  mutate(model = c("no occasion","full model"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor occasion")

```

This table compares models with and without occasion.

#### 5. How does brood size relate to cort?

##### Distribution of brood size

```{r}
(p <- ggplot(aes(x = brood_size),data = filter(c,
                                       Age == "L",
                                       Species == "WEBL")) +
   theme_classic() +
   ggtitle("WEBL") +
   geom_density(fill = "grey"))

(p <- ggplot(aes(x = brood_size),data = filter(c,
                                       Age == "L",
                                       Species == "TRES")) +
   theme_classic() +
   ggtitle("TRES") +
   geom_density(fill = "grey"))

```

##### Seasonal variation in brood size

```{r}
ggplot(mapping = aes(x = juliandate,y = brood_size),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = juliandate,y = brood_size),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES")
```

##### Correlation of brood size and cort

###### WEBL

```{r}
ggplot(mapping = aes(x = brood_size,y = mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = brood_size,y = mean_s2),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
ggplot(mapping = aes(x = brood_size,y = mean_s2-mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2-s1")
```

###### TRES

```{r}
ggplot(mapping = aes(x = brood_size,y = mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = brood_size,y = mean_s2),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
ggplot(mapping = aes(x = brood_size,y = mean_s2-mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES")) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2-s1")
```

##### Model-predicted relationship between brood size and cort

Reminder: full model is
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + mother attempt number

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s1_noint <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_noint <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

Stressed - baseline cort as response variable

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed-baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed-baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_s1_noint <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1_noint,m_s2_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s1_noint <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_noint <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

Stressed - baseline cort as response variable

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed-baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("brood_size_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Brood size") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Brood size") +
   ggtitle("Stressed-baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_s1_noint <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1_noint,m_s2_s1) %>%
  mutate(model = c("no brood_size","brood_size + habitat","brood_size * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

#### 6. How does body condition relate to cort?

##### Distribution of condition

```{r}
(p <- ggplot(aes(x = condition),data = filter(c,
                                       Age == "L",
                                       Species == "WEBL",
                                       condition < 2)) +
   theme_classic() +
   ggtitle("WEBL") +
   geom_density(fill = "grey"))

(p <- ggplot(aes(x = condition),data = filter(c,
                                       Age == "L",
                                       Species == "TRES",
                                       condition > .5)) +
   theme_classic() +
   ggtitle("TRES") +
   geom_density(fill = "grey"))

```

##### Seasonal variation in condition

```{r}
ggplot(mapping = aes(x = juliandate,y = condition),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL",
                                                               condition < 2)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("WEBL")
ggplot(mapping = aes(x = juliandate,y = condition),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES",
                                                               condition > .5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("TRES")
```

##### Correlation of condition and cort

###### WEBL

```{r}
ggplot(mapping = aes(x = condition,y = mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL",
                                                              occasion < 2)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = condition,y = mean_s2),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL",
                                                              occasion < 2)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
ggplot(mapping = aes(x = condition,y = mean_s2-mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "WEBL",
                                                               occasion < 2)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2-s1")
```

###### TRES

```{r}
ggplot(mapping = aes(x = condition,y = mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES",
                                                              condition > .5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S1")
ggplot(mapping = aes(x = condition,y = mean_s2),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES",
                                                              condition > .5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2")
ggplot(mapping = aes(x = condition,y = mean_s2-mean_s1),data = filter(c,
                                                               Age == "L",
                                                               Species == "TRES",
                                                               condition > .5)) +
  geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("S2-s1")
```

##### Model-predicted relationship between condition and cort

Reminder: full model is
- cort ~ mother cort + week2/week3 + brood_size * habitat + condition * habitat + juliandate + rand(attempt_id)

###### WEBL

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s1_noint <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_noint <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and condition, and one without condition in the model.

Stressed - baseline cort as response variable

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed-baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed-baseline CORT WEBL; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_s1_noint <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition < 2,
                   Species == "WEBL") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1_noint,m_s2_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### TRES

Baseline cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s1 <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s1_noint <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s1_nocovar <- lmerTest::lmer(mean_s1_scaled ~ cort_s1_mother_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s1,cort_s1_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s1_nocovar,m_s1_noint,m_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

###### Stressed cort as response variable:

```{r,fig.width=8,fig.height=5}
m_s2 <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed cort and condition:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of brood_size improve the model, and does the interaction brood_size * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_noint <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_nocovar <- lmerTest::lmer(mean_s2_scaled ~ cort_s2_mother_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(across(c(mean_s2,cort_s2_mother,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_nocovar,m_s2_noint,m_s2) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.

Stressed - baseline cort as response variable

```{r,fig.width=8,fig.height=5}
m_s2_s1 <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
t <- summary(m_s2_s1) %>% coef()
p <- row.names(t)
col <- colnames(t)
col[length(col)] <- "P-value"
t <- t %>% data.frame()
names(t) <- col
(t1 <- t %>% mutate(Predictor = p, .before = Estimate) %>% tibble() %>%
  # select(!c(df, t)) %>%
  mutate_at(c("Estimate", "Std. Error"), round, digits = 2) %>%
  mutate_at("P-value",round, digits = 4) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_options(data_row.padding = px(1)) %>%
  tab_header(title = "Response s2-s1, predictor juliandate"))

```

This table presents the full model results.

###### Plot of predicted relationship between stressed-baseline cort and brood size:

```{r,message=FALSE,warning=FALSE,fig.width = 6, fig.height= 4}
(p1 <- ggpredict(m_s2_s1,terms = c("condition_scaled","habitat")) %>% plot(line.size = 1.5,
                                                                                            alpha = .2,show_data = TRUE) +
    theme_classic() +
    xlab("Condition") +
    ylab("Stressed-baseline nestling CORT (z-scaled)") +
    labs(title = element_blank(),color = "Habitat") +
   ggtitle("Stressed-baseline CORT TRES; predictor juliandate") +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(text = element_text(size = 13)))

```

###### Does the inclusion of condition improve the model, and does the interaction condition * habitat further improve it?

```{r,fig.height=4,fig.width=5}

m_s2_s1_noint <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + condition_scaled + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
m_s2_s1_nocovar <- lmerTest::lmer(nest_cort_diff_scaled ~ mother_cort_diff_scaled + occasion + brood_size_scaled * habitat + juliandate_scaled + (1|attempt_id),
          data = c %>%
            filter(Age == "L",
                   occasion %in% c(2,3),
                   !is.na(mean_s2),
                   !is.na(mean_s1),
                   !is.na(cort_s1_mother),
                   !is.na(cort_s2_mother),
                   !is.na(brood_size),
                   !is.na(condition),
                   condition > .5,
                   Species == "TRES") %>%
            mutate(nest_cort_diff = mean_s2-mean_s1,
                   mother_cort_diff = cort_s2_mother-cort_s1_mother,
                   across(c(nest_cort_diff,mother_cort_diff,brood_size,condition,juliandate),
                          ~ scale(.x)[,1],
                          .names = "{.col}_scaled"),
                   occasion = factor(occasion))
          )
anova(m_s2_s1_nocovar,m_s2_s1_noint,m_s2_s1) %>%
  mutate(model = c("no condition","condition + habitat","condition * habitat"),.before = npar) %>%
  rename(`P-value` = `Pr(>Chisq)`) %>%
  mutate(`P-value` = round(`P-value`,digits = 4)) %>%
  mutate(`P-value` = if_else(c(`P-value` < .05),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .01),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  mutate(`P-value` = if_else(c(`P-value` < .001),as.character(`P-value`) %>% paste0("*"),as.character(`P-value`))) %>%
  gt() %>% tab_header(title = "Response s2-s1, predictor juliandate")

```

This table compares three models: the full model, one with no interaction between habitat and brood_size, and one without brood_size in the model.
