---
title: "Publication tables"
output: html_notebook
---

```{r setup}
require(tidyverse)
require(ggplot2)
require(lubridate)
require(scales)
require(viridis)
require(ggeffects)
require(ggimage)
require(magick)
require(cowplot)
require(ggggeffects)
require(emmeans)
require(multcomp)
require(gt)
library(glmmTMB)
library(dagitty)
library(ggdag)
library(ggplot2)
library(egg)
library(igraph)
library(tidyverse)
library(performance)
library(modelsummary)
library(car)
library(lme4)
library(hms)
library(emmeans)
library(patchwork)
getwd()
setwd("..")
getwd()
source("code/growth_model_eval.R")
source("code/survival_model_eval.R")
source("code/cort_model_eval.R")
source("code/provis_model_eval.R")
```


# Sample size tables

```{r}
growth <- rbind(t_samp_year_growth_webl$`_data`,t_samp_year_growth_tres$`_data`) %>% dplyr::select(Habitat, `2021`, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Growth ~ Temp * Land cover") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)
  # dplyr::select(-row) %>%
 

growth_by_basecort_provis <- rbind(t_ss_year_webl_growthbybasecortprovis$`_data`,t_ss_year_tres_growthbybasecortprovis$`_data`) %>% dplyr::select(Habitat, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",3)),
         Response = "Growth ~ Baseline cort + Provisioning") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)
  # dplyr::select(-row) %>%

growth_by_abscort_provis <- rbind(t_ss_year_webl_growthbyabscortprovis$`_data`,t_ss_year_tres_growthbyabscortprovis$`_data`) %>% dplyr::select(Habitat, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",3)),
         Response = "Growth ~ Stress-induced cort + Provisioning") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

survival <- rbind(ss_year_survival_webl,ss_year_survival_tres) %>% dplyr::select(Habitat, `2021`, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Survival") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value) %>%
  mutate(across(everything(),~as.character(.x)))

baseline_cort <- rbind(t_ss_year_webl_s1$`_data`,t_ss_year_tres_s1$`_data`) %>% dplyr::select(Habitat, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Baseline corticosterone") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

s2_cort <- rbind(t_ss_year_webl_s2$`_data`,t_ss_year_tres_s2$`_data`) %>% dplyr::select(Habitat, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Stress-induced corticosterone") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

abs_cort <- rbind(t_ss_year_webl_abs$`_data`,t_ss_year_tres_abs$`_data`) %>% dplyr::select(Habitat, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Stress-induced - baseline corticosterone") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)
  

provis <- rbind(t_ss_year_webl_provis$`_data`,t_ss_year_tres_provis$`_data`) %>% dplyr::select(Habitat, `2021`, `2022`, `2023`) %>% 
  replace_na(replace = list(`2021` = 0,`2022` = 0, `2023` = 0)) %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Provisioning") %>%
  # mutate(row=row_number()) %>% 
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

```

```{r}
# (samp_size_1 <- rbind(growth,growth_by_basecort_provis,growth_by_abscort_provis,survival) %>% gt(rowname_col = "Habitat",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%
#   
#   tab_spanner_delim(
#     delim="_") %>%
# summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)))
# 
# (samp_size_2 <- rbind(provis,baseline_cort,abs_cort) %>% gt(rowname_col = "Habitat",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%
#   
#   tab_spanner_delim(
#     delim="_") %>%
# summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE)))
# 
# rbind(samp_size_1,samp_size_2)
# 
# library(gtExtras)
# 
# process_samp <- function(x){gt(x,rowname_col = "Habitat",groupname_col = "Response") %>%
#     tab_options(data_row.padding = px(1)) %>%
#   
#   tab_spanner_delim(
#     delim="_") %>%
# summary_rows(groups = "Response",columns = -c(Habitat),fns = list(id = "Total") ~ sum(.,na.rm = TRUE))
#     }
# 
# samp_size <- gt_two_column_layout(list(samp_size_1,samp_size_2))
# 
# gtsave_extra(samp_size,"../figures/full_samp_size_tbl.png")

(samp_size_onecol <- rbind(growth,growth_by_basecort_provis,growth_by_abscort_provis,survival,baseline_cort,s2_cort,abs_cort,provis) %>%
   mutate(across(everything(),~replace_na(.x,"0, 0")),
          across(everything(),~str_replace_all(.x,"NA","0"))) %>%
   gt(rowname_col = "Habitat",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_") %>%
summary_rows(columns = -c(Habitat),fns = list(id = "Total") ~ {
        t <- str_split(.,", ",simplify = TRUE)
        if(ncol(t) == 2){
          t[,1] %>% as.numeric() %>% sum(na.rm = TRUE) %>% paste(t[,2] %>% as.numeric() %>% sum(na.rm = TRUE),sep = ", ")
        } else {
          t[,1] %>% as.numeric() %>% sum(na.rm = TRUE) %>% as.character()
        }
        
      })
)

gtsave(samp_size_onecol,"../figures/full_samp_size_tbl.html")

```


## Land cover contrast tables

```{r}
growth <- rbind(growthbyhabitat_webl$`_data`,growthbyhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "t.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Growth") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

survival <- rbind(survival_nestpd_byhabitat_webl$`_data`,
                  survival_nestpd_byhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "z.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Survival") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

base_cort <- rbind(s1byhabitat_webl$`_data`,
                  s1byhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "t.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Baseline corticosterone") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

s2_cort <- rbind(s2byhabitat_webl$`_data`,
                  s2byhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "t.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Stress-induced corticosterone") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

abs_cort <- rbind(absbyhabitat_webl$`_data`,
                  absbyhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "t.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Stress-induced - Baseline corticosterone") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

provis <- rbind(provisbyhabitat_webl$`_data`,
                  provisbyhabitat_tres$`_data`) %>%
  rename(Contrast = "contrast",Estimate = "estimate",Df = "df",`Statistic` = "z.ratio",`P-value` = "p.value") %>%
  mutate(Species = c(rep("Western Bluebird",6),rep("Tree Swallow",6)),
         Response = "Provisioning") %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Contrast)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

(landcover_contrast <- rbind(growth,survival,base_cort,s2_cort,abs_cort,provis) %>% gt(rowname_col = "Contrast",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%

  tab_spanner_delim(
    delim="_"))

gtsave(landcover_contrast,"../figures/full_landcover_contrast_tbl.html")

```

## Trend tables

```{r}
growth <- rbind(weblgrowthtrendmax$`_data`,tresgrowthtrendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Growth",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

survival <- rbind(weblsurvival_nestpd_trendmax$`_data`,tressurvival_nestpd_trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Survival",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

s1_cort <- rbind(webls1trendmax$`_data`,tress1trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Baseline corticosterone",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

s2_cort <- rbind(webls2trendmax$`_data`,tress2trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Stress-induced corticosterone",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

abs_cort <- rbind(weblabstrendmax$`_data`,tresabstrendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",4)),
         Response = "Stress-induced - baseline corticosterone",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

provis <- weblprovistrend$`_data` %>%
  rename(Trend = "Max temp trend",`Statistic` = "Z-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4)),
         Response = "Provisioning",
         Trend = as.character(Trend),
         SE = as.character(SE),
         Df = as.character(Df),
         Statistic = as.character(Statistic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Habitat)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

(trend <- rbind(growth,survival,s1_cort,s2_cort,abs_cort,provis) %>% gt(rowname_col = "Habitat",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%

  tab_spanner_delim(
    delim="_"))

gtsave(trend,"../figures/trend_tbl.html")

```


## Interaction tables

I'm going to combine tables in the style of the growth int tables

```{r}
growth <- rbind(int_tab_growth_webl$`_data`,int_tab_growth_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  dplyr::filter((max_or_min == "Max temp")) %>%
  dplyr::select(-max_or_min) %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Growth",
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

survival <- rbind(int_tab_survival_nestpd_webl$`_data`,int_tab_survival_nestpd_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  dplyr::filter((max_or_min == "Max temp")) %>%
  dplyr::select(-max_or_min) %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Survival",
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

base_cort <- rbind(int_tab_s1_webl$`_data`,int_tab_s1_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  dplyr::filter((max_or_min == "Max temp")) %>%
  dplyr::select(-max_or_min) %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Baseline corticosterone",
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

s2_cort <- rbind(int_tab_s2_webl$`_data`,int_tab_s2_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  dplyr::filter((max_or_min == "Max temp")) %>%
  dplyr::select(-max_or_min) %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Stress-induced corticosterone",
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

abs_cort <- rbind(int_tab_abs_webl$`_data`,int_tab_abs_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  dplyr::filter((max_or_min == "Max temp")) %>%
  dplyr::select(-max_or_min) %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Stress-induced - Baseline corticosterone",
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

provis <- rbind(int_tab_provis_webl$`_data`,int_tab_provis_tres$`_data`) %>%
  rename(`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",3),rep("Tree Swallow",3)),
         Response = "Provisioning",
         Model = rep(c("No interaction",
                       "Linear temp * LC",
                       "Squared temp * LC"),2),
         AIC = as.character(AIC),
         Chisq = as.character(Chisq),
         `P-value` = as.character(`P-value`)) %>%
  pivot_longer(-c(Species, Response, Model)) %>%
  pivot_wider(names_from=c(Species, name), values_from=value)

(int_tab <- rbind(growth,survival,base_cort,s2_cort,abs_cort,provis) %>% gt(rowname_col = "Model",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%

  tab_spanner_delim(
    delim="_"))

gtsave(int_tab,"../figures/int_tbl.html")
```

## Growth coefficient table

```{r}
webl <- summary(g_lintemp_webl) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- summary(g_lintemp_addmin_tres) %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")

```

# covariate name replacement table

```{r}
name_key_growth <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Maximum temperature (scaled)",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Minimum temperature (scaled)",
               "Nestling age",
               "Julian date of hatching",
               "Year: 2022",
               "Year: 2023",
               "Max temp slope in orchards",
               "Max temp slope in grasslands",
               "Max temp slope in row crops",
               "Min temp slope in orchards",
               "Min temp slope in grasslands",
               "Min temp slope in row crops"))
```


```{r}

(g_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_growth$new[match(Covariate, name_key_growth$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(g_coef,"../figures/growth_coef.html")

```


## Coefficients for survival

```{r}
webl <- s_nestpd_WEBL_addmin %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`z value`,~round(.x,digits = 2)),
           across(`Pr(>|z|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- s_nestpd_TRES_noint %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`z value`,~round(.x,digits = 2)),
           across(`Pr(>|z|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_s <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Maximum temperature (scaled)",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Minimum temperature (scaled)",
               "Julian date of hatching",
               "Year: 2022",
               "Year: 2023",
               "Site: PG",
               "Site: RR",
               "Site: WI",
               "Max temp slope in orchards",
               "Max temp slope in grasslands",
               "Max temp slope in row crops"))
```

```{r}

(s_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`Z-value` = `z value`,P = `Pr(>|z|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_s$new[match(Covariate, name_key_s$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(s_coef,"../figures/survival_coef.html")

```

## Coefficients for baseline cort

```{r}
webl <- s1_prior_day_webl %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- s1_prior_day_tres %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_s1 <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Maximum temperature (scaled)",
               "Minimum temperature (scaled)",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Nestling age",
               "Julian date of hatching",
               "Year: 2023",
               "Min temp slope in orchards",
               "Min temp slope in grasslands",
               "Min temp slope in row crops",
               "Max temp slope in orchards",
               "Max temp slope in grasslands",
               "Max temp slope in row crops"))
```

```{r}

(s1_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_s1$new[match(Covariate, name_key_s1$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(s1_coef,"../figures/s1_coef.html")

```


## Coefficients for abs cort

```{r}
webl <- abs_webl_priordayt %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- abs_tres_priordayt %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_abs <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Maximum temperature (scaled)",
               "Minimum temperature (scaled)",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Nestling age",
               "Julian date of hatching",
               "Year: 2023",
               "Max temp slope in orchards",
               "Max temp slope in grasslands",
               "Max temp slope in row crops",
               "Min temp slope in orchards",
               "Min temp slope in grasslands",
               "Min temp slope in row crops"))
```

```{r}

(abs_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_abs$new[match(Covariate, name_key_abs$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(abs_coef,"../figures/abs_coef.html")

```

## Coefficients for s2 cort

```{r}
webl <- s2_webl %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- s2_tres %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_s2 <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Maximum temperature (scaled)",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Minimum temperature (scaled)",
               "Nestling age",
               "Julian date of hatching",
               "Year: 2023",
               "Max temp slope in orchards",
               "Max temp slope in grasslands",
               "Max temp slope in row crops",
               "Min temp slope in orchards",
               "Min temp slope in grasslands",
               "Min temp slope in row crops"))
```

```{r}

(s2_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_s2$new[match(Covariate, name_key_s2$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(s2_coef,"../figures/s2_coef.html")

```

## Coefficients for provis

```{r}
library(magrittr)
webl <- provis_webl %>% summary() %>% coef() %>% extract2(1) %>% as_tibble(rownames = "Covariate") %>%
    dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`z value`,~round(.x,digits = 2)),
           across(`Pr(>|z|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- provis_tres %>% summary() %>% coef() %>% extract2(1) %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`z value`,~round(.x,digits = 2)),
           across(`Pr(>|z|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_provis <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Linear effect of mean temp",
               "Land cover: Orchard",
               "Land cover: Grassland",
               "Land cover: Row crop",
               "Quadratic effect of mean temp",
               "Julian date of hatching",
               "Linear effect of time of day",
               "Quadratic effect of time of day",
               "Nestling age",
               "Year: 2022",
               "Year: 2023",
               "Mean temp slope in orchards",
               "Mean temp slope in grasslands",
               "Mean temp slope in row crops",
               "Linear effect of mean temp",
               "Mean temp slope in orchards",
               "Slope of quadratic mean temp in orchards",
               "Mean temp slope in grasslands",
               "Slope of quadratic mean temp in grasslands",
               "Mean temp slope in row crops",
               "Slope of quadratic mean temp in row crop"))
```

```{r}

(provis_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`Z-value` = `z value`,P = `Pr(>|z|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_provis$new[match(Covariate, name_key_provis$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(provis_coef,"../figures/provis_coef.html")

```


## Coefficients for growth ~ s1 + provis

```{r}
library(magrittr)
webl <- g_provis_cort_webl %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- g_provis_cort_tres %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_s1_provis <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Baseline corticosterone (scaled)",
               "Mean provisioning rate (scaled)",
               "Linear effect of max temp",
               "Quadratic effect of max temp",
               "Mean humidity (scaled)",
               "Nestling age (scaled)",
               "Nestling condition (scaled)"))
```

```{r}

(g_s1_provis_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_s1_provis$new[match(Covariate, name_key_s1_provis$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(g_s1_provis_coef,"../figures/g_s1_provis_coef.html")

```

## Coefficients for growth ~ abs + provis

```{r}
library(magrittr)
webl <- g_provis_abscort_webl %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Western Bluebird")

tres <- g_provis_abscort_tres %>% summary() %>% coef() %>% as_tibble(rownames = "Covariate") %>%
    # dplyr::filter(Covariate != "poly(mean_temp_scaled, 2)1") %>%
    mutate(across(Estimate:`t value`,~round(.x,digits = 2)),
           across(`Pr(>|t|)`,~round(.x,digits = 3))) %>%
  mutate(Species = "Tree Swallow")
```

```{r}
name_key_abs_provis <- tibble(old = c(webl$Covariate,tres$Covariate) %>% unique(),
       new = c("Intercept","Stress-induced corticosterone (scaled)",
               "Mean provisioning rate (scaled)",
               "Maximum temperature (scaled)",
               "Minimum temperature (scaled)",
               "Mean humidity (scaled)",
               "Nestling age (scaled)",
               "Nestling condition (scaled)"))
```

```{r}

(g_abs_provis_coef <- rbind(webl,tres) %>%
  rename(SD = `Std. Error`,`T-value` = `t value`,P = `Pr(>|t|)`) %>%
   filter(!Covariate=="(Intercept)") %>%
   mutate(Covariate = name_key_abs_provis$new[match(Covariate, name_key_abs_provis$old)]) %>%
  pivot_longer(-c(Species,Covariate)) %>%
  mutate(value = as.character(value),
         value = if_else(name == "P" & value == "0","<0.001",value)) %>%
  pivot_wider(names_from = c(Species,name),values_from = value) %>% gt() %>%
  tab_options(data_row.padding = px(1)) %>%
  tab_spanner_delim(
    delim="_"))

gtsave(g_abs_provis_coef,"../figures/g_abs_provis_coef.html")

```

#### Validation table

Response will be row group
Predictor will be row name
Species is column spanner
Habitat is column name
each cell: estimate (p_value)
Could consider just putting the estimate with a significance indicator

predictors: meanmax temp week, max temp day, max hi week, max hi day, cum deg >30 week, cum hi >25 week


```{r}
setwd("..")
getwd()
source("code/growth_model_eval_othertempmeasures.R")
source("code/survival_model_eval_othertempmeasures.R")
source("code/provis_model_eval_othertempmeasures.R")
```



```{r}
growth <- rbind(weblgrowthtrendmax$`_data`,tresgrowthtrendmax$`_data`,
                weblgrowthtrendmaxhiweek$`_data`,tresgrowthtrendmaxhiweek$`_data`,
                weblgrowthtrenddeghr30week$`_data`,tresgrowthtrenddeghr30week$`_data`,
                weblgrowthtrendhihr25week$`_data`,tresgrowthtrendhihr25week$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = rep(c(rep("Western Bluebird",4),rep("Tree Swallow",4)),4),
         Response = "Growth",
         Predictor = c(rep("Mean max temp over prior week",8),
                       rep("Mean max heat index over prior week",8),
                       rep("Cumulative degree-hours >30\u00b0C",8),
                       rep("Cumulative heat index-hours >30\u00b0C",8)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

survival <- rbind(weblsurvival_nestpd_trendmax$`_data`,tressurvival_nestpd_trendmax$`_data`,
                  weblsurvival_nestpd_trendmax_meanmaxhi$`_data`,tressurvival_nestpd_trendmax_meanmaxhi$`_data`,
                  weblsurvival_nestpd_trendmax_deghr_30$`_data`,tressurvival_nestpd_trendmax_deghr_30$`_data`,
                  weblsurvival_nestpd_trendmax_hihr_30$`_data`,tressurvival_nestpd_trendmax_hihr_30$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = rep(c(rep("Western Bluebird",4),rep("Tree Swallow",4)),4),
         Response = "Survival",
         Predictor = c(rep("Mean max temp over prior week",8),
                       rep("Mean max heat index over prior week",8),
                       rep("Cumulative degree-hours >30\u00b0C",8),
                       rep("Cumulative heat index-hours >30\u00b0C",8)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

s1_cort <- rbind(webls1trendmax$`_data`,tress1trendmax$`_data`,
                 webls1_priordayt_trendmax$`_data`,tress1_priordayt_trendmax$`_data`,
                 webls1_weekhi_trendmax$`_data`,tress1_weekhi_trendmax$`_data`,
                 webls1_priordaymaxhhi_trendmax$`_data`,tress1_priordaymaxhhi_trendmax$`_data`,
                 webls1_cumdegreeweek_trendmax$`_data`,tress1_cumdegreeweek_trendmax$`_data`,
                 webls1_cumhiweek_trendmax$`_data`,tress1_cumhiweek_trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = rep(c(rep("Western Bluebird",4),rep("Tree Swallow",4)),6),
         Response = "Baseline corticosterone",
         Predictor = c(rep("Mean max temp over prior week",8),
                       rep("Max temp over prior day",8),
                       rep("Mean max heat index over prior week",8),
                       rep("Max heat index over prior day",8),
                       rep("Cumulative degree-hours >30\u00b0C",8),
                       rep("Cumulative heat index-hours >30\u00b0C",8)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

s2_cort <- rbind(webls2trendmax$`_data`,tress2trendmax$`_data`,
                 webls2_priordayt_trendmax$`_data`,tress2_priordayt_trendmax$`_data`,
                 webls2_weekhi_trendmax$`_data`,tress2_weekhi_trendmax$`_data`,
                 webls2_priordaymaxhhi_trendmax$`_data`,tress2_priordaymaxhhi_trendmax$`_data`,
                 webls2_cumdegreeweek_trendmax$`_data`,tress2_cumdegreeweek_trendmax$`_data`,
                 webls2_cumhiweek_trendmax$`_data`,tress2_cumhiweek_trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = rep(c(rep("Western Bluebird",4),rep("Tree Swallow",4)),6),
         Response = "Stress-induced corticosterone",
         Predictor = c(rep("Mean max temp over prior week",8),
                       rep("Max temp over prior day",8),
                       rep("Mean max heat index over prior week",8),
                       rep("Max heat index over prior day",8),
                       rep("Cumulative degree-hours >30\u00b0C",8),
                       rep("Cumulative heat index-hours >30\u00b0C",8)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

abs_cort <- rbind(weblabstrendmax$`_data`,tresabstrendmax$`_data`,
                  weblabs_priordayt_trendmax$`_data`,tresabs_priordayt_trendmax$`_data`,
                  weblabs_weekhi_trendmax$`_data`,tresabs_weekhi_trendmax$`_data`,
                  weblabs_priordaymaxhhi_trendmax$`_data`,tresabs_priordaymaxhhi_trendmax$`_data`,
                  weblabs_cumdegreeweek_trendmax$`_data`,tresabs_cumdegreeweek_trendmax$`_data`,
                  weblabs_cumhiweek_trendmax$`_data`,tresabs_cumhiweek_trendmax$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "T-ratio",`P-value` = "P") %>%
  mutate(Species = rep(c(rep("Western Bluebird",4),rep("Tree Swallow",4)),6),
         Response = "Stress-induced - baseline corticosterone",
         Predictor = c(rep("Mean max temp over prior week",8),
                       rep("Max temp over prior day",8),
                       rep("Mean max heat index over prior week",8),
                       rep("Max heat index over prior day",8),
                       rep("Cumulative degree-hours >30\u00b0C",8),
                       rep("Cumulative heat index-hours >30\u00b0C",8)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

provis <- rbind(weblprovistrend$`_data` %>% mutate(degree = "linear"),tresprovistrend$`_data`,
                weblprovistrend_hi$`_data`,tresprovistrend_hi$`_data`) %>%
  rename(Trend = "Max temp trend",`Statistic` = "Z-ratio",`P-value` = "P") %>%
  mutate(Species = c(rep("Western Bluebird",4),rep("Tree Swallow",8),rep("Western Bluebird",8),rep("Tree Swallow",8)),
         Response = "Provisioning",
         Predictor = c(rep("Mean hourly temperature",12),rep("Mean hourly heat index",16)),
         sig = if_else(`P-value` == "<0.001","***",
                       if_else(as.numeric(`P-value`) < .01, "**",
                               if_else(as.numeric(`P-value`) < .05,"*",""))),
         Estimate = paste0(as.character(Trend),sig)) %>%
  dplyr::select(Species, Response, Predictor, Habitat, Estimate, degree) %>%
  pivot_wider(names_from = degree,values_from = Estimate) %>%
  mutate(quadratic = replace_na(quadratic, "NA"),
         Estimate = paste0(linear,", ",quadratic)) %>%
  dplyr::select(-c(linear,quadratic)) %>%
  group_by(Response) %>%
  pivot_longer(-c(Species, Response, Predictor,Habitat)) %>%
  pivot_wider(names_from=c(Species, Habitat), values_from=value) %>%
  dplyr::select(-name)

(trend <- rbind(growth,survival,s1_cort,s2_cort,abs_cort,provis) %>% gt(rowname_col = "Predictor",groupname_col = "Response") %>% tab_options(data_row.padding = px(1)) %>%

  tab_spanner_delim(
    delim="_"))

gtsave(trend,"../figures/val_tbl.html")
```

## Validation table for interaction of max temp and julian day

The data from this comes from seasonal_sensitivity.Rmd, but I don't have time to make the purl whatever work. So to my future self, just run all that file before you run this chunk. Sorry.




